---
title: "Multiple Imputation"
subtitle: "MICE imputation and within/between-person centering for 'All BANG, little buck'"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

This document runs multiple imputation on the enriched survey data from
`preprocessing.qmd` and derives the primary analysis dataset (`dat`). It is
its own `targets` stage (`imputation_report`), separate from data loading and
from model fitting (`modelling.qmd`) -- so editing a model formula doesn't
force this (comparatively expensive) imputation to rerun.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(mice)
library(scales)
library(targets)
```

```{r}
#| label: source-functions
#| code-summary: "Show code (Load pipeline functions)"

source("R/targets/imputation.R")
source("R/targets/derive.R")
```

```{r}
#| label: load-inputs
#| code-summary: "Show code (Load preprocessing.qmd's exported objects)"

tar_load(surveys)
```

## Multiple Imputation

Main analysis imputes the analytical sample (participants with at least 15
completed daily surveys) using `mice`, with predictive mean matching for
continuous items and logistic regression for the binary self-reported-play
item. BANGS (in-game need) items are only imputed for days when the person
reported playing (or play status is unknown) -- they aren't "missing" on
non-play days, the question wasn't applicable.

```{r}
#| label: mice
#| code-summary: "Show code (Run MICE imputation on analytical sample)"
#| results: hide

min_waves <- 15
full_eligible_pids <- unique(surveys$pid)

message(glue(
  "Imputing analytical sample: {length(unique(surveys$pid[surveys$diaries_completed >= min_waves]))}/{length(full_eligible_pids)} participants with >={min_waves} waves"
))

telemetry_vars <- surveys |>
  filter(diaries_completed >= min_waves) |>
  select(
    pid,
    wave,
    date,
    telemetry_played_any_24h,
    play_minutes_24h,
    telemetry_played_any_12h,
    play_minutes_12h,
    telemetry_played_any_6h,
    play_minutes_6h,
    telemetry_played_any_24h_pre,
    play_minutes_24h_pre
  )

surveys_wide <- build_wide_survey(surveys, min_waves = min_waves)

M_IMPUTATIONS <- 27
m_imputations <- M_IMPUTATIONS

message(glue(
  "Running MICE: M={M_IMPUTATIONS}, N={nrow(surveys_wide)}, started {Sys.time()}"
))
imp <- run_mice(surveys_wide, m = M_IMPUTATIONS, maxit = 5, seed = 8675309)
message(glue("Completed {Sys.time()}"))

if (nrow(imp$loggedEvents) > 0) {
  message(glue("Warning: {nrow(imp$loggedEvents)} logged events during imputation"))
} else {
  message("No logged events - imputation completed without issues")
}
```

Convert the completed imputations to long format, compute composite need
scores, and add within/between-person centered predictors:

```{r}
#| label: post-imputation-centering
#| code-summary: "Show code (Calculate composites and within/between-person centering)"

daily_imputed <- derive_analysis_dat(imp, telemetry_vars)

# Main analysis dataset: use .imp > 0 (imputed datasets); .imp == 0 is the
# original data with missingness
dat <- daily_imputed |> filter(.imp > 0)
dat_desc <- dat |> filter(.imp == 1)

# Observed (non-imputed) rows: .imp == 0 from the long frame, all columns.
# Feeds supplement.qmd's observed-vs-imputed diagnostic figure and the
# complete-case sensitivity analyses (S2, S4).
dat_observed <- daily_imputed |> filter(.imp == 0)

message(glue(
  "Main analysis dataset: {n_distinct(dat$pid)} participants, {nrow(dat)} observations"
))
```

## Exported Objects

```{r}
#| label: export
#| code-summary: "Show code (Export objects for modelling.qmd/manuscript.qmd/supplement.qmd)"

source("R/targets/export.R")
dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  imputation_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(imputation_export_names)} objects to data/exports/"))
```
