---
title: "Multiple Imputation"
subtitle: "MICE imputation and within/between-person centering for 'All BANG, little buck'"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

Runs multiple imputation by chained equations (MICE, M = 27) on the survey
data, then derives the analysis datasets: composite need-satisfaction and
need-frustration scores from the imputed items, joined to the telemetry play
measures, with within- and between-person centered predictors.

Two imputations are run with identical settings. The **primary** imputation
covers all eligible participants (>=1 completed daily survey -- the
preregistered imputation target). The **restricted** imputation covers the
>=15-survey (>=50%) subsample, and is used only for the sample-construction
sensitivity analysis (S4) and the Bayesian random-slopes check (S2).

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(mice)
library(scales)
library(targets)
```

```{r}
#| label: source-functions
#| code-summary: "Show code (Load pipeline functions)"

source("R/targets/imputation.R")
source("R/targets/derive.R")
```

```{r}
#| label: load-inputs
#| code-summary: "Show code (Load preprocessing.qmd's exported objects)"

tar_load(surveys)
```

## Multiple Imputation

`mice` is run with predictive mean matching for continuous items and logistic
regression for the binary self-reported-play item. BANGS (in-game need) items
are only imputed for days when the person reported playing (or play status is
unknown) -- they aren't "missing" on non-play days, the question wasn't
applicable.

```{r}
#| label: mice
#| code-summary: "Show code (Run MICE on the primary and restricted samples)"
#| results: hide

M_IMPUTATIONS <- 27
m_imputations <- M_IMPUTATIONS

# Telemetry columns joined to the imputed survey data. Passively logged, so
# never imputed; filtered per-sample to match each imputation's participants.
telemetry_cols <- c(
  "pid", "wave", "date",
  "telemetry_played_any_24h", "play_minutes_24h",
  "telemetry_played_any_12h", "play_minutes_12h",
  "telemetry_played_any_6h", "play_minutes_6h",
  "telemetry_played_any_24h_pre", "play_minutes_24h_pre"
)

# Impute one survey-completion sample: pivot wide, run MICE, and derive the
# long analysis frame (item composites + within/between-person centering).
# min_waves = 0 keeps every participant with at least one completed survey.
impute_sample <- function(min_waves) {
  n_pids <- n_distinct(surveys$pid[surveys$diaries_completed >= min_waves])
  message(glue(
    "MICE (min_waves={min_waves}): {n_pids} participants, M={M_IMPUTATIONS}, started {Sys.time()}"
  ))
  telemetry_vars <- surveys |>
    filter(diaries_completed >= min_waves) |>
    select(all_of(telemetry_cols))
  surveys_wide <- build_wide_survey(surveys, min_waves = min_waves)
  imp <- run_mice(surveys_wide, m = M_IMPUTATIONS, maxit = 5, seed = 8675309)
  message(glue(
    "  completed {Sys.time()} ({nrow(imp$loggedEvents)} logged events)"
  ))
  derive_analysis_dat(imp, telemetry_vars)
}

daily_primary <- impute_sample(min_waves = 0)
daily_restricted <- impute_sample(min_waves = 15)
```

Split each imputation into the analysis datasets (`.imp > 0`) and the
non-imputed slice (`.imp == 0`, used for the observed-vs-imputed diagnostic
and complete-case analyses):

```{r}
#| label: post-imputation-centering
#| code-summary: "Show code (Split imputed and non-imputed frames)"

# Primary sample: all eligible participants (preregistered imputation target).
dat <- daily_primary |> filter(.imp > 0)
dat_desc <- dat |> filter(.imp == 1)
dat_complete <- daily_primary |> filter(.imp == 0)

# Restricted sample: >=15-survey subsample, for S4 and S2 only.
dat_restricted <- daily_restricted |> filter(.imp > 0)
dat_restricted_complete <- daily_restricted |> filter(.imp == 0)

message(glue(
  "Primary: {n_distinct(dat$pid)} participants, {nrow(dat) / m_imputations} rows/imputation. ",
  "Restricted: {n_distinct(dat_restricted$pid)} participants."
))
```

## Exported Objects

```{r}
#| label: export
#| code-summary: "Show code (Export objects for modelling, sensitivity, and the manuscript)"

source("R/targets/export.R")
dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  imputation_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(imputation_export_names)} objects to data/exports/"))
```
