---
title: |
  All BANG, little buck: Basic psychological needs are weakly linked with video gaming behavior
abstract: |
  Psychological theories of media use often assume that subjective motivation affects observable behavior. Using video games as a test case, we examine this assumption by pairing repeated self-reports of motivation with objective digital trace data at scale. Across two datasets comprising tens of thousands of hours of gaming behavior, we test predictions derived from self-determination theory and the Basic Needs in Games (BANG) model, which posit that autonomy, competence, and relatedness experiences drive engagement. Study A (preregistered) pairs daily diary surveys with 30 days of multi-platform digital trace data from 1,217 U.S. players. Study B (exploratory) examines 102k sessions from 9k PowerWash Simulator players, linking in-game experience prompts to behavioral logs. In both studies, need satisfaction was robustly associated with subjective states but showed weak or null associations with short-term gaming behavior, including subsequent play, session length, and return latency, across extensive preregistered and robustness analyses. These findings reveal a substantial motivation--behavior gap and suggest that SDT-based accounts may overestimate the role of need satisfaction in explaining when or how much people play. Data and code are available under a {{< meta data-license >}} license at {{< meta data-url >}}.
author:
  - name: Nick Ballou
    corresponding: true
    orcid: 0000-0003-4126-0696
    email: nick@nickballou.com
    affiliations: [ref: 1, ref: 2]
    roles: [conceptualization, data curation, investigation, methodology, formal analysis, visualization, writing, editing]
  - name: Tamás Andrei Földes
    corresponding: false
    orcid: 0000-0002-0623-9149
    email: tamas.foldes@oii.ox.ac.uk
    affiliations: [ref: 2]
    roles: [data curation, methodology, validation, editing]
  - name: Matti Vuorre
    corresponding: false
    orcid: 0000-0001-5052-066X
    email: mjvuorre@uvt.nl
    affiliations: [ref: 3]
    roles: [methodology, funding acquisition, editing]
  - name: Thomas Hakman
    corresponding: false
    orcid: 0009-0009-8292-2482
    email: thomas.hakman@oii.ox.ac.uk
    affiliations: [ref: 2]
    roles: [investigation, data curation, editing]
  - name: Kristoffer Magnusson
    corresponding: false
    orcid: 0000-0003-0713-0556
    affiliations: [ref: 4, ref: 2]
    roles: [software, editing]
  - name: Andrew K Przybylski
    corresponding: true
    orcid: 0000-0001-5547-2185
    email: andy.przybylski@oii.ox.ac.uk
    affiliations: [ref: 2]
    roles: [conceptualization, funding acquisition, project administration, editing]
affiliations:
  - id: 1
    name: Imperial College London
  - id: 2
    name: University of Oxford
  - id: 3
    name: Tilburg University
  - id: 4
    name: Karolinska Institute
csl: https://www.zotero.org/styles/apa
bibliography: references.bib
keywords: [motivation, digital trace data, video games, self-determination theory, displacement, compensatory behavior]
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: right
    number-sections: true
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    embed-resources: false
  docx:
    echo: false
  preprint-typst:
    echo: false
    wordcount: true
    theme: jou
    citeproc: true
    mainfont: "Liberation Serif"
    sansfont: "Liberation Sans"
    include-before-body:
      - text: "#show <refs>: set par(hanging-indent: 1.4em)"
knitr:
  opts_chunk:
    warning: false
    message: false
    fig-width: 6
    fig-asp: 0.618
    out-width: 80%
    fig-align: center
data-license: CC0
data-url: https://doi.org/10.5281/zenodo.18352505
---

<!--
NOTE: this document is the manuscript + appendix. It reads every computed
object from the targets pipeline (preprocessing / imputation / modelling /
sensitivity / studyb) via tar_load(); it fits no models itself. The model
fitting (H1-H3 diagnostics, S1-S9 sensitivity models) lives in modelling.qmd
and sensitivity.qmd.
-->

```{r}
#| label: libraries
#| code-summary: "Show code (Load required R packages)"

library(tidyverse)
library(glue)
library(glmmTMB)
library(lme4)
library(mice)
library(splines)
library(marginaleffects)
library(broom.mixed)
library(modelsummary)
library(psych)
library(tinytable)
library(patchwork)
library(ggridges)
library(ggdist)
library(scales)
library(janitor)
library(targets)
```

```{r}
#| label: setup
#| code-summary: "Show code (Presentation constants and pipeline inputs)"

set.seed(8675309)
options(scipen = 999)

theme_set(theme_minimal())
theme_update(
  plot.background = element_rect(fill = "white", color = NA),
  panel.background = element_rect(fill = "white", color = NA),
  strip.background = element_rect(fill = "black"),
  strip.text = element_text(color = "white", size = 10),
  axis.text = element_text(color = "black", size = 10),
  panel.grid.minor = element_blank(),
  panel.border = element_rect(colour = "black", fill = NA, linewidth = 1)
)

source("R/helpers.R") # colors, labels, and reporting helpers
source("R/targets/imputation.R") # build_wide_survey(), setup_mice_inputs()

tar_load(c(
  surveys,
  intake,
  hourly_telemetry,
  daily_telemetry,
  activity_categories,
  dat,
  dat_desc,
  dat_complete,
  dat_restricted,
  m_imputations,
  h1_pooled,
  h1mod,
  h1_restricted_pooled,
  h1_cc_pooled,
  h2_pooled,
  h2mod,
  h2_restricted_pooled,
  h2_cc_pooled,
  h3_pooled,
  h3mod,
  h3_restricted_pooled,
  h3_cc_pooled,
  pws_m1,
  pws_m2,
  pws_wide,
  pws_n_players,
  pws_n_sessions,
  # appendix / S1-S9 (from sensitivity.qmd)
  sens1_pooled,
  sens1b_pooled,
  sens1c_pooled,
  s2_bayes_fixed,
  s2_h2a_pooled,
  s2_h2b_pooled,
  sens3_pooled,
  sample_results,
  sens5b_pooled,
  sens8_linear,
  sens8_spline,
  sens9_h2_aut,
  sens9_h2_com,
  sens9_h2_rel,
  sens10_pooled,
  s10_pooled
))

full_eligible_pids <- unique(surveys$pid)
pws_n_players_fmt <- scales::comma(pws_n_players)
pws_n_sessions_fmt <- scales::comma(pws_n_sessions)
```

# Introduction

Digital technology use constitutes one of the domains in which behavior is most directly observable. Digital media (1) are widely used---upwards of half of adults and nearly all children in the UK and US regularly play video games [@EntertainmentSoftwareAssociation20242024; @Ofcom2023Online]; (2) generate digital trace data (automatically logged histories of user behavior), and (3) affect the health of at least some users in important ways, both for better and for worse [@GranicEtAl2014benefits; @BallouEtAl2024How]. These putative impacts of media use behavior on health are of interest to users, industry professionals, policymakers, clinicians, and families, but research to date has had limited success supporting these groups [@Ballou2023Manifesto]. Among other difficulties, progress has been stymied by three challenges: (1) accessing granular behavioral data, (2) measuring mental health with sufficient temporal detail, and (3) aligning theory with growing evidence that effects relate primarily to the quality, rather than quantity, of play [@BallouDeterding2024Basic; @Buchi2024Digital; @Orben2022Digital].

Digital trace data addresses several of these challenges. Compared to self-report, trace data provides greater detail about what, when and how much people play while alleviating concerns about recall biases [@ErnalaEtAl2020How; @KahnEtAl2014why; @ParryEtAl2021systematic]. However, three key limitations remain. First, while gaming companies collect player data at scale [@El-NasrEtAl2021Game], these data are rarely accessible to independent researchers. Where access has been negotiated or engineered via open source methods, it typically covers just one game or platform. While single-game studies can offer high depth and detail, they are potentially a small part of a person's gaming diet---engaged UK and US players use an average of 2.8 platforms [@BallouEtAl2025Perceived]. Given this, we advocate for openly available digital trace data spanning both single-game studies and multi-platform data access to understand holistic effects.

Second, while trace data is often richly longitudinal, it has to date only been paired with wellbeing surveys consisting of either a single measurement wave [@BallouEtAl2025Perceived; @JohannesEtAl2021Video] or waves separated by multiple weeks [@LarrieuEtAl2023How; @VuorreEtAl2022Time]. Early evidence suggests gaming effects may materialize and dissipate within 6 hours [@VuorreEtAl2023Affective; @BallouEtAl2025Perceived], and subjective wellbeing varies substantially across a day [@LuhmannEtAl2021Subjective]. Experience sampling and daily diary methods, embraced in social media research [@AalbersEtAl2021Caught; @SiebersEtAl2021Explaining], are needed to capture nuanced, short-lived effects and to better differentiate within- and between-person relationships [@JohannesEtAl2024How].

Third, effects of gaming are likely nuanced and contextual, but existing research lacks strong theoretical frameworks to guide investigation. Studies using digital trace data have ruled out simple playtime--wellbeing relationships [@BallouEtAl2024Registered; @JohannesEtAl2021Video; @VuorreEtAl2022Time; @LarrieuEtAl2023How; @BallouEtAl2025Perceived], supporting calls to move beyond quantity-focused approaches [@BallouEtAl2025How]. To do so, we need theory-driven predictions about how psychological states relate to gaming behavior itself—what motivates people to play in the first place, and how daily fluctuations in wellbeing shape engagement patterns. Self-Determination Theory [SDT, @Ryan2023Oxforda] offers such a framework, proposing that satisfaction of basic psychological needs---autonomy, competence, and relatedness---drives motivated behavior including media use. Understanding whether and when people choose to play games may depend critically on their experiences of needs satisfaction in daily life, yet the majority of studies that have tested these behavioral predictions did so without access to intensive longitudinal data [e.g., @BenderGentile2019internet; @AllenAnderson2018satisfaction].

Together, these gaps point to clear next steps: collect digital trace data in the form of both comprehensive multi-platform records and single-game, granular interactions; pair it with high-resolution, repeated wellbeing measurements; and use this data for theory-driven investigations of play quality and context. These are the aims of the present study.

::: {#nte-stage2 .callout-note}
## Relationship to the Stage 1 Registered Report

The introduction and method of this Stage 2 report differ substantially in wording and structure from the accepted Stage 1 Programmatic Registered Report [@BallouEtAl2025Psychological]. The Stage 1 introduction was written to motivate three planned Stage 2 outputs at once---covering basic needs, sleep, and genre differences---and its deliberately broad framing does not cohere as the introduction to any single study. We have therefore rewritten it to focus on the basic-needs hypotheses tested here. These changes are textual and organisational: the hypotheses (H1--H3), their operationalisations, and the confirmatory analysis plan are unchanged from Stage 1, and none of the revisions were informed by the results. A fully annotated version of the manuscript, giving the rationale for each substantive change, is provided in the supplementary materials.
:::

# Self-determination theory

Self-determination theory [@RyanDeci2017Selfdetermination] proposes three innate and universal psychological needs: the need for autonomy (to feel in control over one’s life and volitional in one’s actions), competence (to act effectively and exert mastery in the world), and relatedness (to feel that one is valued by others and values them in return). These basic psychological needs are theorized to be direct antecedents of intrinsic and autonomous motivation, as well as vital nutriments required for a person to live a fully functional life [@Ryan2023Oxford]. Across the environments we inhabit and activities we perform, these needs can be either satisfied or frustrated [@VansteenkisteEtAl2020basic]. 

There has been substantial research into how games and other entertainment media can support basic psychological needs [@PrzybylskiEtAl2010motivational; @TyackMekler2020Selfdetermination]. Games are adept at satisfying all three basic needs; games that better satisfy needs are more engaging; and having one’s needs satisfied during gaming is associated with better mental health outcomes during and after play [@ReerQuandt2020Digital; @TyackMekler2020Selfdetermination; @VellaJohnson2012Flourishing]. A large body of work supports that basic need satisfaction supports intrinsic motivation, and intrinsic motivation translates to higher self-reported behavioral engagement [@RyanEtAl2022We]. 

## The Basic Needs in Games (BANG) Model

The Basic Needs in Games (BANG) model of video game play and mental health [@BallouDeterding2024Basic] builds upon the core SDT principle that any action’s impact on mental health is mediated by the extent to which it satisfies or frustrates basic psychological needs. By differentiating between playtime and quality of play, BANG seeks to explain seemingly conflicting earlier findings that playtime itself is largely unrelated to wellbeing, but that some players do experience meaningful benefits or harms from their video game play. 

To date, however, BANG remains largely untested. Hence, the goal of this study is to test several key BANG hypotheses. We label the hypotheses of the current study in numerical order (e.g., H1) but also provide the numbered label from the original paper (e.g., B6) for clarity of potential falsification.

### The Relationship Between Basic Needs in Games and Global Basic Needs (H1)

Following the hierarchical model of intrinsic and extrinsic motivation [@Vallerand1997Hierarchical], BANG conceives of basic needs as operating at three levels of generality: situational (a particular gaming session), contextual (gaming as a whole), and global (one’s life in general). Experiences at lower levels of generality feed into and co-constitute higher levels---experiences with games are one (greater or lesser) element of one's life overall. 

A positive relationship between need satisfaction in games and overall need satisfaction is well-established in prior literature [@AllenAnderson2018satisfaction; @BallouEtAl2024Basic; @BradtEtAl2024Are]. BANG (B6) formalizes this relationship, proposing that need satisfaction experienced during gaming sessions contributes to overall need satisfaction in life. Thus, BANG hypothesizes:

*H1. When individuals’ in-game needs are better satisfied, they report greater overall need satisfaction.*

### Expectations (H2a)

Early articulations of SDT propose that goal or activity selection is (intrinsically) motivated by the 'awareness of potential satisfaction' of basic psychological needs or 'expectations about the satisfaction of those [salient] motives' [@DeciRyan1985Intrinsic, p. 231--239]. Need-related outcome expectations are closely related to intrinsic motivation [perhaps even forming part of the computational machinery underlying motivation @MurayamaJach2023critique], and the behavioral product of these expectations is therefore greater behavioral engagement. 

Expectations have, perhaps surprisingly, not featured prominently in subsequent empirical work; most gaming and media use-related SDT work focuses on need satisfaction or frustration as the experiential consequence of media consumption [@BallouDeterding2023Basic]. Need experiences can explain loops of self-sustaining activity, but cannot explain initial selective exposure to gaming where the activity has not commenced. 

BANG proposes that experiences of need satisfaction during a particular gaming session positively affect players' expectations for future need satisfaction with the current game, similar games, and gaming as a whole. This prediction is grounded in reports that expected need frustration is reported to modulate both initial and continued gaming exposure [@BallouDeterding2023Just], and in broader findings that outcome expectations are a strong predictor of continued media engagement [@ChangEtAl2014effects; @KocakAlanEtAl2022Replaying; @LaroseEtAl2001Understanding]. From BANG (B8), we therefore derive the following hypothesis:

*H2a. When individuals’ in-game need satisfaction is higher, they are more likely to play video games in the 24-hour period after survey completion.*

### Compensation (H2b)

SDT predicts that (global) need frustration results in compensatory behavior---people attempt to replenish needs that are not being met by altering their behavior [e.g., @SheldonEtAl2011twoprocess]. The potent need satisfaction offered by games constitute one way for people to compensate, particularly those who are highly engaged with gaming and have high gaming literacy [@BallouEtAl2022People]. The so-called "need density hypothesis" predicts that problematic or disordered gaming is most likely to occur when a person experiences high need satisfaction in games and high need frustration in other life domains [@RigbyRyan2011glued]. In other words, problematic gaming is theorized to occur, at least for some, due to a negative feedback loop whereby compensation occurs and becomes maladaptive such that the person's other compensatory tools besides gaming are progressively diminished. Several studies have found support for the need density hypothesis account [@BradtEtAl2024Are; @AllenAnderson2018satisfaction; @MillsEtAl2018exploring]. 

BANG operationalizes this compensatory play via intrinsic motivation. Frustrated needs in one’s life in general make opportunities to fulfill those needs more salient, which---all else equal---manifests phenomenologically as a stronger preference towards activities that satisfy the frustrated need(s). Given this, we hypothesize in the context of our sample of moderately to highly-engaged video game players (derived from BANG Hypothesis 9):

*H2b. When individuals’ global need frustration is higher, they are more likely to play video games in the 24-hour period after survey completion.* 

### Displacement (H3)

Playtime, BANG argues, only becomes problematic when it displaces other activities essential to the maintenance of need satisfaction in life overall. Commonly proposed problematic displacements are work/school responsibilities [@DrummondSauer2020Timesplitters], personal relationships [@DomahidiEtAl2018Longitudinal], and physical health or sleep [@KingEtAl2013impact]. Displacing these essential activities would thereby reduce global need satisfaction. Thus, BANG (B5) hypothesizes:

*H3. When a person’s most recent gaming is reported to displace a core life domain (work/school, social engagements, sleep/eating/fitness, or caretaking), their global need satisfaction is lower.*

# Study A: Preregistered Analysis of Multi-Platform Digital Trace Data and Daily Surveys

Study A was pre-registered on the Open Science Framework (OSF) in the form of a Stage 1 Programmatic Registered Report [@BallouEtAl2025Psychological] at *Peer Community In: Registered Reports*. The present Study A corresponds to Study 1 in the programmatic Registered Report; two other preregistered Stage 2 outputs, focused on sleep (Registered Report Study 2) and genres (Registered Report Study 3), respectively, are forthcoming. 

All data and analysis code are available on Zenodo ({{< meta data-url >}}).

## Study A Method

::: {.place arguments='top, scope: "parent", float: true'}

```{r}
#| label: tbl-platforms
#| code-summary: "Show code (Create platform details table)"
#| tbl-cap: "Platform Details"

tibble(
  Platform = c(
    "Nintendo",
    "Xbox",
    "Steam"
  ),
  `Data Source` = c(
    "Data-sharing agreements with Nintendo of America",
    "Data-sharing agreement with Microsoft",
    "Custom web app (Gameplay.Science)"
  ),
  `Account Linking Process` = c(
    "Participants shared an identifier contained within a QR code on the Nintendo web interface. Nintendo of America uses this identifier to retrieve gameplay data and share it with the research team.",
    "Participants consented to data sharing by opting in to the study on Xbox Insiders with their Xbox account. Microsoft retrieved and shared pseudonymized gameplay data for all consented accounts.",
    "Using a web app we developed (https://gameplay.science), participants consented to have their gameplay data monitored for the duration of the study. Authentication uses the official Steam API (OpenID)."
  ),
  `Type of Data Collected` = c(
    "Session records (what game was played, at what time, for how long) for first-party games only (games published in whole or in part by Nintendo).",
    "Session records (what game was played, at what time, for how long). Game titles were replaced with a random persistent identifier, but genre(s) and age ratings are shared.",
    "Hourly aggregates per game (every hour, the total time spent playing each game during the previous hour)"
  )
) |>
  tt(
    escape = TRUE,
    notes = list(
      "a" = list(
        i = 1,
        j = 3,
        text = "See https://accounts.nintendo.com/qrcode."
      ),
      "b" = list(
        i = 1,
        j = 4,
        text = "Nintendo-published games accounted for 63% of Switch playtime in our sample."
      ),
      "c" = list(
        i = 2,
        j = 3,
        text = "See https://support.xbox.com/en-US/help/account-profile/manage-account/guide-to-insider-program."
      )
    )
  ) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE, align = "c")
```

:::

### Design

The data for this study comprise a subset of the data from the Open Play study [@BallouEtAl2025Open], version 1.2.5. In the Open Play study, participants provided access to automated records of their gaming history on one or more platforms (Xbox, Steam, Nintendo Switch, iOS, Android) and completed an intake survey followed by a 30-day daily diary study. The intake survey included demographic questions and baseline measures of wellbeing. Daily data was collected between Oct 2024 and Aug 2025. 

Participants were recruited in collaboration with two panel providers, Prolific and PureProfile. Participants were eligible if they were aged 18 or older, resided in the United States, self-reported playing video games for at least 1 hour per week with ≥50% of that gaming taking place on eligible platforms (Nintendo, Xbox, and Steam), and successfully linked at least one gaming account on Xbox, Steam, and/or Nintendo Switch with validated recent digital trace data. iOS and Android data were collected but are not used in this analysis. For full details of the recruitment procedures and study methodology, see [@BallouEtAl2025Open].

### Ethics

This study received ethical approval from the Social Sciences and Humanities Inter-Divisional Research Ethics Committee at the University of Oxford (OII_CIA_23_107). All participants provided informed consent at the start of the study, including consent to their data being shared openly for reanalysis.

Participants were paid at an average rate of £12/hour, equating to: £0.20 for a 1-minute screening, £2 for the 10-minute intake survey (plus £5 for linking at least one account with recent data), £0.80 for each 4-minute daily survey. Participants received a £10 bonus payment for completing at least 24 out of 30 daily surveys.

### Sample Size Justification 

As specified in the Stage 1 Registered Report, sample size was determined by feasibility/resources rather than a formal power analysis, with an initial target of recruiting up to 1,000 U.S. participants into the diary component, with ~30% expected attrition. Sensitivity analyses showed that this sample size was sufficient to estimate target associations with moderate precision (95% CI spanning .13 scale points on a 7-point scale) (https://github.com/digital-wellbeing/platform-study-rr).

### Participant Inclusion/Exclusion Criteria

All eligibility and exclusion criteria were specified prior to data analysis in Stage 1 and/or documented as deviations in @tbl-deviations. Participants were eligible if they were aged 18+, resided in the U.S., reported playing video games at least 1 hour/week, reported that a substantial share of their gaming occurred on eligible platforms (Nintendo/Xbox/Steam), and successfully linked at least one eligible account with validated recent digital trace data. As documented, two eligibility thresholds were adjusted for feasibility relative to Stage 1: the platform-share requirement was lowered (75% → 50%), and the recent valid trace requirement was extended (7 days → 14 days).

Following the preregistered plan, the primary analyses impute and analyse all eligible participants who completed at least one daily survey. Because imputing a near-complete diary series for participants who responded on only a handful of days is a strong assumption, we also report each hypothesis test on the subsample of participants who completed at least 15 surveys (>=50% of the diary period; @tbl-deviations, @tbl-s4-results) and on complete cases only.

### Participants

```{r}
#| label: participants
#| code-summary: "Show code (Calculate participant statistics and response rates)"

# >=15-survey subsample (used in the sample-construction sensitivity analysis)
subsample_pids <- surveys |>
  filter(diaries_completed >= 15) |>
  distinct(pid) |>
  pull(pid)

# Prepare participant data with collapsed categories. Every eligible
# participant is in the primary sample; `in_subsample` flags the >=15 subset.
participant_data <- intake |>
  filter(pid %in% full_eligible_pids) |>
  mutate(
    # Collapse gender to main categories
    gender = ifelse(
      gender %in% c("Man", "Woman"),
      gender,
      "Other gender identity"
    ),
    # Collapse ethnicity to main categories
    ethnicity_collapsed = case_when(
      str_detect(ethnicity, "White") ~ "White",
      str_detect(
        ethnicity,
        "Black|African American|African, Caribbean"
      ) ~ "Black/African American",
      str_detect(ethnicity, "Asian") ~ "Asian",
      str_detect(ethnicity, "Two or More|Mixed") ~ "Multiracial",
      is.na(ethnicity) ~ NA_character_,
      TRUE ~ "Other"
    ),
    # Collapse education to main levels
    education_collapsed = case_when(
      str_detect(
        edu_level,
        "Less than|No formal|Primary"
      ) ~ "Less than high school",
      str_detect(
        edu_level,
        "High school|Secondary School|GCSE|Some college|Some University"
      ) ~ "High school or some college",
      str_detect(edu_level, "Associate") ~ "Associate degree",
      str_detect(
        edu_level,
        "Bachelor|University Bachelors"
      ) ~ "Bachelor's degree",
      str_detect(
        edu_level,
        "Master|Graduate|professional degree|doctoral|post-graduate"
      ) ~ "Graduate degree",
      is.na(edu_level) ~ NA_character_,
      TRUE ~ "Other"
    ),
    in_subsample = pid %in% subsample_pids
  ) |>
  select(
    pid,
    in_subsample,
    age,
    gender,
    ethnicity_collapsed,
    education_collapsed,
    self_reported_weekly_play,
    diaries_completed
  )

# Sample sizes for text
n_primary <- nrow(participant_data)
n_subsample <- sum(participant_data$in_subsample)

# Gender summary for the primary sample (for text)
gender_primary <- participant_data |>
  count(gender) |>
  mutate(pct = round(100 * n / sum(n), 1))

pull_pct <- function(g) gender_primary |> filter(gender == g) |> pull(pct)
gender_summary <- glue(
  "{pull_pct('Man')}% men, {pull_pct('Woman')}% women, ",
  "{pull_pct('Other gender identity')}% other gender identities"
)
```

```{r}
#| label: tbl-participants
#| tbl-cap: "Participant characteristics by sample"
#| code-summary: "Show code (Generate participant demographics table)"

# Build table. "Primary sample" is every eligible participant; the subsample
# column is the >=15-survey subset (a subset of, not disjoint from, the first).
sub <- participant_data$in_subsample

summary_table <- bind_rows(
  # Sample sizes
  tibble(
    Characteristic = "**N**",
    `Primary sample` = as.character(n_primary),
    `≥15-survey subsample` = as.character(n_subsample)
  ),

  # Age
  tibble(
    Characteristic = "Age (years)",
    `Primary sample` = format_mean_sd(participant_data$age),
    `≥15-survey subsample` = format_mean_sd(participant_data$age[sub])
  ),

  # Categorical demographics
  create_categorical_section(
    participant_data,
    "gender",
    "Gender",
    c("Man", "Woman", "Other gender identity")
  ),

  create_categorical_section(
    participant_data,
    "ethnicity_collapsed",
    "Ethnicity",
    c("White", "Black/African American", "Asian", "Multiracial", "Other")
  ),

  create_categorical_section(
    participant_data,
    "education_collapsed",
    "Education",
    c(
      "Less than high school",
      "High school or some college",
      "Associate degree",
      "Bachelor's degree",
      "Graduate degree"
    )
  ),

  # Gaming behavior section
  tibble(
    Characteristic = "**Gaming behavior**",
    `Primary sample` = "",
    `≥15-survey subsample` = ""
  ),

  tibble(
    Characteristic = "Weekly play (hours)",
    `Primary sample` = format_mean_sd(
      participant_data$self_reported_weekly_play / 60
    ),
    `≥15-survey subsample` = format_mean_sd(
      participant_data$self_reported_weekly_play[sub] / 60
    )
  ),

  # Study engagement section
  tibble(
    Characteristic = "**Study engagement**",
    `Primary sample` = "",
    `≥15-survey subsample` = ""
  ),

  tibble(
    Characteristic = "Surveys completed",
    `Primary sample` = format_mean_sd(participant_data$diaries_completed),
    `≥15-survey subsample` = format_mean_sd(
      participant_data$diaries_completed[sub]
    )
  )
)

# Identify rows for styling
header_rows <- which(
  str_detect(summary_table$Characteristic, "^\\*\\*") |
    (summary_table$`Primary sample` == "" &
      summary_table$`≥15-survey subsample` == "")
)
indent_rows <- which(str_detect(summary_table$Characteristic, "^    "))

# Create table
summary_table |>
  tt(
    notes = "Values are M (SD) or N (%). Ethnicity and education categories collapsed to main levels for clarity. The >=15-survey subsample is a subset of the primary sample, used for sensitivity analyses."
  ) |>
  format_tt(j = 1, markdown = TRUE) |>
  style_tt(i = header_rows, bold = TRUE) |>
  format_tt(i = header_rows, j = 1, fn = function(x) {
    str_remove_all(x, "\\*\\*")
  }) |>
  style_tt(i = indent_rows, j = 1, indent = 1) |>
  format_tt(i = indent_rows, j = 1, fn = function(x) str_trim(x)) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

The primary sample comprised `r n_primary` participants (`r gender_summary`) who completed at least one daily survey. Of these, `r n_subsample` completed at least 15 surveys; this subsample is used for the sample-construction sensitivity analyses.

### Measures

```{r}
#| label: psychometrics
#| code-summary: "Show code (Calculate reliability for all scales)"
#| output: false

omega_global_ns <- number(
  omega(
    surveys |> select(bpnsfs_1, bpnsfs_3, bpnsfs_5),
    plot = FALSE
  )$omega.tot,
  .01
)
omega_global_nf <- number(
  omega(
    surveys |> select(bpnsfs_2, bpnsfs_4, bpnsfs_6),
    plot = FALSE
  )$omega.tot,
  .01
)

omega_game_ns <- number(
  omega(
    surveys |> select(bangs_1, bangs_3, bangs_5),
    plot = FALSE
  )$omega.tot,
  .01
)
omega_game_nf <- number(
  omega(
    surveys |> select(bangs_2, bangs_4, bangs_6),
    plot = FALSE
  )$omega.tot,
  .01
)

# proportion of surveys with subsequent play

prop_subsequent_play <- number(
  nrow(surveys[surveys$telemetry_played_any_24h, ]) / nrow(surveys) * 100,
  .1
)
minutes_subsequent_play <- number(
  mean(surveys$play_minutes_24h, na.rm = TRUE),
  1
)
sd_minutes_subsequent_play <- number(
  sd(surveys$play_minutes_24h, na.rm = TRUE),
  1
)

# total hours per platform during 30-day study period

platform_hours <- daily_telemetry |>
  mutate(day_local_date = as.Date(day_local)) |>
  inner_join(
    surveys |>
      select(pid, date, wave) |>
      distinct() |>
      mutate(
        date_only = as.Date(date),
        wave_num = as.numeric(as.character(wave))
      ) |>
      filter(wave_num <= 30),
    by = c("pid", "day_local_date" = "date_only"),
    relationship = "many-to-many"
  ) |>
  group_by(platform) |>
  summarise(total_hours = sum(minutes, na.rm = TRUE) / 60, .groups = "drop")

hours_nintendo <- number(
  platform_hours |> filter(platform == "Nintendo") |> pull(total_hours),
  1,
  big.mark = ","
)
hours_xbox <- number(
  platform_hours |> filter(platform == "Xbox") |> pull(total_hours),
  1,
  big.mark = ","
)
hours_steam <- number(
  platform_hours |> filter(platform == "Steam") |> pull(total_hours),
  1,
  big.mark = ","
)
```

The measures used in this paper are detailed below, with descriptive statistics shown in @tbl-descriptives. For other measures in the Open Play study not used here, we refer readers to the Open Play codebook [@BallouEtAl2025Open]. 

*Need satisfaction in games*. We measured need satisfaction and frustration in games during the most recent gaming session using 3 items from an abbreviated version of the Basic Psychological Need Satisfaction in Gaming Scale [BANGS, @BallouDeterding2024Basic]. The BANGS assesses autonomy, competence, and relatedness need satisfaction with three items for each need; we selected the highest-loading item for each need for our brief daily measure (e.g., relatedness satisfaction: "I felt I formed relationships with other players and/or characters."). Participants rated each item on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree). We calculated mean scores for need satisfaction by averaging all three items. Reliability of the composite 3-item need satisfaction index was assessed using McDonald’s omega total ($\omega_t$ = `r omega_game_ns` for need satisfaction, $\omega_t$ `r omega_game_nf` for need frustration). As needs are conceptually distinct, we expect lower reliability for the composite index than for unidimensional scales.

*Need satisfaction and frustration in daily life*. We measured need satisfaction and frustration in daily life ("global need satisfaction and frustration") during the previous 24 hours using the brief version of the Basic Psychological Need Satisfaction and Frustration Scale [@ChenEtAl2015Basic; @MartelaRyan2024Assessing]. This scale includes 6 items, with one item for need satisfaction and one item for need frustration for each of the three needs (e.g., "Today ... I was able to do things that I really want and value in life"). Participants rated each item on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree). We calculated mean scores for need satisfaction and need frustration by averaging the relevant items. Reliability of the composite 3-item need satisfaction index was assessed using McDonald’s omega total ($\omega_t$ = `r omega_global_ns` for need satisfaction; $\omega_t$ = `r omega_global_nf` for need frustration). As needs are conceptually distinct, we expect lower reliability for this composite index than for unidimensional scales.

*Video game playtime*. We measured video game playtime using digital trace data collected from participants' gaming accounts on Xbox, Steam, and Nintendo Switch. During the 30-day study period, we recorded a total of `r hours_nintendo` hours of play on Nintendo Switch, `r hours_xbox` hours on Xbox, and `r hours_steam` hours on Steam. For each daily survey, we calculated total minutes played in the 24-hour period following survey completion. We also created a binary variable indicating whether any play occurred during this period. On average, `r prop_subsequent_play`% of surveys were followed by any play in the subsequent 24 hours, with a mean of `r minutes_subsequent_play` minutes (SD = `r sd_minutes_subsequent_play`).

*Displacement*: We measured displacement of core life domains via an open text field asking participants about the hypothetical alternative activity: "Think back to your most recent gaming session. If you hadn't played a game, what would you most likely have done instead?" Using Qwen3-4b-instruct [@qwen3technicalreport], we coded participant responses based on whether they mentioned any of the following activities: work/school responsibilities, social engagements, sleep/eating/fitness, or caretaking---so-called "core life domains". We refined the LLM prompt through 5 iterations of manual verification of 100 random coded responses. We created a boolean variable indicating whether any core life domain was hypothetically displaced. Full materials are provided in the supplement, including the exact LLM prompt used for classification, all raw participant responses, coded outputs, manual verification results, and reproducible code.

::: {.place arguments='top, scope: "parent", float: true'}

```{r}
#| label: tbl-descriptives
#| tbl-cap: "Descriptive statistics for primary Study A and Study B variables, decomposed into between- and within-person components."
#| code-summary: "Show code (Build multilevel descriptive statistics table)"

# Decompose a variable's variance into between- and within-person components,
# using the same var()-based approach as fig-descriptives panel B
describe_multilevel <- function(value, pid) {
  value <- as.numeric(value)
  var_total <- var(value, na.rm = TRUE)
  var_between <- var(tapply(value, pid, mean, na.rm = TRUE), na.rm = TRUE)
  var_within <- var_total - var_between

  tibble(
    M = mean(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    sd_total = sqrt(var_total),
    sd_between = sqrt(var_between),
    sd_within = sqrt(var_within),
    icc1 = var_between / var_total
  )
}

desc_vars_a <- tribble(
  ~var                       , ~Variable                     , ~is_pct ,
  "game_ns"                  , "Game need satisfaction"      , FALSE   ,
  "global_ns"                , "Global need satisfaction"    , FALSE   ,
  "global_nf"                , "Global need frustration"     , FALSE   ,
  "play_minutes_24h"         , "Playtime, next 24h (min)"    , FALSE   ,
  "telemetry_played_any_24h" , "Any play, next 24h (%)"      , TRUE    ,
  "displaced_core_domain"    , "Displaced a core domain (%)" , TRUE
) |>
  mutate(stats = map(var, ~ describe_multilevel(dat_desc[[.x]], dat_desc$pid)))

desc_vars_b <- tribble(
  ~var             , ~Variable                , ~is_pct ,
  "game_ns"        , "Game need satisfaction" , FALSE   ,
  "session_length" , "Session length (min)"   , FALSE   ,
  "session_gap"    , "Session gap (hrs)"      , FALSE
) |>
  mutate(stats = map(var, ~ describe_multilevel(pws_wide[[.x]], pws_wide$pid)))

desc_table <- bind_rows(
  `Study A` = desc_vars_a,
  `Study B` = desc_vars_b,
  .id = "study"
) |>
  unnest(stats) |>
  mutate(
    scale = if_else(is_pct, 100, 1),
    accuracy = if_else(is_pct, 0.1, 0.01),
    M = number(M * scale, accuracy),
    Median = number(median * scale, accuracy),
    `SD (Total)` = number(sd_total * scale, accuracy),
    `SD (Between)` = number(sd_between * scale, accuracy),
    `SD (Within)` = number(sd_within * scale, accuracy),
    `ICC(1)` = number(icc1, 0.01)
  ) |>
  select(
    study,
    Variable,
    M,
    `Median`,
    `SD (Total)`,
    `SD (Between)`,
    `SD (Within)`,
    `ICC(1)`
  )

group_rows <- list(
  "Study A" = 1,
  "Study B" = nrow(desc_vars_a) + 1
)

desc_table |>
  select(-study) |>
  tt(
    notes = "SD (Total) is pooled across all observations (person-days in Study A, sessions in Study B); SD (Between) is the SD of person-level means; SD (Within) is the residual person-mean-centered SD. ICC(1) = between-person variance / total variance. Game need satisfaction is on a 1-7 scale in both studies. Study A playtime is in minutes; Study A binary variables are shown as percentages. Study B session length is in minutes and session gap in hours.",
    width = .85
  ) |>
  group_tt(i = group_rows) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

:::

### Data Exclusions

Consistent with Stage 1, we applied preregistered exclusions to telemetry records prior to analysis: we excluded telemetry days with >16 hours total logged play across linked platforms, sessions >8 hours, and sessions logged in the future (indicating logging error or system-clock manipulation). We also excluded survey responses failing the preregistered attention check (duplicate need item responses differing by >1 scale point). As part of preregistered data quality processing, we removed background sessions. No additional exclusion criteria beyond those preregistered were introduced.

### Imputation

```{r}
#| label: imputation-missingness
#| code-summary: "Show code (Quantify missingness for the imputation prose)"

# Reconstruct the MICE where-matrix (same functions the imputation stage
# uses) for the primary sample and the >=15 subsample, purely to report
# missingness rates.
miss_pct <- function(min_waves) {
  sw <- build_wide_survey(surveys, min_waves = min_waves)
  where <- setup_mice_inputs(sw)$where
  scales::number(100 * mean(where), 0.1)
}
overall_miss_pct <- miss_pct(0)
subsample_miss_pct <- miss_pct(15)

# FMI (fraction of missing information) for the focal within-person terms,
# from mice::pool(). Reported as the range across H1/H2/H3.
focal_fmi <- c(
  h1_pooled$pooled$fmi[h1_pooled$pooled$term == "game_ns_cw"],
  h2_pooled$pooled$fmi[h2_pooled$pooled$term == "global_nf_cw"],
  h3_pooled$pooled$fmi[
    h3_pooled$pooled$term == "displaced_core_domainTRUE"
  ]
)
fmi_range <- glue(
  "{scales::number(min(focal_fmi), .001)}--{scales::number(max(focal_fmi), .001)}"
)
```

We used multiple imputation by chained equations (MICE, M = `r m_imputations`) with predictive mean matching for the need satisfaction/frustration items (BPNSFS, BANGS) and displacement measures. The preregistered plan imputes and analyses all eligible participants; because many participants completed few surveys, missingness in the primary sample is high (`r overall_miss_pct`% of imputable cells, versus `r subsample_miss_pct`% in the >=15-survey subsample). Digital trace data were not imputed because tracking was continuous and automatic; missing data represent recorded absence of play. Models were fit separately to each imputed dataset and pooled by Rubin's rules using the `mice` package [@vanBuurenGroothuis-Oudshoorn2011mice].

Because the play outcome for H2 is objective trace data, the fraction of missing information for the focal day-level coefficients is low despite the high cell-level missingness (`r fmi_range` across H1--H3), so `r m_imputations` imputations are sufficient [@VonHippel2020How]. For every hypothesis we report the preregistered primary analysis alongside the >=15-survey subsample and complete-case analyses (@tbl-s4-results); where these diverge in statistical significance we say so explicitly.

### Deviations from Preregistration

We made several deviations from our preregistration to ensure we could recruit enough high-quality participants to meet our sample size goals. In our view, none are so severe enough to threaten the validity of the study. Deviations are summarized in @tbl-deviations.

Our handling of missing data follows the preregistered plan: multiple imputation of all eligible participants. An earlier version of this Stage 2 report restricted the primary analyses to participants who completed at least 15 surveys; following review, that restriction is now reported only as a sensitivity analysis (@tbl-s4-results).

::: {.place arguments='top, scope: "parent", float: true'}

```{r}
#| label: tbl-deviations
#| code-summary: "Show code (Create table of preregistration deviations)"
#| tbl-cap: "Summary of deviations from preregistration"

tibble(
  `Study Aspect` = c(
    "Data collection",
    "Data collection",
    "Data collection",
    "Data collection",
    "Data collection",
    "Data collection"
  ),
  Preregistered = c(
    "All participants sourced from PureProfile",
    "Screening sample would be nationally representative by ethnicity and gender",
    "Sample consists of participants aged 18--30",
    "To qualify, >=75% of a participant's total gaming must take place on platforms included in the study (Xbox, Steam, Nintendo Switch)",
    "Qualification contingent upon valid digital trace data within last 7 days",
    "Daily surveys sent at 7pm local time"
  ),
  Actual = c(
    "Participants sourced from both PureProfile and Prolific",
    "Approximately 50% of screening was done using quotas for national representativeness by ethnicity and gender; all subsequent sampling used convenience sampling with no quotas",
    "Sample consists of participants aged 18-40",
    "To qualify, >=50% of a participant's total gaming must take place on platforms included in the study (Xbox, Steam, Nintendo Switch)",
    "Qualification contingent upon valid digital trace data within last 14 days",
    "Daily surveys sent at 2pm local time"
  ),
  `Justification for Deviation` = c(
    "Exhausted PureProfile participant pool before reaching required sample size",
    "Exhausted participant pools of smaller demographic categories on both Prolific and PureProfile before reaching required sample size",
    "(1) Unable to recruit enough participants in the US aged 18--30",
    "Low rates of study qualification at 75% threshold, in large part due to substantial uncaptured Playstation play",
    "Feedback from participants indicating that play during a 7-day period was subject to too many fluctuations (e.g., a busy workweek)",
    "Feedback from participants indicating that evening plans often interfered with survey completion and thus adversely affected response rate"
  )
) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE, align = "c")
```

:::

### Positive Controls

```{r}
#| label: positive-controls
#| code-summary: "Show code (Test positive controls)"

# Use first imputation for positive control check
cor_playtime <- cor.test(
  dat$self_reported_weekly_play[dat$.imp == 1],
  dat$play_minutes_24h[dat$.imp == 1],
  method = "pearson"
)

cor_playtime_inline <- glue(
  "r = {number(cor_playtime$estimate, .01)}, 95% CI [{number(cor_playtime$conf.int[1], .01)}, {number(cor_playtime$conf.int[2], .01)}]"
)

cor_lifesat <- cor.test(
  rowMeans(surveys[, c("bpnsfs_1", "bpnsfs_3", "bpnsfs_5")], na.rm = FALSE),
  surveys$life_sat,
  method = "pearson"
)

cor_lifesat_inline <- glue(
  "r = {number(cor_lifesat$estimate, .01)}, 95% CI [{number(cor_lifesat$conf.int[1], .01)}, {number(cor_lifesat$conf.int[2], .01)}]"
)
```

As specified in the preregistration, we assessed three positive controls designed to assess whether our data were capable of addressing our stated hypotheses. All three passed: self-reported playtime correlated positively with logged playtime (`r cor_playtime_inline`); global need satisfaction correlated positively with life satisfaction (`r cor_lifesat_inline`); and after preprocessing (e.g., to remove background sessions), there were no overlapping sessions. We therefore proceeded with the planned analyses.

### Analysis Approach

We tested each hypothesis using multilevel within-between regression models estimated with `glmmTMB` [@BrooksEtAl2017glmmTMB]. Focal predictors were within-person mean-centered, with 30-day person means included to separate day-level from 30-day aggregate associations. All models included random intercepts and AR(1) autocorrelation structures; H1 and H3 additionally included random slopes for day-level predictors, while H2 used random intercepts only due to convergence issues with the binary outcome. H2 uses a logistic link, so its coefficients are reported throughout as odds ratios (with 95% CIs obtained by exponentiating the Wald interval); H1 and H3 coefficients are on the response scale. No demographic covariates were included, as the within-between specification controls for all time-invariant individual differences.

This approach isolates day-to-day dynamics: day-level coefficients estimate how much a person's outcome deviates from their own 30-day average when their predictor deviates from their own 30-day average. For example, H1's day-level coefficient answers: 'On days when individuals experience better game need satisfaction than their typical level, do they report higher global need satisfaction than their typical level?' The non-focal 30-day aggregate coefficients capture whether people with generally higher predictor levels also have generally higher outcomes across the study period. Random effects account for stable individual differences (e.g., personality, gaming preferences), and the AR(1) term models temporal autocorrelation in daily data. This specification does not adjust for time-varying confounds; estimates should be interpreted as associations rather than causal effects.

## Study A Results: Confirmatory

We present visualizations for each hypothesis test in turn; all key estimates are summarized @tbl-main-results.

### H1. Greater in-game need satisfaction is associated with greater global need satisfaction

```{r}
#| label: tbl-h1-results
#| include: false
#| code-summary: "Show code (Extract H1 estimates for inline text)"

# Extract estimates for narrative reporting
h1_summary <- summary(h1_pooled) |> as_tibble()
h1_ests <- report_wb_estimate(
  h1_summary,
  "game_ns_cw",
  "game_ns_cb",
  accuracy = 0.01
)

# Individual variables for inline reporting
h1_day_est <- h1_ests$day_level
h1_day_coef <- h1_ests$day_coef
h1_agg_est <- h1_ests$aggregate
h1_agg_coef <- h1_ests$agg_coef

h1_results <- h1_summary |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    term = ifelse(term %in% names(labels), labels[term], term),
    across(c(estimate, std.error, statistic), ~ round(.x, 3))
  )

h1_sensitivity <- report_sample_sensitivity(
  h1_pooled, h1_restricted_pooled, h1_cc_pooled, "game_ns_cw"
)
```

::: {.place arguments='top, scope: "parent", float: true'}

```{r}
#| label: fig-h1-predictions
#| fig-cap: "Estimated global need satisfaction as a function of need satisfaction in games (H1). Individual trajectories shown as gray lines, population-level association shown as blue line with 95% confidence ribbon."
#| code-summary: "Show code (Plot H1)"

plot_relationship(
  model = h1mod,
  x_var = "game_ns_cw",
  x_label = labels["game_ns"],
  y_label = labels["global_ns"],
  color = colors$game_ns,
  n_keepers = 100,
  within_vars = c("game_ns_cw"),
  between_vars = c("game_ns_cb")
)
```

:::

Results strongly support H1 (@fig-h1-predictions). At the day level, game need satisfaction was positively associated with global need satisfaction (B = `r h1_day_est`). On days when participants experienced game need satisfaction 1 scale point (1--7 scale) above their personal 30-day average, they reported global need satisfaction `r h1_day_coef` units above their personal 30-day average. 

At the 30-day aggregate level, which was not the focus of our hypothesis about day-to-day dynamics, the association (B = `r h1_agg_est`) was strong, indicating strong between-individual differences.

The day-level association was essentially unchanged in the subsample and complete-case analyses (`r h1_sensitivity`).

### H2. Situational need satisfaction is positively associated with the likelihood of playing in the period after survey completion (H2a), while global need frustration is negatively associated (H2b)

```{r}
#| label: h2-reporting
#| code-summary: "Show code (Extract H2 estimates for reporting)"

# Extract estimates for narrative reporting
h2_summary <- summary(h2_pooled) |> as_tibble()

# H2 uses a logistic model, so estimates are reported as odds ratios
# (exponentiate = TRUE): the point estimate and 95% CI are on the OR scale.

# H2a: Game need satisfaction
h2a_ests <- report_wb_estimate(
  h2_summary,
  "game_ns_cw",
  "game_ns_cb",
  accuracy = 0.01,
  stat_label = "z",
  exponentiate = TRUE
)
h2a_day_est <- h2a_ests$day_level
h2a_day_coef <- h2a_ests$day_coef
h2a_agg_est <- h2a_ests$aggregate
h2a_agg_coef <- h2a_ests$agg_coef

# H2b: Global need frustration
h2b_ests <- report_wb_estimate(
  h2_summary,
  "global_nf_cw",
  "global_nf_cb",
  accuracy = 0.01,
  stat_label = "z",
  exponentiate = TRUE
)
h2b_day_est <- h2b_ests$day_level
h2b_day_coef <- h2b_ests$day_coef
h2b_agg_est <- h2b_ests$aggregate
h2b_agg_coef <- h2b_ests$agg_coef

# Primary / >=15-subsample / complete-case comparison (odds ratios) and FMI,
# for the sentences reported alongside H2a and H2b.
h2a_sensitivity <- report_sample_sensitivity(
  h2_pooled, h2_restricted_pooled, h2_cc_pooled, "game_ns_cw", exponentiate = TRUE
)
h2b_sensitivity <- report_sample_sensitivity(
  h2_pooled, h2_restricted_pooled, h2_cc_pooled, "global_nf_cw", exponentiate = TRUE
)
h2b_primary_ep <- report_estimate_p(h2_pooled, "global_nf_cw", exponentiate = TRUE)
h2b_sub_ep <- report_estimate_p(
  h2_restricted_pooled, "global_nf_cw", exponentiate = TRUE
)
h2b_fmi <- scales::number(
  h2_pooled$pooled$fmi[h2_pooled$pooled$term == "global_nf_cw"], .001
)

pull_p <- function(pooled, term_name) {
  summary(pooled) |> as_tibble() |> filter(term == term_name) |> pull(p.value)
}
sig_phrase <- function(p) {
  if (p < 0.05) "was statistically significant" else "was not statistically significant"
}
h2b_primary_sig <- sig_phrase(pull_p(h2_pooled, "global_nf_cw"))
h2b_sub_sig <- sig_phrase(pull_p(h2_restricted_pooled, "global_nf_cw"))
```

```{r}
#| label: h2-sensitivity-reporting
#| include: false
#| code-summary: "Show code (Extract day-level H2 sensitivity estimates for inline text)"

# Day-level game NS / global NF estimates from each sensitivity model, as odds
# ratios (logistic models) unless noted. Point estimates only -- these back up
# the narrative claim that the focal associations stay near the null.

# S1: shorter post-survey windows (logistic)
s1_6h_gamens <- pooled_coef(sens1b_pooled, "game_ns_cw", exponentiate = TRUE)
s1_6h_globalnf <- pooled_coef(
  sens1b_pooled,
  "global_nf_cw",
  exponentiate = TRUE
)
s1_12h_gamens <- pooled_coef(sens1_pooled, "game_ns_cw", exponentiate = TRUE)
s1_12h_globalnf <- pooled_coef(
  sens1_pooled,
  "global_nf_cw",
  exponentiate = TRUE
)

# S2: one random slope at a time (logistic); take each focal term from the
# model that carries its matching random slope
s2_slopes_gamens <- pooled_coef(
  s2_h2a_pooled,
  "game_ns_cw",
  exponentiate = TRUE
)
s2_slopes_globalnf <- pooled_coef(
  s2_h2b_pooled,
  "global_nf_cw",
  exponentiate = TRUE
)

# S3: linear model of minutes played (Gaussian) -- raw coefficient in minutes,
# NOT an odds ratio
s3_gamens_b <- pooled_coef(sens3_pooled, "game_ns_cw")
s3_globalnf_b <- pooled_coef(sens3_pooled, "global_nf_cw")

# S4: complete cases and >=15-survey subsample (logistic), from the combined
# sample-robustness results
sample_or <- function(spec_name, term_name) {
  est <- sample_results |>
    filter(spec == spec_name, term == term_name) |>
    pull(estimate)
  number(exp(est), 0.01)
}
s4_cc_gamens <- sample_or("Complete cases", "game_ns_cw")
s4_cc_globalnf <- sample_or("Complete cases", "global_nf_cw")
s4_sub_gamens <- sample_or(">=15 subsample", "game_ns_cw")
s4_sub_globalnf <- sample_or(">=15 subsample", "global_nf_cw")

# S5: game NS x global NF interaction (logistic). The interaction term
# exponentiates to a ratio of odds ratios (how much the global NF OR shifts
# per 1-point higher game NS), not a plain OR.
s5_int_gamens <- pooled_coef(sens5b_pooled, "game_ns_cw", exponentiate = TRUE)
s5_int_globalnf <- pooled_coef(
  sens5b_pooled,
  "global_nf_cw",
  exponentiate = TRUE
)
s5_int_product <- pooled_coef(
  sens5b_pooled,
  "game_ns_cw:global_nf_cw",
  exponentiate = TRUE
)
```

::: {.place arguments='top, scope: "parent", float: true'}

```{r}
#| label: fig-h2-predictions
#| fig-cap: "Estimated probability of playing in subsequent 24 hours. (A) As a function of need satisfaction in games (H2a). (B) As a function of global need frustration (H2b). Individual trajectories shown as gray lines, population-level associations shown with 95% confidence ribbons."
#| code-summary: "Show code (Plot H2)"
#| fig-asp: 0.5

# Panel A: Game need satisfaction
p_h2a <- plot_relationship(
  model = h2mod,
  x_var = "game_ns_cw",
  x_label = labels["game_ns"],
  y_label = "Pr(played in subsequent 24h)",
  color = colors$game_ns,
  n_keepers = 50,
  within_vars = c("game_ns_cw", "global_nf_cw"),
  between_vars = c("game_ns_cb", "global_nf_cb")
)

# Panel B: Global need frustration
p_h2b <- plot_relationship(
  model = h2mod,
  x_var = "global_nf_cw",
  x_label = labels["global_nf"],
  y_label = "Pr(played in subsequent 24h)",
  color = colors$global_nf,
  n_keepers = 50,
  within_vars = c("game_ns_cw", "global_nf_cw"),
  between_vars = c("game_ns_cb", "global_nf_cb")
)

# Combine with patchwork and set y-axis limits to 0-100%
p_h2a +
  p_h2b +
  plot_annotation(tag_levels = "A") &
  coord_cartesian(ylim = c(0, 1)) &
  theme(plot.tag = element_text(face = "bold", size = 14))
```

:::

We tested H2a and H2b using a single multilevel within-between logistic regression, where in-game need satisfaction and global need frustration (each within- and between-person centered) predicted a binary variable whether any play happened in the 24-hour period after diary survey completion.

Because the outcome is binary, estimates are reported as odds ratios (OR), where 1 indicates no association.

**H2a.** Day-level game need satisfaction was not meaningfully associated with the odds of subsequent play (OR = `r h2a_day_est`; see @fig-h2-predictions), and this held in the subsample and complete-case analyses (`r h2a_sensitivity`). H2a was not supported.

**H2b.** Support for H2b was weak and not robust. In the preregistered primary analysis, higher day-level global need frustration was associated with slightly lower odds of subsequent play (OR = `r h2b_day_est`), a small effect that `r h2b_primary_sig` (`r h2b_primary_ep`). Restricted to the >=15-survey subsample, the same association `r h2b_sub_sig` (`r h2b_sub_ep`); the complete-case estimate was similar (OR = `r s4_cc_globalnf`). The fraction of missing information for this coefficient was `r h2b_fmi`, so the difference between the primary and restricted results reflects the larger sample rather than imputation noise. Because the effect is negligible and near-identical in magnitude across every specification while its statistical significance depends on which participants are included, we do not treat H2b as robustly supported.

We conducted a wide range of further sensitivity analyses. Key estimates for game need satisfaction (game NS) and global need frustration (global NF) remained small and, for the most part, indistinguishable from the null in models that:

- use subsequent 6 hours (game NS: OR = `r s1_6h_gamens`; global NF: OR = `r s1_6h_globalnf`) or 12 hours (game NS: OR = `r s1_12h_gamens`; global NF: OR = `r s1_12h_globalnf`) as the outcome, instead of 24 hours (Sensitivity Analysis 1)
- use alternative random slopes specifications (game NS: OR = `r s2_slopes_gamens`; global NF: OR = `r s2_slopes_globalnf`) (Sensitivity Analysis 2)
- use a linear model of minutes played in the subsequent 24 hours instead of binary play/no-play, where estimates are on the raw scale of minutes rather than odds ratios (game NS: B = `r s3_gamens_b`; global NF: B = `r s3_globalnf_b`) (Sensitivity Analysis 3)
- use complete case data or the >=15-survey subsample instead of the primary sample (complete case, game NS: OR = `r s4_cc_gamens`, global NF: OR = `r s4_cc_globalnf`; subsample, game NS: OR = `r s4_sub_gamens`, global NF: OR = `r s4_sub_globalnf`), and sweep the survey-completion threshold from 10 to 24 (Sensitivity Analysis 4)
- include an interaction between gaming need satisfaction and global need frustration (game NS: OR = `r s5_int_gamens`; global NF: OR = `r s5_int_globalnf`; game NS × global NF: ratio of ORs = `r s5_int_product`) (Sensitivity Analysis 5)
- use a spline term for gaming need satisfaction and global need frustration, instead of a linear term (Sensitivity Analysis 6)
- enter each individual need (autonomy, competence, relatedness) as predictors instead of composite need satisfaction or frustration (Sensitivity Analysis 7)

The 30-day aggregate associations (game need satisfaction: OR = `r h2a_agg_est`; global need frustration: OR = `r h2b_agg_est`) similarly indicate no relationship across individuals; these are reported as exploratory and unrelated to the focal hypotheses about short-term behavioral dynamics.

In short, we find no support for H2a and, at most, weak and fragile support for H2b: situational need satisfaction and global need frustration are at best negligibly associated with subsequent play behavior.

### H3. When gaming displaces a core life domain, global need satisfaction will be lower

```{r}
#| label: h3-displaced-categories
#| include: false
#| code-summary: "Show code (Calculate displaced activity category frequencies)"

# Calculate frequencies of each displaced activity category
# Use first imputation to avoid double-counting
activity_summary <- dat |>
  filter(.imp == 1, !is.na(displaced_core_domain)) |>
  left_join(
    activity_categories |> select(pid, wave, activity_label),
    by = c("pid", "wave")
  ) |>
  count(activity_label, displaced_core_domain) |>
  group_by(activity_label) |>
  mutate(
    pct = 100 * n / sum(n),
    total = sum(n)
  ) |>
  ungroup() |>
  arrange(desc(total))

# Get counts for core vs non-core
core_summary <- dat |>
  filter(.imp == 1, !is.na(displaced_core_domain)) |>
  count(displaced_core_domain) |>
  mutate(pct = 100 * n / sum(n))

# Store values for inline reporting (formatted)
total_responses <- scales::comma(sum(activity_summary$n))
n_core_raw <- core_summary |> filter(displaced_core_domain == TRUE) |> pull(n)
n_core <- scales::comma(n_core_raw)
pct_core <- round(
  core_summary |> filter(displaced_core_domain == TRUE) |> pull(pct),
  1
)

# Core domain specific counts
n_sleep <- scales::comma(
  activity_summary |>
    filter(activity_label == "sleep_eat_fitness") |>
    pull(total) |>
    first()
)

n_social <- scales::comma(
  activity_summary |>
    filter(activity_label == "social_engagement") |>
    pull(total) |>
    first()
)

n_work <- scales::comma(
  activity_summary |>
    filter(activity_label == "work_school") |>
    pull(total) |>
    first()
)

n_caretaking <- scales::comma(
  activity_summary |>
    filter(activity_label == "caretaking") |>
    pull(total) |>
    first()
)

# Non-core category counts for informal mention
n_digital_media <- scales::comma(
  activity_summary |>
    filter(activity_label == "other_digital_media") |>
    pull(total) |>
    first()
)

n_other_leisure <- scales::comma(
  activity_summary |>
    filter(activity_label == "other_leisure") |>
    pull(total) |>
    first()
)
```

```{r}
#| label: h3-reporting
#| code-summary: "Show code (Extract H3 estimates for reporting)"

# Extract estimates for narrative reporting
h3_summary <- summary(h3_pooled) |> as_tibble()
h3_ests <- report_wb_estimate(
  h3_summary,
  "displaced_core_domainTRUE",
  term_cb = NULL,
  accuracy = 0.01
)

h3_est <- h3_ests$day_level
h3_coef <- h3_ests$day_coef

h3_sensitivity <- report_sample_sensitivity(
  h3_pooled,
  h3_restricted_pooled,
  h3_cc_pooled,
  "displaced_core_domainTRUE"
)
```

::: {.place arguments='top, scope: "parent", float: true'}

```{r}
#| label: fig-h3-predictions
#| fig-cap: "Global need satisfaction when gaming was reported to displace vs. not displace a core life domain. Plot shows distribution (histogram) and mean with 80% and 95% quantile intervals."
#| code-summary: "Show code (Plot H3: displaced activity categories vs global NS)"
#| out-width: 60%

# Get raw data from first imputation for visualization
h3_data <- dat |>
  filter(.imp == 1, !is.na(displaced_core_domain)) |>
  mutate(
    displacement_label = if_else(
      displaced_core_domain,
      "Displaced core domain",
      "Displaced non-core domain"
    ),
    x_numeric = if_else(displaced_core_domain, 2, 1)
  )

# Calculate means for each group (to match what stat_histinterval will show)
h3_means <- h3_data |>
  group_by(x_numeric, displacement_label) |>
  summarise(mean_ns = mean(global_ns, na.rm = TRUE), .groups = "drop")

ggplot(h3_data, aes(x = x_numeric, y = global_ns)) +
  # Raincloud plot with asymmetric histograms
  stat_histinterval(
    data = h3_data |> filter(!displaced_core_domain),
    aes(fill = displacement_label),
    slab_alpha = 0.5,
    point_interval = mean_qi,
    breaks = seq(1, 7, by = .4),
    interval_color = "black",
    point_color = "black",
    point_size = 3,
    slab_fill = colors$global_ns,
    side = "left"
  ) +
  stat_histinterval(
    data = h3_data |> filter(displaced_core_domain),
    aes(fill = displacement_label),
    slab_alpha = 0.5,
    point_interval = mean_qi,
    breaks = seq(1, 7, by = .4),
    interval_color = "black",
    point_color = "black",
    point_size = 3,
    slab_fill = colors$global_ns,
    side = "right"
  ) +
  # Line connecting the mean point estimates
  geom_line(
    data = h3_means,
    aes(x = x_numeric, y = mean_ns),
    color = "black",
    linewidth = 0.8,
    linetype = "solid"
  ) +
  scale_x_continuous(
    breaks = c(1, 2),
    labels = c("Displaced non-core\ndomain", "Displaced core\ndomain")
  ) +
  scale_y_continuous(
    breaks = 1:7,
    limits = c(1, 7)
  ) +
  labs(
    x = NULL,
    y = labels["global_ns"]
  ) +
  theme(
    axis.text.x = element_text(size = 11),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  )
```

:::

Participants reported what activity their gaming session displaced `r total_responses` times across the study. In `r n_core` cases (`r pct_core`%), gaming displaced a core life domain: sleep, eating, or fitness (*n* = `r n_sleep`), social engagements (*n* = `r n_social`), work or school (*n* = `r n_work`), or caretaking (*n* = `r n_caretaking`). Gaming most commonly displaced non-core activities such as other digital media use (*n* = `r n_digital_media`) and other leisure activities (*n* = `r n_other_leisure`).

Results provide very weak support for H3 (B = `r h3_est`). When gaming displaced a core life domain rather than a non-core activity, participants reported global need satisfaction `r h3_coef` units lower on average. On a 7-point scale, this difference is extremely small, and the distributions of global need satisfaction when gaming displaced core vs. non-core domains are nearly identical (@fig-h3-predictions). The estimate was similarly small in the subsample and complete-case analyses (`r h3_sensitivity`).

An exploratory analysis (Appendix Sensitivity Analysis 9) examined whether this relationship differed for specific displaced life domains. Results showed that need satisfaction was lower when gaming displaced work/school responsibilities and sleep/eating/fitness, but---contrary to expectations---tended to be higher when gaming displaced social engagements or caretaking. 

```{r}
#| label: tbl-main-results
#| tbl-cap: "Summary of main hypothesis tests (H1-H3)"
#| code-summary: "Show code (Create combined results table)"

# Combine all three hypothesis results into one table. H1 and H3 are linear,
# so Estimate is a raw coefficient; H2 is logistic, so it additionally gets an
# odds-ratio column (exp of the estimate and of its Wald 95% CI).
h1_combined <- summary(h1_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    Hypothesis = glue(
      "{labels[str_remove(term, '_cw$')]} → global need satisfaction"
    ),
    test_stat = "t",
    or_ci = ""
  )

h2_combined <- summary(h2_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    Hypothesis = glue("{labels[str_remove(term, '_cw$')]} → play"),
    test_stat = "z",
    or_ci = glue(
      "{number(exp(estimate), 0.01)} ",
      "[{number(exp(estimate - 1.96 * std.error), 0.01)}, ",
      "{number(exp(estimate + 1.96 * std.error), 0.01)}]"
    )
  )

h3_combined <- summary(h3_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)") |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    Hypothesis = "Displaced core domain → global need satisfaction",
    test_stat = "t",
    or_ci = ""
  )

# Combine and format
bind_rows(h1_combined, h2_combined, h3_combined) |>
  mutate(
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    ),
    # Create combined test statistic column with appropriate label
    test_result = glue("{statistic} ({test_stat})")
  ) |>
  select(
    Hypothesis,
    Estimate = estimate,
    SE = std.error,
    `OR [95% CI]` = or_ci,
    `Statistic` = test_result,
    `p` = p.value
  ) |>
  tt(
    notes = "Preregistered primary analysis (all eligible participants, multiple imputation). Estimate is a raw coefficient; H2 has a binary outcome (logistic model) and the OR column gives the odds ratio and its 95% CI. Estimates for the >=15-survey subsample and for complete cases are reported in the text and in Table S4."
  ) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

# Study B: Exploratory Evidence from PowerWash Simulator

## Study B Method

To assess whether our findings generalize beyond the Open Play dataset, we conducted a secondary analysis of data from *PowerWash Simulator* (PWS) [@VuorreEtAl2023intensivea]. PWS is a first-person simulation game where players use pressure washers to clean various objects. The PWS dataset complements the Open Play data because it is highly granular: players were prompted during gameplay to rate their experiences of autonomy, competence, focus, wellbeing, immersion, and enjoyment on 0-100 scales, on average once every 10 minutes throughout a play session. We linked these ratings to play behavior extracted from game logs.

The original study procedures were granted ethical approval by Oxford University’s Central University Research Ethics Committee (SSH_OII_CIA_21_011).

### Participants

The characteristics of the full sample of 11,080 players in the PWS dataset are described in @VuorreEtAl2023intensivea; here, we briefly describe the subset of data relevant to our questions. All participants in the original study were over 18 years old and provided informed consent; for inclusion in Study B here participants also needed to have answered at least one mood prompt. The median age was 27 (19, 40; 1st and 9th deciles), and the four most frequent gender responses were Male (4,537, 52.2%), Female (2,675, 30.8%), Non-binary (723, 8.3%), and Transgender (326, 3.7%). Participants were resident in 39 countries, with the USA (4,917, 56.5%), UK (840, 9.7%), Canada (448, 5.2%), and Germany (390, 4.5%) being the most represented. Recruitment happened in multiple waves through multiple avenues inside and outside of the game. Study participation was incentivized through cosmetic in-game rewards (e.g., item skins). 

### Measures

*Play sessions* were defined as continuous periods of activity separated by gaps in engagement of at least 30 minutes, yielding `r pws_n_sessions_fmt` sessions across `r pws_n_players_fmt` players. Based on the session timestamps, we calculated two behavioral outcomes: session length (minutes) and session gap (hours; defined as the end timestamp of the previous session and the start timestamp of the subsequent one). 

*Need satisfaction* was measured via two in-game prompts on a visual analogue scale from 0 to 100: an autonomy item "Just now, I was doing the things I really wanted to in Powerwash Simulator” and a competence item "Just now, I felt competent playing PowerWash Simulator", each with visual analogue scale endpoints "Not at all" and "As much as possible". We converted each observation to a 1--7 scale to match Study A's BANGS items. For each session, we took the mean of all autonomy and competence ratings to generate a single need satisfaction indicator (analogously to Study A) and decomposed it into within- and between-person components.

### Analysis Approach

Analogously to Study A, we estimated the relationship between need satisfaction and outcomes (session length, session gap) using linear mixed effects models, with random intercepts and slopes for each participant. Outcomes were log-transformed due to heavily right-skewed distributions. Following our main analysis approach, we decomposed need satisfaction predictors into within- and between-person components and controlled for previous session length and session gap to isolate need satisfaction effects.

```{r}
#| label: studyb-reporting
#| code-summary: "Show code (Study B predictions and reporting)"

pred_m1 <- predictions(
  pws_m1,
  newdata = datagrid(
    model = pws_m1,
    game_ns_cw = c(0, 6),
    game_ns_cb = 0,
    prev_session_length = mean(pws_wide$prev_session_length, na.rm = TRUE)
  ),
  re.form = NA
) |>
  as_tibble() |>
  arrange(game_ns_cw) |>
  mutate(
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high)
  )

pws_m1_max_eff <- pred_m1 |>
  summarise(
    est = diff(estimate),
    lo = diff(conf.low),
    hi = diff(conf.high)
  ) |>
  transmute(
    glue(
      "{number(est, accuracy = 0.1)} minutes ",
      "[95% CI {number(lo, accuracy = 0.1)}, ",
      "{number(hi, accuracy = 0.1)}]"
    )
  ) |>
  pull()

pred_m2 <- predictions(
  pws_m2,
  newdata = datagrid(
    model = pws_m2,
    game_ns_cw = c(0, 6),
    game_ns_cb = 0,
    prev_session_gap = mean(pws_wide$prev_session_gap, na.rm = TRUE)
  ),
  re.form = NA
) |>
  as_tibble() |>
  arrange(game_ns_cw) |>
  mutate(
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high)
  )

pws_m2_max_eff <- pred_m2 |>
  summarise(
    est = diff(estimate),
    lo = diff(conf.low),
    hi = diff(conf.high)
  ) |>
  transmute(
    glue(
      "{number(est, accuracy = 0.1)} hours ",
      "[95% CI {number(lo, accuracy = 0.1)}, ",
      "{number(hi, accuracy = 0.1)}]"
    )
  ) |>
  pull()

pws_m1_est <- report_lmer_term(pws_m1, "game_ns_cw", p_method = "wald_z")
pws_m2_est <- report_lmer_term(pws_m2, "game_ns_cw", p_method = "wald_z")

game_ns_sd <- number(sd(pws_wide$game_ns_cw, na.rm = TRUE), .01)
```

::: {.place arguments='top, scope: "parent", float: true'}

```{r}
#| label: fig-study2-results
#| fig-cap: "Relationship between session-to-session fluctuations in need satisfaction and play behavior in PowerWash Simulator. (A) Session length. (B) Time to next session. Shaded regions show 95% confidence intervals. The x-axis spans the largest observed positive and negative within-person deviations in need satisfaction."
#| code-summary: "Show code (Visualize PWS relationships)"
#| fig-asp: 0.36

# Generate predictions for session length
pred_m1 <- marginaleffects::predictions(
  pws_m1,
  newdata = datagrid(
    game_ns_cw = seq(
      min(pws_wide$game_ns_cw, na.rm = TRUE),
      max(pws_wide$game_ns_cw, na.rm = TRUE),
      length.out = 100
    ),
    game_ns_cb = 0,
    prev_session_length = mean(pws_wide$prev_session_length, na.rm = TRUE)
  ),
  re.form = NA
) |>
  as_tibble() |>
  mutate(
    # Back-transform from log scale to original scale (minutes)
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high)
  )

# Generate predictions for session gap
pred_m2 <- marginaleffects::predictions(
  pws_m2,
  newdata = datagrid(
    game_ns_cw = seq(
      min(pws_wide$game_ns_cw, na.rm = TRUE),
      max(pws_wide$game_ns_cw, na.rm = TRUE),
      length.out = 100
    ),
    game_ns_cb = 0,
    prev_session_gap = mean(pws_wide$prev_session_gap, na.rm = TRUE)
  ),
  re.form = NA
) |>
  as_tibble() |>
  mutate(
    # Back-transform from log scale to original scale (hours)
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high)
  )

# Panel A: Session length
p_m1 <- ggplot(pred_m1, aes(x = game_ns_cw, y = estimate)) +
  geom_ribbon(
    aes(ymin = conf.low, ymax = conf.high),
    alpha = 0.2,
    fill = colors$game_ns
  ) +
  geom_line(color = colors$game_ns, linewidth = 1) +
  scale_y_log10(
    breaks = scales::breaks_log(n = 6),
    labels = scales::label_number()
  ) +
  labs(
    x = labels["game_ns"],
    y = "Session length (minutes)"
  )

# Panel B: Session gap
p_m2 <- ggplot(pred_m2, aes(x = game_ns_cw, y = estimate)) +
  geom_ribbon(
    aes(ymin = conf.low, ymax = conf.high),
    alpha = 0.2,
    fill = colors$global_ns
  ) +
  geom_line(color = colors$global_ns, linewidth = 1) +
  scale_y_log10(
    breaks = scales::breaks_log(n = 6),
    labels = scales::label_number()
  ) +
  labs(
    x = labels["game_ns"],
    y = "Time to next session (hours)"
  )

# Combine panels
p_m1 +
  p_m2 +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(face = "bold", size = 14))
```

:::

## Study B Results: Exploratory

Results are shown in @fig-study2-results. At the session level, game need satisfaction was weakly and non-significantly correlated with session length (B = `r pws_m1_est`). Panel A illustrates that when players experienced higher need satisfaction than their personal average, they did not play meaningfully longer: if a player who typically reported need satisfaction of 1 instead reported a 7, their expected change in session length would be only `r pws_m1_max_eff`.

Similarly, game need satisfaction showed a weak association with time to next session (B = `r pws_m2_est`). Panel B shows that if a player who typically reported need satisfaction of 1 instead reported a 7, their next session would begin `r pws_m2_max_eff` sooner than usual. While this association is significant, given that typical session-to-session deviations in need satisfaction are much smaller (within-person SD = `r game_ns_sd` points), we interpret the practical relevance to behavior as small.

Broadly, results therefore converge with Study A: Despite examining `r pws_n_sessions_fmt` sessions from `r pws_n_players_fmt` players in a different game using different measures, the pattern of weak behavioral associations replicated. Full model outputs are provided in the Supplement.

# Discussion

Across Study A and Study B, our findings reveal a consistent pattern: basic psychological needs---whether satisfied in games or frustrated in daily life---show weak or null relationships with subsequent gaming behavior. This apparent disconnect between self-reported and behavioral outcomes has important implications. Self-determination theory, particularly as applied to games, has been extensively validated using self-report measures. Players who report higher need satisfaction also report greater enjoyment, stronger intentions to continue playing, and better wellbeing outcomes [@TyackMekler2020Selfdetermination]; @AdinolfTurkay2019differences; @OliverEtAl2016video; @TamboriniEtAl2011Media; @FormosaEtAl2022Need; @TyackEtAl2020Restorative]. Our results do not challenge these relationships. Rather, they suggest that for individual players, the pathway from needs to actual behavior may be substantially weaker or more complex than the pathway from needs to self-reported experiences and intentions.

Our findings are not the first to report weak links between basic needs and gaming engagement as measured by digital trace data. Motivation was only very weakly associated with total engagement in *League of Legends* [@BruhlmannEtAl2020Motivational]. Competence satisfaction did not meaningfully relate to voluntary engagement in a custom RPG [@KaoEtAl2024How], and satisfaction of all three needs was only very weakly related to playtime in Animal Crossing: New Horizons and Plants vs Zombies: Battle for Neighborville over a 2-week timescale (r = .07, likely too small to be practically significant) [@JohannesEtAl2021Video]. We add to these findings with more comprehensive trace data (spanning 5 platforms in Study A and detailed single-game records in Study B) and higher-frequency wellbeing data. Given accumulating weak links between needs and behavior, we suggest several paths forward.

## Implications for the BANG model

Only one of BANG's predictions was supported (H1/B6: game needs are positively associated with global needs), consistent with prior literature [@AllenAnderson2018satisfaction; @BallouEtAl2024Basic] and the proposed hierarchical structure at the core of SDT [@Vallerand1997Hierarchical]. However, the behavioral predictions fared poorly. In-game positive experiences were unrelated to subsequent play (H2a), and self-reported displacement was negligibly related to wellbeing (H3). Global need frustration (H2b) was associated with a marginally lower probability of subsequent play in the preregistered analysis, but the effect was negligible in size and its statistical significance did not survive restriction to participants with more complete data, so we do not read it as compensatory play. All in all, BANG hypotheses B5, B8, and B9 were unsupported or, for H2b, at best weakly and inconsistently supported in our data.

Null results for theoretical predictions can generally be attributed to (1) lack of statistical power, (2) validity issues (e.g., poor design, poor measures), (3) incorrect auxiliary hypotheses, or (4) theory failure [@Meehl1990Why]. We argue that our study is reasonably well-powered [see @BallouEtAl2025Psychological for simulated sensitivity analyses], and with the exception of H3 whose "hypothetical displacement" measure has obvious flaws (see Limitations), uses valid measures---in particular, because we observe real-world behavior.

We endeavored to test one of the most prominent auxiliary hypotheses present, namely the auxiliary of correct timescale, by comparing 6-hour, 12-hour, and 24-hour time periods, and by triangulating using the PowerWash Simulator dataset, wherein need-related experiences are captured within the session itself. However, none were able to find meaningful support for the behavioral predictions. 

We therefore interpret our results as evidence against certain BANG predictions, necessitating model updating. From a metascientific perspective, model updating after falsification is central to iterative model calibration  and theory modulation [@Meehl1990Why], in which constructs are sharpened, measurement improved, and boundary conditions more precisely articulated. Updating BANG requires identifying *when* and *why* need-related processes do and do not relate to behavioral engagement. 

A wholesale revision of BANG is beyond the scope of the current paper, but our results suggest follow-up investigation should aimn to determine whether the null results here reflect (i) temporal misalignment [for example, it may be that need satisfaction updates expectations on a timescale longer than 24 hours, @BallouDeterding2023Just]; (ii) boundary conditions (for example, if need--behavior links emerge only for specific players, games, or contexts with low constraint and weak habitual control); or (iii) competing processes (for example, if habits, reinforcement histories, and situational affordances dominate short-term behavior, leaving needs to shape preferences rather than actions). Critically, if behavioral effects remain absent under conditions designed to maximise their detectability, BANG’s behavioral claims should be revised or removed rather than further insulated.

## Alternative behavioral frameworks

The modest associations we found between need experiences and subsequent play behavior suggest that basic psychological needs may not be the primary drivers of short-term gaming engagement. In light of this, we suggest player experience research consider other theoretical frameworks that might provide better or complementary explanations for short-term gaming engagement. We are aware of least three such frameworks.  

Behaviorist and reinforcement-learning accounts emphasize the power of recent rewards and environmental cues, rather than subjective motives, in sustaining behavior [@Skinner1965Science; @Niv2009Reinforcement]. Recent work has expanded and adapted these predictions for the digital media domain [@NorwoodEtAl2026Digital; @JamesTunney2017relationship; @JamesTunney2017need]. Under such models, a primary cause of players re-engaging is that the behavior has been reliably reinforced, not because they recently felt more autonomy, competence, or relatedness. 

Habit theory similarly predicts minimal coupling between momentary experiences and action. With sufficient repetition in stable contexts, gaming becomes cue-triggered and automatic, guided by procedural memory rather than conscious motivational states [@OuelletteWood1998Habit; @WoodRunger2016Psychology]. If players typically launch games at particular times or in response to specific cues, need fluctuations may exert little incremental influence over behavior.

A third possibility is regulatory cessation. In homeostatic and cybernetic models, behavior is energized by need- or goal-discrepancies and should weaken once these are reduced; highly satisfying engagement may therefore decrease the likelihood of immediate re-engagement [@Hull1943Principles; @Toates1986Motivational; @CarverScheier2001selfregulation]. Self-determination theory explicitly rejects this logic for psychological needs, arguing that need satisfaction does not produce satiation or motivational decline and may instead sustain intrinsic motivation [@SheldonGunz2009psychological]. However, SDT evidence has primarily relied on self-reported motivation rather than observed behavioral continuation, potentially obscuring homeostatic or satiation-like dynamics that operate at the level of action. In games research, where engagement unfolds as repeated consumption, such regulatory processes may better account for short-term disengagement following highly satisfying play episodes.

Each of these perspectives aligns with broader evidence that subjective intentions and experiences often predict real-world actions only weakly because behavior is multiply determined and heavily constrained by situational affordances [@SheeranWebb2016Intention]. For researchers, our findings therefore suggest that comprehensive models of gaming behavior may need to incorporate reinforcement histories, habits, and regulatory processes alongside need-based motivations [@SharpeEtAl2025Quantifying]. For game developers, they suggest that relying on experiential metrics (e.g., 'fun', satisfaction surveys) may provide an incomplete picture of what sustains engagement. For parents and clinicians, they suggest that efforts to promote healthier play patterns may benefit from structural interventions (e.g., increasing friction, modifying environment to reduce contextual cues) rather than focusing on enhancing need fulfilment.

## The value of open behavioral data

The introduction to this paper outlined three key limitations in gaming research: lack of researcher access to industry data, temporal mismatch between trace data and surveys, and weak theoretical frameworks. Our study addressed all three by negotiating multi-platform access, implementing daily diaries, and testing theory-driven predictions. Yet the clearest contribution may be demonstrating what becomes visible when self-report is paired with comprehensive behavioral records.

Self-report measures of play behavior commonly correlates with intrinsic motivation, and thereby higher engagement [@NeysEtAl2014exploring; @KosaUysal2024Exploration]. The trace data reveal a different picture. This disconnect is not unique to SDT or gaming; intention-behavior gaps are well-documented across health behaviors, environmental actions, and consumer choices [@SheeranWebb2016Intention]. Whether or not the underlying reasons are shared across these domains and media use, intention-behavior gaps are particularly consequential in a field where theoretical claims increasingly concern behavior, such as how much people play, when they play, what motivates them to start or stop.

The broader lesson extends beyond SDT. As gaming research matures beyond simple quantity-based approaches [@BallouEtAl2025How], theories must be validated against behavioral outcomes, not just self-reported proxies. Open player behavior data, sourced through a mix of player-led data sharing infrastructure, industry partnerships, and other mechanisms, is essential for this work. 

There are, however, practical barriers to making such behavioral evidence routine. Privacy and re-identification risks are non-trivial for high-resolution digital trace data, particularly when combined with survey responses, and these risks create understandable reluctance among both participants and data holders [@RocherEtAl2019Estimating]. Industry incentives also rarely align with open scientific practices: the most informative behavioral data are often commercially sensitive, operationally costly to extract, and legally complex to share across jurisdictions. Methodologically, the field also lacks shared standards for defining sessions, handling idle time, linking multi-platform identities, and documenting preprocessing decisions—each of which can meaningfully affect substantive conclusions.

We therefore advocate for multi-platform solutions, mixing both open source and, where possible with high transparency standards, industry collaborations. Multi-platform coverage matters substantively because platform ecosystems structure when and how people play. Different platforms afford different play contexts (e.g., portable vs. fixed-location play, solitary vs. social defaults, friction to launch, and typical session cadence), and these affordances can shift the distribution of sessions across the day and week. When studies observe only a single platform, they risk misclassifying a person’s true “non-play” periods (e.g., apparent disengagement on one platform may simply reflect switching to another), attenuating within-person associations and obscuring displacement dynamics. Single-platform datasets also risk overgeneralizing from idiosyncratic platform cultures and technical constraints (such as background processes, suspend/resume behavior, or account sharing) that can inflate or distort behavioral measures.

## Limitations and Future Directions

Several limitations qualify the interpretation of the present findings. First, although our analyses focus on within-person associations, these estimates should not be interpreted as causal effects [@RohrerMurayama2021These]. Even with high-frequency longitudinal measurement, within-person variation does not isolate exogenous change: need satisfaction may covary with unmeasured situational factors (e.g., time availability, fatigue, social context) that independently shape gaming behavior. Our results therefore speak to the strength of empirical coupling between needs and behavior, not to causal necessity or sufficiency.

Second, our test of displacement (H3) relies on a hypothetical counterfactual measure: what participants report they would have done had they not played. This approach is coarse and vulnerable to recall bias, rationalisation, and ambiguity in how respondents interpret "most likely" alternatives. While the measure provides a useful first pass at identifying potentially displaced life domains, it is ill-suited for detecting subtle or cumulative displacement processes and likely attenuates any true effects. More rigorous tests of displacement will require objective time-use data or designs that directly observe trade-offs between activities.

Third, the behavioral outcomes examined here reflect short-term engagement patterns, such as session length and return latency. Null or weak associations at this timescale do not rule out need-related effects on longer-term outcomes, such as game choice, persistence over months, or disengagement trajectories. Our conclusions are therefore limited to short-term behavioral dynamics and should not be generalized to all forms of gaming involvement.

Fourth, while the Study A data represent a substantial advancement in capturing comprehensive multi-platform data, they are nonetheless incomplete: players in our sample may have played games on Playstation, played third-party games on Nintendo, or played on mobile (which, while captured, was not captured in sufficient temporal resolution to inform the hypotheses here). Methods for reliably capturing data from each gaming platform require further development.

Fifth, following the preregistration, the primary analyses impute and analyse all eligible participants, including many who completed only a few surveys and whose diary responses are therefore largely imputed. Reassuringly, the day-level estimates were near-identical when the sample was restricted to higher-completion participants or to complete cases, and the fraction of missing information for the focal coefficients was low because the play outcome is observed trace data. The one exception is the borderline statistical significance of H2b, which we discuss above and do not over-interpret.

Finally, our sample, although purposively sampled for racial and gender diversity, should be understood as consisting of engaged 18--40 year old players willing to share detailed behavioral data and complete intensive surveys, rather than as representative of all players. This selectivity limits generalizability in two ways. First, casual players, younger adolescents, and individuals with minimal or highly irregular play patterns are underrepresented. Second, highly engaged players' behavior may differ systematically from those among less engaged populations (e.g,more routinized or more highly habit-driven). The weak need–behavior associations observed here may not generalize to all player groups, nor do they preclude stronger effects in populations with greater variability in motivation or fewer structural constraints.

Together, these limitations suggest that the present findings should be interpreted as strong evidence against large, general, short-term behavioral effects of need satisfaction among engaged adult players, rather than as definitive evidence against any role for psychological needs in shaping gaming behavior more broadly.

## Data Availability

All data, materials, and code related to the dataset and this manuscript are available under {{< meta data-license >}} at {{< meta data-url >}}.

## Funding

This research was supported by the UK Economic and Social Research Council (ES/W012626/1 and ES/Y010736/1). AP was supported by the Huo Family Foundation. 

## Conflicts of Interest

The authors declare no competing financial, intellectual, or institutional interests relevant to this research. The disclosures below are provided in the interest of full transparency.

All members of the research team have worked on scientific projects funded by government and charitable grants that used data from tech companies provided under a data-sharing agreement. No authors have received funding or compensation from the tech companies or other industries connected to the work presented here. 

MV has provided in-kind consultations and served as a nonpaid panel member for Meta and K-Games. AKP has served in advisory or expert roles for the Sync Digital Wellbeing Program (2022–2024), the Google Expert Advisory on Youth and Technology (2025), the OpenAI Expert Council on Well-Being and AI (2025), and UK Department for Science, Innovation and Technology–funded research on children’s smartphone and social media use (University of Cambridge, 2025). He is a member of the UK Department for Culture, Media & Sport College of Experts. Any industry fees are directly donated to charity, and his research is conducted in accordance with University of Oxford academic integrity policies.

Data-sharing partners had no role in the design, analysis, or publication of results. 

## Generative AI Use

We used Claude Code to implement and refactor some aspects of the analysis code, and Claude to edit and clarify (but not write initial drafts of) certain written content. We have verified all manuscript content to the best of our ability and take full responsibility for its accuracy. 

{{< pagebreak >}}

# Appendix

## Design Table

The following is the Design Table from the Stage 1 Registered Report [@BallouEtAl2025Psychological], reproduced verbatim with the addition of an Observed Outcome column. 

```{r}
#| label: tbl-design
#| tbl-cap: "Study A design table"
#| code-summary: "Show code (Design table)"

tibble(
  `Research Question` = c(
    "Does in-game need satisfaction contribute to overall need satisfaction?",
    "Do positive play experiences result in more frequent future play behavior?",
    "Do players compensate for frustrated needs using games?",
    "Is the displacement of core life domains more associated with harm than non-core domains?"
  ),
  Hypothesis = c(
    "H1. When individuals' in-game needs are better satisfied, they report greater global need satisfaction.",
    "H2a. When individuals' in-game need satisfaction is higher, they are more likely to play video games in the 24-hour period after survey completion.",
    "H2b. When individuals' global need frustration is higher, they are more likely to play video games in the 24-hour period after survey completion.",
    "H3. When a person's most recent gaming displaced a core life domain (work/school, social engagements, sleep/eating/fitness, or caretaking), their global need satisfaction will be lower."
  ),
  `Sampling Plan` = c(
    "1,000 US adults, completing a diary study over 30 days. The hypotheses in Study A are better-suited to the diary study data, and therefore do not use the panel data (and by extension, the UK sample). The telemetry data in Study A consists of Xbox, Nintendo, and Steam.",
    "",
    "",
    ""
  ),
  `Analysis Plan†` = c(
    "Multilevel within-between linear regression whereby within-person centered game-level need satisfaction (gameNS_cw) predicts deviation from a person's typical global need satisfaction (globalNS). glmmTMB(globalNS ~ gameNS_cw + gameNS_cb + (1 + gameNS_cw | pid) + ar1(day + 0 | pid))",
    "Multilevel logistic regression with the binary presence or absence of playtime in the subsequent 24 hours from survey completion as the outcome (playedLater), predicted by within-person centered in-game need satisfaction (gameNS_cw; H2a) and global need frustration (globalNF_cw; H2b). glmmTMB(playedLater ~ gameNS_cw + gameNS_cb + globalNF_cw + globalNF_cb + (1 + gameNS_cw + globalNF_cw | pid) + ar1(day + 0 | pid), family = binomial(link = \"logit\"))",
    "",
    "Multilevel linear regression predicting global need satisfaction (globalNS) from the presence or absence of the player's most recent gaming session having displaced a core life domain (displacedCoreDomain). glmmTMB(globalNS ~ displacedCoreDomain + (1 + displacedCoreDomain | pid) + ar1(day + 0 | pid))"
  ),
  `Rationale for deciding the sensitivity of the test for confirming or disconfirming the hypothesis` = c(
    "We did not conduct an a priori power analysis, as resource constraints dictated the maximum sample we could collect. The complexity of the data structure and lack of prior information about within-person playtime variance across days, effect size expectations, or meaningful smallest effect sizes of interests (SESOIs). Instead, we used simulated data to establish the approximate precision with which coefficients will eventually be estimated. In our assessment, these are sufficiently precise to be valuable and to differentiate statistical vs practical significance (see column right), but we leave further judgement to the reader.",
    "",
    "",
    ""
  ),
  `Interpretation given different outcomes` = c(
    "We will only interpret results subject to the data meeting the relevant positive controls specified: (1) a significant positive correlation between self-reported playtime and digital trace playtime, (2) no overlapping game sessions for a given individual on a particular platform, and (3) a significant positive correlation between global need satisfaction and life satisfaction. We will use statistical significance to determine whether the results support (p < .05) or fail to support (p > .05) the hypothesis. However, much greater emphasis will be placed on marginal outcomes, which we will contextualize in real-world terms so as to let readers make judgements about whether any statistically significant results are also practically significant.",
    "",
    "",
    ""
  ),
  `Theory that could be shown wrong by the outcomes` = c(
    "H6 in BANG",
    "H8 in BANG",
    "H9 in BANG",
    "H5 in BANG"
  ),
  `Observed Outcome` = c(
    "Supported; in-game need satisfaction was positively related to global need satisfaction.",
    "Unsupported; in-game need satisfaction was not related to probability of play in the subsequent 24 hours.",
    glue(
      "Not robustly supported; global need frustration was negatively related to the ",
      "probability of subsequent play in the preregistered analysis ",
      "(OR = {pooled_coef(h2_pooled, 'global_nf_cw', exponentiate = TRUE)}), but the ",
      "effect was negligible and its significance was contingent on which participants were included."
    ),
    "Unsupported; self-reported displacement of a core life domain was not associated with lower global need satisfaction."
  )
) |>
  tt(
    notes = "†All multilevel models in Study A include random slopes and intercepts by participant (pid) for the predictor of interest, and an AR(1) autocorrelation structure for outcome measures. Between-person centered predictors (†\\_cb) are included for debiasing the within-person coefficient of interest, but are not used as part of the primary hypothesis test."
  ) |>
  style_tt(i = 1, j = 3, rowspan = 4, alignv = "m") |>
  style_tt(i = 1, j = 5, rowspan = 4, alignv = "m") |>
  style_tt(i = 1, j = 6, rowspan = 4, alignv = "m") |>
  style_tt(i = 2, j = 4, rowspan = 2, alignv = "m") |>
  style_tt(fontsize = 0.6) |>
  style_tt(i = 0, bold = TRUE)
```

## Full Model Outputs

This section provides complete model summaries for the three main hypothesis tests (H1-H3), including all fixed effects, random effects, and autocorrelation parameters.

### H1: Game need satisfaction is related to global need satisfaction

```{r}
#| label: tbl-full-h1
#| tbl-cap: "H1: Complete model summary for game NS → global NS"
#| code-summary: "Show code (Full H1 model output)"

# Use first imputation model for complete summary
modelsummary(
  list("H1: Game NS positively associated with Global NS" = h1mod),
  coef_rename = labels,
  statistic = c(
    "conf.int",
    "s.e. = {std.error}",
    "t = {statistic}",
    "p = {p.value}"
  ),
  coef_omit = "wave", # Omit individual AR(1) wave parameters
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### H2: Need satisfaction and frustration is related to subsequent play

```{r}
#| label: tbl-full-h2
#| tbl-cap: "H2: Complete model summary for game NS + global NF → play"
#| code-summary: "Show code (Full H2 model output)"

# Use first imputation model for complete summary
# modelsummary(
#   h2mod,
#   coef_rename = labels,
#   statistic = c(
#     "conf.int",
#     "s.e. = {std.error}",
#     "t = {statistic}",
#     "p = {p.value}"
#   ),
#   coef_omit = "wave", # Omit individual AR(1) wave parameters
# ) |>
#   style_tt(fontsize = 0.7) |>
#   style_tt(i = 0, bold = TRUE)

## 1) Pre-tidy with CIs
tt <- tidy(h2mod, effects = "fixed", conf.int = TRUE)

## 2) Optional: rename coefficients manually now
tt <- tt |>
  mutate(
    term = dplyr::recode(term, !!!labels)
  )

## 3) Pre-compute glance once
gl <- glance(h2mod)

## 4) Wrap as a modelsummary_list (no further introspection)
mod_obj <- structure(
  list(
    tidy = tt,
    glance = gl
  ),
  class = "modelsummary_list"
)

## 5) Now call modelsummary on this object
modelsummary(
  list("H2: NS & NF associated with likelihood of subsequent play" = mod_obj),
  statistic = c(
    "CI = [{conf.low}, {conf.high}]",
    "s.e. = {std.error}",
    "z = {statistic}",
    "p = {p.value}"
  ),
  coef_omit = "wave",
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### H3: Displacing core domains is associated with lower global need satisfaction

```{r}
#| label: tbl-full-h3
#| tbl-cap: "H3: Complete model summary for displaced core → global NS"
#| code-summary: "Show code (Full H3 model output)"

# Use first imputation model for complete summary
modelsummary(
  list(
    "H3: Displacement of core life domain associated with lower Global NF" = h3mod
  ),
  coef_rename = labels,
  statistic = c(
    "conf.int",
    "s.e. = {std.error}",
    "t = {statistic}",
    "p = {p.value}"
  ),
  coef_omit = "wave", # Omit individual AR(1) wave parameters
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### Study B: Game need satisfaction and play behavior in PowerWash Simulator

```{r}
#| label: tbl-full-study2
#| tbl-cap: "Study B: Complete model summaries for game NS → play behavior"
#| code-summary: "Show code (Full Study B model output)"

# Create model summaries for both Study B models
modelsummary(
  list(
    "Session Length" = pws_m1,
    "Time to Next Session" = pws_m2
  ),
  coef_rename = labels,
  statistic = c(
    "conf.int",
    "s.e. = {std.error}",
    "t = {statistic}",
    "p = {p.value}"
  )
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

## Diagnostics

```{r}
#| label: fig-imputation
#| fig-cap: "Imputed vs observed distributions for need satisfaction/frustration variables"
#| fig-height: 3
#| fig-width: 12

# Compare observed vs imputed distributions (pooled across waves)
bind_rows(dat_complete, dat) |>
  pivot_longer(
    c(global_ns, global_nf, game_ns),
    names_to = "variable",
    values_to = "value"
  ) |>
  filter(!is.na(value)) |>
  mutate(
    data_type = if_else(.imp == 0, "Observed", "Imputed"),
    data_type = factor(data_type, levels = c("Observed", "Imputed")),
    variable = factor(
      variable,
      levels = c("game_ns", "global_ns", "global_nf"),
      labels = c(labels["game_ns"], labels["global_ns"], labels["global_nf"])
    )
  ) |>
  ggplot(aes(x = value, color = data_type, group = .imp)) +
  geom_density(linewidth = 0.7) +
  scale_color_manual(
    values = c("Observed" = "black", "Imputed" = "steelblue")
  ) +
  facet_wrap(~variable, scales = "free", nrow = 1) +
  labs(color = NULL, x = "Value", y = "Density") +
  theme(legend.position = "bottom")
```

## Sensitivity Analyses

We conducted several sensitivity analyses to assess the robustness of our findings regarding the relationship between need satisfaction/frustration and subsequent play behavior.

### S1: Temporal window robustness

Testing whether the temporal window affects results of H2a (game need satisfation) and H2b (global need frustration). The main analysis used 24 hours post-survey. Here we test: (a) 24 hours pre-survey (reverse temporal ordering to test bidirectionality), (b) 6 hours post-survey, (c) 12 hours post-survey, and (d) 24 hours post-survey (preregistered analysis).







```{r}
#| label: tbl-s1-temporal-windows
#| tbl-cap: "S1: H2 associations (odds ratios) across different temporal windows. Cells show OR (p). Main analysis (24h post-survey) shown for comparison. Pre-survey window tests reverse temporal ordering."
#| code-summary: "Show code (Create combined temporal windows table)"

# Combine all results (odds ratios, since the H2 outcome is binary)
bind_rows(
  clean_results(sens1c_pooled, "24h pre", exponentiate = TRUE),
  clean_results(sens1b_pooled, "6h post", exponentiate = TRUE),
  clean_results(sens1_pooled, "12h post", exponentiate = TRUE),
  clean_results(h2_pooled, "24h post", exponentiate = TRUE)
) |>
  pivot_wider(
    names_from = window,
    values_from = result,
    names_sort = FALSE
  ) |>
  rename(Parameter = term) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

Results indicate that shorter windows post-survey are still unassociated with play likelihood, but that video game play is more likely in the day preceding a report of high in-game need satisfaction or high general need frustration. 

### S2: Random effects specification robustness

Random slopes allow associations to vary across individuals, which is theoretically appropriate for these constructs. The main analysis used a random intercept only model due to convergence issues in frequentist estimation. Here we test whether this simplification affects fixed effect estimates by comparing four specifications: (a) no random slopes (main model), (b) random slope for game NS within-person only, (c) random slope for global NF within-person only, and (d) both random slopes simultaneously using Bayesian estimation (which handles complex random effects more robustly).





```{r}
#| label: tbl-s2-specification-comparison
#| tbl-cap: "S2: H2 fixed effects (odds ratios) across random effects specifications. Frequentist estimates (first three columns) show OR (p-value). Bayesian estimates show OR [95% credible interval]."
#| code-summary: "Show code (Create S2 combined specification comparison table)"

# All estimates are exponentiated to odds ratios (binary H2 outcome).

# Extract estimates from main H2 model (no random slopes)
h2_simple <- summary(h2_pooled) |>
  as_tibble() |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    result = glue(
      "{number(exp(estimate), 0.01)} ({ifelse(p.value < 0.001, '<.001', round(p.value, 3))})"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "No slopes")

# Extract estimates from one-slope models
h2a_est <- summary(s2_h2a_pooled) |>
  as_tibble() |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    result = glue(
      "{number(exp(estimate), 0.01)} ({ifelse(p.value < 0.001, '<.001', round(p.value, 3))})"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "RS: game NS")

h2b_est <- summary(s2_h2b_pooled) |>
  as_tibble() |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    result = glue(
      "{number(exp(estimate), 0.01)} ({ifelse(p.value < 0.001, '<.001', round(p.value, 3))})"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "RS: global NF")

# Extract estimates from Bayesian model with both slopes
sens2_est <- s2_bayes_fixed |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    # Bayesian doesn't have p-values, show 95% credible interval instead
    result = glue(
      "{number(exp(Estimate), 0.01)} [{number(exp(`l-95% CI`), 0.01)}, {number(exp(`u-95% CI`), 0.01)}]"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "Both slopes (Bayesian)")

# Combine all specifications
bind_rows(h2_simple, h2a_est, h2b_est, sens2_est) |>
  mutate(
    term = ifelse(term %in% names(labels), labels[term], term)
  ) |>
  pivot_wider(names_from = specification, values_from = result) |>
  rename(Parameter = term) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

All results vary minimally and can be considered robust to the decision to drop random slopes from the main models.  

### S3: Play volume (continuous outcome)

Here we test whether the predictors have a linear association with play volume in minutes, rather than binary play occurrence. Because this is a linear (Gaussian) model, estimates are raw coefficients on the scale of minutes played, not odds ratios.



```{r}
#| label: tbl-s3-results
#| tbl-cap: "S3: H2 with continuous play volume (minutes) as the outcome, rather than binary play"
#| code-summary: "Show code (Create S3 results table)"

summary(sens3_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    term = as.character(term),
    term = ifelse(term %in% names(labels), labels[term], term),
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  rename(
    Parameter = term,
    Estimate = estimate,
    SE = std.error,
    t = statistic,
    p = p.value
  ) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```







### S4: Sample construction robustness

The preregistered primary analysis imputes and analyses all eligible participants, including many who completed only a few surveys. Here we test whether the H2a/H2b estimates depend on restricting the sample to participants with more observed data. We refit the H2 model (i) on complete cases only, with no imputation; (ii) on the >=15-survey subsample (>=50% of the diary period), imputed separately; and (iii) across survey-completion thresholds swept from 10 to 24, to check that the estimate does not hinge on the specific >=15 cutoff.

```{r}
#| label: tbl-s4-results
#| tbl-cap: "S4: H2 estimates (odds ratios) across sample-construction specifications. The full-sample row is the preregistered primary analysis."
#| code-summary: "Show code (S4: Build combined sample-robustness table)"

sample_results |>
  arrange(coefficient, spec) |>
  transmute(
    coefficient,
    Specification = as.character(spec),
    OR = number(exp(estimate), 0.01),
    `95% CI` = glue(
      "[{number(exp(lo), 0.01)}, {number(exp(hi), 0.01)}]"
    ),
    Statistic = number(statistic, 0.001),
    df = number(df, 0.1),
    p = ifelse(p.value < 0.001, "<.001", number(p.value, 0.001))
  ) |>
  select(-coefficient) |>
  tt(
    notes = "Odds ratios (binary H2 outcome); CIs exponentiate the Wald interval. Statistic and df follow Rubin's rules (Barnard-Rubin approximation).",
    width = .82
  ) |>
  group_tt(
    i = list(
      "H2a: Game need satisfaction" = 1,
      "H2b: Global need frustration" = 9
    )
  ) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = c(0, 1, 10), bold = TRUE)
```

```{r}
#| label: fig-s4-sample-robustness
#| fig-cap: "S4: H2 estimates (odds ratios) across sample-construction specifications. Points show pooled odds ratios; bars show 95% confidence intervals (log scale). The preregistered primary analysis (full sample) is highlighted."
#| code-summary: "Show code (S4: Plot sample-robustness estimates)"

sample_results |>
  ggplot(aes(
    x = spec,
    y = exp(estimate),
    ymin = exp(lo),
    ymax = exp(hi),
    colour = is_primary,
    shape = is_primary
  )) +
  geom_hline(yintercept = 1, linetype = "dashed", colour = "grey50") +
  geom_pointrange() +
  scale_colour_manual(
    values = c("FALSE" = "grey40", "TRUE" = "#E05C2A"),
    guide = "none"
  ) +
  scale_shape_manual(values = c("FALSE" = 16, "TRUE" = 18), guide = "none") +
  scale_y_log10() +
  facet_wrap(~coefficient, ncol = 1, scales = "free_y") +
  labs(
    x = NULL,
    y = "Odds ratio for subsequent play"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 30, hjust = 1)
  )
```

### S5: Interaction between game NS and global NF

Testing whether the association of global need frustration with play depends on recent game need satisfaction (i.e., do satisfied players respond differently to global need frustration?).



```{r}
#| label: tbl-s5-results
#| tbl-cap: "S5: H2 with game NS \u00d7 global NF interaction (odds ratios)"
#| code-summary: "Show code (Create S5 results table)"

summary(sens5b_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  mutate(
    term = as.character(term),
    Parameter = ifelse(term %in% names(labels), labels[term], term),
    OR = number(exp(estimate), 0.01),
    `95% CI` = glue(
      "[{number(exp(estimate - 1.96 * std.error), 0.01)}, ",
      "{number(exp(estimate + 1.96 * std.error), 0.01)}]"
    ),
    z = number(statistic, 0.001),
    p = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  select(Parameter, OR, `95% CI`, z, p) |>
  tt(
    notes = "Odds ratios (binary H2 outcome). The interaction term is a ratio of odds ratios: the multiplicative shift in the global NF odds ratio per 1-point higher game NS."
  ) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### S6: Non-linearity test with splines

Testing whether the relationships between predictors and play behavior are non-linear by fitting natural splines to the H2 predictors. We use complete cases only (no imputation) for computational simplicity.



```{r}
#| label: tbl-s6-results
#| tbl-cap: "S6: Model comparison between linear and spline specifications"
#| code-summary: "Show code (Create S6 comparison table)"

# Compare model fit
comparison <- tibble(
  Model = c("Linear", "Spline (3 df)"),
  AIC = c(AIC(sens8_linear), AIC(sens8_spline)),
  BIC = c(BIC(sens8_linear), BIC(sens8_spline)),
  LogLik = c(logLik(sens8_linear), logLik(sens8_spline)),
  N = c(nobs(sens8_linear), nobs(sens8_spline))
) |>
  mutate(
    `ΔAic` = AIC - min(AIC),
    across(c(AIC, BIC, LogLik), ~ round(.x, 1))
  )

comparison |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

```{r}
#| label: fig-s6-spline-predictions
#| fig-cap: "S6: Comparison of linear vs spline predictions for H2 predictors. Points show observed data (aggregated), solid lines show linear model predictions, dashed lines show spline model predictions with 95% confidence ribbons."
#| code-summary: "Show code (Plot S6 spline vs linear predictions)"
#| fig-height: 6

dat_complete <- dat |>
  filter(.imp == 1) |>
  select(
    pid,
    wave,
    date,
    telemetry_played_any_24h,
    game_ns_cw,
    game_ns_cb,
    global_nf_cw,
    global_nf_cb
  ) |>
  filter(complete.cases(pick(everything())))

# Generate predictions across the range of predictors
pred_data <- expand_grid(
  game_ns_cw = seq(
    min(dat_complete$game_ns_cw, na.rm = TRUE),
    max(dat_complete$game_ns_cw, na.rm = TRUE),
    length.out = 100
  ),
  global_nf_cw = seq(
    min(dat_complete$global_nf_cw, na.rm = TRUE),
    max(dat_complete$global_nf_cw, na.rm = TRUE),
    length.out = 100
  )
)

# Predictions for game NS (holding global NF at mean)
pred_game_linear <- marginaleffects::predictions(
  sens8_linear,
  newdata = datagrid(
    game_ns_cw = unique(pred_data$game_ns_cw),
    global_nf_cw = 0,
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Linear")

pred_game_spline <- marginaleffects::predictions(
  sens8_spline,
  newdata = datagrid(
    game_ns_cw = unique(pred_data$game_ns_cw),
    global_nf_cw = 0,
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Spline")

panel_a <- bind_rows(pred_game_linear, pred_game_spline) |>
  ggplot(aes(x = game_ns_cw, y = estimate, color = model, fill = model)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  geom_line(aes(linetype = model), linewidth = 1) +
  scale_color_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_fill_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_linetype_manual(values = c("Linear" = "solid", "Spline" = "dashed")) +
  labs(
    x = labels["game_ns (within-person)"],
    y = "P(Play in next 24h)",
    color = NULL,
    fill = NULL,
    linetype = NULL
  ) +
  theme(legend.position = "top")

# Predictions for global NF (holding game NS at mean)
pred_nf_linear <- marginaleffects::predictions(
  sens8_linear,
  newdata = datagrid(
    game_ns_cw = 0,
    global_nf_cw = unique(pred_data$global_nf_cw),
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Linear")

pred_nf_spline <- marginaleffects::predictions(
  sens8_spline,
  newdata = datagrid(
    game_ns_cw = 0,
    global_nf_cw = unique(pred_data$global_nf_cw),
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Spline")

panel_b <- bind_rows(pred_nf_linear, pred_nf_spline) |>
  ggplot(aes(x = global_nf_cw, y = estimate, color = model, fill = model)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  geom_line(aes(linetype = model), linewidth = 1) +
  scale_color_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_fill_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_linetype_manual(values = c("Linear" = "solid", "Spline" = "dashed")) +
  labs(
    x = labels["global_nf (within-person)"],
    y = "P(Play in next 24h)",
    color = NULL,
    fill = NULL,
    linetype = NULL
  ) +
  theme(legend.position = "top")

panel_a +
  panel_b +
  plot_annotation(tag_levels = "A") +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "top",
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA)
  )
```

The spline model `r if(exists("comparison") && comparison$ΔAic[2] < -2) "shows substantially better fit (ΔAIC < -2)" else if(exists("comparison") && comparison$ΔAic[2] > 2) "does not outperform the linear model (ΔAIC > 2)" else "shows similar fit to the linear model"`, suggesting that the relationships between need satisfaction/frustration and play behavior `r if(exists("comparison") && comparison$ΔAic[2] < -2) "exhibit non-linear patterns" else "are adequately captured by linear terms"`.

### S7: Separate needs components

Testing whether associations with play differ across the three basic psychological needs (autonomy, competence, relatedness) rather than using composite need satisfaction scores. We test H2 separately for each need component.



```{r}
#| label: tbl-s7-h2-results
#| tbl-cap: "S7: Associations (odds ratios) between need components and subsequent play"
#| code-summary: "Show code (Create S7 results table)"

# H2a rows first (game NS components), then H2b rows (global NF components)
bind_rows(
  summary(sens9_h2_aut) |>
    as_tibble() |>
    filter(term == "game_aut_cw") |>
    mutate(predictor = "Autonomy satisfaction"),
  summary(sens9_h2_com) |>
    as_tibble() |>
    filter(term == "game_com_cw") |>
    mutate(predictor = "Competence satisfaction"),
  summary(sens9_h2_rel) |>
    as_tibble() |>
    filter(term == "game_rel_cw") |>
    mutate(predictor = "Relatedness satisfcation"),
  summary(sens9_h2_aut) |>
    as_tibble() |>
    filter(term == "global_aut_nf_cw") |>
    mutate(predictor = "Autonomy frustration"),
  summary(sens9_h2_com) |>
    as_tibble() |>
    filter(term == "global_com_nf_cw") |>
    mutate(predictor = "Competence frustration"),
  summary(sens9_h2_rel) |>
    as_tibble() |>
    filter(term == "global_rel_nf_cw") |>
    mutate(predictor = "Relatedness frustration")
) |>
  mutate(
    OR = number(exp(estimate), 0.01),
    `95% CI` = glue(
      "[{number(exp(estimate - 1.96 * std.error), 0.01)}, ",
      "{number(exp(estimate + 1.96 * std.error), 0.01)}]"
    ),
    z = number(statistic, 0.001),
    p = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  select(
    Predictor = predictor,
    OR,
    `95% CI`,
    z,
    p
  ) |>
  tt(
    width = 0.7,
    notes = "Odds ratios (binary outcome: any play in the subsequent 24 hours). All predictors are day-to-day fluctuations (within-person centered). Each need component is from a separate model."
  ) |>
  group_tt(
    i = list(
      "H2a: In-game need satisfaction → subsequent play" = 1,
      "H2b: Global need frustration → subsequent play" = 4
    )
  ) |>
  style_tt(i = c(1, 5), bold = TRUE) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### S8: Game need frustration and play behavior

Testing whether game need frustration (rather than satisfaction) is related to subsequent play behavior. This mirrors the H2a hypothesis but uses frustration instead of satisfaction.

```{r}
#| label: tbl-s8-results
#| tbl-cap: "S8: Game need frustration predicting subsequent play (odds ratios)"
#| code-summary: "Show code (Create S8 results table)"

summary(sens10_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  mutate(
    term = as.character(term),
    Parameter = ifelse(term %in% names(labels), labels[term], term),
    OR = number(exp(estimate), 0.01),
    `95% CI` = glue(
      "[{number(exp(estimate - 1.96 * std.error), 0.01)}, ",
      "{number(exp(estimate + 1.96 * std.error), 0.01)}]"
    ),
    z = number(statistic, 0.001),
    p = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  select(Parameter, OR, `95% CI`, z, p) |>
  tt(
    notes = "Odds ratios (binary outcome: any play in the subsequent 24 hours)."
  ) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

Results show that when people experience higher than usual in-game need frustration, they are less likely to play on the following day, but that this relationship is small. Nonetheless, in contrast to the robust null results for game need satisfaction across various specifications, this provides some initial evidence that need frustration may be more salient for day-to-day change in gaming behavior than need satisfaction.

### S9: H3 displacement by specific core life domain

The main H3 analysis aggregated all core life domains (work/school, social engagements, sleep/eating/fitness, caretaking) into a single binary indicator. Here we test whether specific displaced domains differ in their relationship with global need satisfaction.

```{r}
#| label: tbl-s9-domain-results
#| tbl-cap: "H3 sensitivity analysis: Effect of displacing specific core life domains on global need satisfaction"
#| code-summary: "Show code (Create S9 results table)"

# Extract results for each domain
s10_results <- bind_rows(
  lapply(names(s10_pooled), function(domain) {
    summary(s10_pooled[[domain]]) |>
      as_tibble() |>
      filter(str_detect(term, "TRUE")) |>
      select(term, estimate, std.error, statistic, p.value) |>
      mutate(
        Domain = case_when(
          domain == "displaced_work_school" ~ "Work/School",
          domain == "displaced_social" ~ "Social Engagement",
          domain == "displaced_health_sleep" ~ "Sleep/Eating/Fitness",
          domain == "displaced_caretaking" ~ "Caretaking",
          TRUE ~ domain
        )
      ) |>
      select(Domain, estimate, std.error, statistic, p.value)
  })
)

s10_results |>
  mutate(
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      p.value < 0.01 ~ sprintf("%.3f", p.value),
      TRUE ~ sprintf("%.2f", p.value)
    )
  ) |>
  tt(
    width = 0.7,
    escape = TRUE,
    notes = "All models include random intercepts, random slopes, and AR(1) autocorrelation. Estimates represent the difference in global need satisfaction when the specific domain was displaced vs. not displaced."
  ) |>
  style_tt(fontsize = 0.8) |>
  style_tt(i = 0, bold = TRUE)
```

Results showed that global need satisfaction was lower when gaming displaced sleep/eating/fitness, but---contrary to expectations---tended to be higher when gaming displaced social engagements or caretaking.

# References

::: {#refs}
:::
