---
title: |
  A title goes here
author:
  - name: author
    corresponding: true
    orcid: 0000-0000-0000-0000
    email: name@domain.com
    affiliations:
      - ref: 1
    # roles:
    #   - conceptualization
    #   - data curation
    #   - methodology
    #   - formal analysis
    #   - writing

affiliations:
  - id: 1
    name: University
    department: Department
csl: https://www.zotero.org/styles/apa
keywords: [keywords]
editor_options:
  chunk_output_type: console
  markdown:
    wrap: none
knitr:
  opts_chunk:
    echo: false
    cache: true
    warning: false
    message: false
    fig-width: 6
    fig-asp: 0.618
    out-width: 80%
    fig-align: center
code-links: repo
format:
  html:
    theme:
      light: united
      dark: darkly
    toc: true
    toc-depth: 2
    fontsize: 13pt
  preprint-typst:
    wordcount: true
    theme: jou
    citeproc: true
    mainfont: "Liberation Serif"
    sansfont: "Liberation Sans"
    include-before-body:
      - text: "#show <refs>: set par(hanging-indent: 1.4em)"
  docx: default

```{r}
#| label: libraries

```

```{r}
#| label: load-data

```

