---
title: "Modelling"
subtitle: "Primary hypothesis tests for 'All BANG, little buck'"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

Fits the three primary hypothesis tests (H1-H3) for Study A with `glmmTMB`,
each fit separately to all 27 imputed datasets and pooled by Rubin's rules,
and reports convergence checks and residual diagnostics. Each hypothesis is
fit three ways: on the primary (full) sample -- the headline result -- and,
as sensitivity analyses reported alongside it, on the >=15-survey subsample
and on complete cases with no imputation. Study B models are in the Study B
document; the S1-S9 sensitivity analyses are in the sensitivity document.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(glmmTMB)
library(mice)
library(broom.mixed)
library(DHARMa)
library(future)
library(furrr)
library(targets)
```

```{r}
#| label: source-functions
#| code-summary: "Show code (Load pipeline functions)"

source("R/targets/models_main.R")
```

```{r}
#| label: load-inputs
#| code-summary: "Show code (Load imputation.qmd's exported objects)"

tar_load(c(dat, dat_restricted, dat_complete, m_imputations))
```

```{r}
#| label: formulas
#| code-summary: "Show code (Hypothesis model formulas)"

# One formula per hypothesis, reused across the primary, >=15-subsample, and
# complete-case fits. H1 and H3 are linear with a random slope for the focal
# day-level predictor; H2 is logistic with random intercepts only (random
# slopes did not converge for the binary outcome). All include AR(1).
h1_formula <- global_ns ~
  game_ns_cw + game_ns_cb + (1 + game_ns_cw | pid) + ar1(wave + 0 | pid)

h2_formula <- telemetry_played_any_24h ~
  game_ns_cw + game_ns_cb + global_nf_cw + global_nf_cb +
  (1 | pid) + ar1(wave + 0 | pid)

h3_formula <- global_ns ~
  displaced_core_domain + (1 + displaced_core_domain | pid) + ar1(wave + 0 | pid)
```

## Primary Hypothesis Models

Each model is fit separately to all `r m_imputations` imputed datasets
(parallelized via `fit_mi_models()`) and pooled using Rubin's rules. The
`*_restricted_pooled` fits repeat this on the >=15-survey subsample; the
`*_cc_pooled` fits use complete cases only (`fit_cc_model()`).

### H1: Game need satisfaction -> global need satisfaction

```{r}
#| label: h1-model
#| code-summary: "Show code (Fit H1 models: game NS -> global NS)"

h1_fits <- fit_mi_models(dat, h1_formula, m = m_imputations)
h1_pooled <- pool(h1_fits)
h1mod <- h1_fits[[1]]

h1_restricted_pooled <- pool(fit_mi_models(
  dat_restricted, h1_formula, m = m_imputations
))
h1_cc_pooled <- fit_cc_model(
  dat_complete, h1_formula, key_vars = c("global_ns", "game_ns")
)
```

### H2: Game need satisfaction + global need frustration -> play

```{r}
#| label: h2-model
#| code-summary: "Show code (Fit H2 models: game NS + global NF -> play)"

h2_fits <- fit_mi_models(
  dat,
  h2_formula,
  m = m_imputations,
  family = binomial(link = "logit"),
  ziformula = ~0
)
h2_pooled <- pool(h2_fits)
h2mod <- h2_fits[[1]]

h2_restricted_pooled <- pool(fit_mi_models(
  dat_restricted,
  h2_formula,
  m = m_imputations,
  family = binomial(link = "logit"),
  ziformula = ~0
))
h2_cc_pooled <- fit_cc_model(
  dat_complete,
  h2_formula,
  key_vars = c("telemetry_played_any_24h", "game_ns", "global_nf"),
  family = binomial(link = "logit"),
  ziformula = ~0
)
```

### H3: Displaced core domain -> global need satisfaction

```{r}
#| label: h3-model
#| code-summary: "Show code (Fit H3 models: displaced core domain -> global NS)"

h3_fits <- fit_mi_models(dat, h3_formula, m = m_imputations)
h3_pooled <- pool(h3_fits)
h3mod <- h3_fits[[1]]

h3_restricted_pooled <- pool(fit_mi_models(
  dat_restricted, h3_formula, m = m_imputations
))
h3_cc_pooled <- fit_cc_model(
  dat_complete, h3_formula, key_vars = c("global_ns", "displaced_core_domain")
)
```

### Convergence and singularity across primary fits

The primary sample includes participants with very few completed surveys, so
the H1/H3 random slopes may be estimated as singular for some imputations.
This tallies convergence codes and near-zero random-slope SDs across the 27
primary fits; if many fits are singular the random slope should be dropped
(as it already is for H2) and that documented as a deviation.

```{r}
#| label: primary-convergence
#| code-summary: "Show code (Convergence + singularity tally, primary fits)"

slope_sd <- function(fit) {
  vc <- glmmTMB::VarCorr(fit)$cond$pid
  sd <- attr(vc, "stddev")
  if (length(sd) > 1) sd[2] else NA_real_
}

tibble(
  hypothesis = c("H1", "H2", "H3"),
  fits = list(h1_fits, h2_fits, h3_fits)
) |>
  mutate(
    converged = map_int(fits, ~ sum(map_lgl(.x, \(f) f$fit$convergence == 0))),
    min_slope_sd = map_dbl(fits, ~ min(map_dbl(.x, slope_sd), na.rm = TRUE)),
    n_singular_slope = map_int(
      fits,
      ~ sum(map_dbl(.x, slope_sd) < 1e-4, na.rm = TRUE)
    )
  ) |>
  select(-fits) |>
  print()
```

## Model Diagnostics

Convergence across imputations, random-effect structure, and (for the binary
H2 outcome) DHARMa residual checks. These operate on the per-imputation fit
lists (`h1_fits` / `h2_fits`), which are not exported -- so they live here in
the modelling stage rather than in the manuscript. None of these quantities
are cited in the manuscript text.

```{r}
#| label: h1-diagnostics
#| code-summary: "Show code (H1 convergence and random-effect structure)"

# Convergence check across imputations
conv_summary <- tibble(
  imputation = seq_along(h1_fits),
  converged = map_lgl(h1_fits, ~ .x$fit$convergence == 0),
  warnings = map_chr(
    h1_fits,
    ~ {
      w <- .x$fit$warnings
      if (length(w) > 0) paste(w, collapse = "; ") else "None"
    }
  )
)
print(conv_summary)
glue("Converged: {sum(conv_summary$converged)}/{nrow(conv_summary)}")

# Random effect structure (from the first imputation's model)
re_sd <- attr(VarCorr(h1mod)$cond$pid, "stddev")
glue("Random intercept SD: {round(re_sd[1], 3)}")
if (length(re_sd) > 1) {
  glue("Random slope SD (game_ns_cw): {round(re_sd[2], 3)}")
}
```

```{r}
#| label: h2-diagnostics
#| code-summary: "Show code (H2 convergence, random effects, DHARMa residuals)"
#| fig-width: 8

# Convergence check across imputations
conv_summary <- tibble(
  imputation = seq_along(h2_fits),
  converged = map_lgl(h2_fits, ~ .x$fit$convergence == 0),
  warnings = map_chr(
    h2_fits,
    ~ {
      w <- .x$fit$warnings
      if (length(w) > 0) paste(w, collapse = "; ") else "None"
    }
  )
)
print(conv_summary)
glue("Converged: {sum(conv_summary$converged)}/{nrow(conv_summary)}")

# Random effect structure (first imputation's model)
re_sd <- attr(VarCorr(h2mod)$cond$pid, "stddev")
re_names <- names(re_sd)
walk2(re_names, re_sd, ~ glue("{.x} SD: {round(.y, 3)}"))

# Random intercept distribution (logit scale)
re_intercepts <- coef(h2mod)$cond$pid[, "(Intercept)"]
tibble(
  stat = c("Mean", "SD", "Min", "Max", "IQR_25%", "IQR_75%"),
  value = c(
    mean(re_intercepts),
    sd(re_intercepts),
    min(re_intercepts),
    max(re_intercepts),
    quantile(re_intercepts, 0.25),
    quantile(re_intercepts, 0.75)
  )
) |>
  mutate(value = round(value, 3)) |>
  print()

# Implied probability at fixed intercept
fixed_int <- fixef(h2mod)$cond["(Intercept)"]
glue("Pr(play) at population mean: {round(plogis(fixed_int), 3)}")

# DHARMa residual diagnostics
sim_resid <- simulateResiduals(h2mod, plot = FALSE)
plot(sim_resid, main = "H2 Model: DHARMa diagnostics")

list(
  dispersion = testDispersion(sim_resid),
  outliers = testOutliers(sim_resid),
  quantiles = testQuantiles(sim_resid)
) |>
  walk(print)

# Residuals vs. predictors
par(mfrow = c(2, 2))
walk2(
  c("game_ns_cw", "global_nf_cw", "game_ns_cb", "global_nf_cb"),
  c(
    "Game NS (within)",
    "Global NF (within)",
    "Game NS (between)",
    "Global NF (between)"
  ),
  ~ plotResiduals(sim_resid, form = h2mod$frame[[.x]], main = glue("vs. {.y}"))
)
par(mfrow = c(1, 1))

# Temporal autocorrelation (within-person lag-1)
acf_by_person <- h2mod$frame |>
  group_by(pid) |>
  arrange(wave) |>
  filter(n() >= 3) |>
  reframe(
    acf = cor(
      sim_resid$scaledResiduals[cur_group_rows()][-n()],
      sim_resid$scaledResiduals[cur_group_rows()][-1],
      use = "complete.obs"
    )
  ) |>
  pull(acf)

tibble(
  stat = c("Mean", "Median", "Min", "Max"),
  lag1_acf = c(
    mean(acf_by_person),
    median(acf_by_person),
    min(acf_by_person),
    max(acf_by_person)
  )
) |>
  mutate(lag1_acf = round(lag1_acf, 3)) |>
  print()

# Aggregated residuals
recalculateResiduals(sim_resid, group = h2mod$frame$wave) |>
  plot(main = "Residuals by wave")
recalculateResiduals(sim_resid, group = h2mod$frame$pid) |>
  plot(main = "Residuals by individual")
```

## Exported Objects

```{r}
#| label: export
#| code-summary: "Show code (Export objects for the manuscript and supplement)"

source("R/targets/export.R")
dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  modelling_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(modelling_export_names)} objects to data/exports/"))
```
