---
title: "Modelling"
subtitle: "Primary hypothesis tests for 'All BANG, little buck'"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

This document fits every model reported in the manuscript and supplement:
the three primary hypothesis tests (H1-H3) here, and (in later pipeline
phases) Study B and the S1-S9 sensitivity analyses. It is its own `targets`
stage (`modelling_report`), separate from data loading and imputation -- so
fixing a model formula only reruns model fitting, not the imputation.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(glmmTMB)
library(mice)
library(broom.mixed)
library(DHARMa)
library(future)
library(furrr)
library(targets)
```

```{r}
#| label: source-functions
#| code-summary: "Show code (Load pipeline functions)"

source("R/targets/models_main.R")
```

```{r}
#| label: load-inputs
#| code-summary: "Show code (Load imputation.qmd's exported objects)"

tar_load(c(dat, m_imputations))
```

## Primary Hypothesis Models

Each model is fit separately to all `r m_imputations` imputed datasets
(parallelized via `fit_mi_models()`) and pooled using Rubin's rules.

### H1: Game need satisfaction -> global need satisfaction

```{r}
#| label: h1-model
#| code-summary: "Show code (Fit H1 models: game NS -> global NS)"

h1_fits <- fit_mi_models(
  dat,
  global_ns ~ game_ns_cw + game_ns_cb + (1 + game_ns_cw | pid) + ar1(wave + 0 | pid),
  m = m_imputations
)
h1_pooled <- pool(h1_fits)
h1mod <- h1_fits[[1]]
```

### H2: Game need satisfaction + global need frustration -> play

```{r}
#| label: h2-model
#| code-summary: "Show code (Fit H2 models: game NS + global NF -> play)"

h2_fits <- fit_mi_models(
  dat,
  telemetry_played_any_24h ~
    game_ns_cw +
      game_ns_cb +
      global_nf_cw +
      global_nf_cb +
      (1 | pid) +
      ar1(wave + 0 | pid),
  m = m_imputations,
  family = binomial(link = "logit"),
  ziformula = ~0
)
h2_pooled <- pool(h2_fits)
h2mod <- h2_fits[[1]]
```

### H3: Displaced core domain -> global need satisfaction

```{r}
#| label: h3-model
#| code-summary: "Show code (Fit H3 models: displaced core domain -> global NS)"

h3_fits <- fit_mi_models(
  dat,
  global_ns ~
    displaced_core_domain + (1 + displaced_core_domain | pid) + ar1(wave + 0 | pid),
  m = m_imputations
)
h3_pooled <- pool(h3_fits)
h3mod <- h3_fits[[1]]
```

## Model Diagnostics

Convergence across imputations, random-effect structure, and (for the binary
H2 outcome) DHARMa residual checks. These operate on the per-imputation fit
lists (`h1_fits` / `h2_fits`), which are not exported -- so they live here in
the modelling stage rather than in the manuscript. None of these quantities
are cited in the manuscript text.

```{r}
#| label: h1-diagnostics
#| code-summary: "Show code (H1 convergence and random-effect structure)"

# Convergence check across imputations
conv_summary <- tibble(
  imputation = seq_along(h1_fits),
  converged = map_lgl(h1_fits, ~ .x$fit$convergence == 0),
  warnings = map_chr(
    h1_fits,
    ~ {
      w <- .x$fit$warnings
      if (length(w) > 0) paste(w, collapse = "; ") else "None"
    }
  )
)
print(conv_summary)
glue("Converged: {sum(conv_summary$converged)}/{nrow(conv_summary)}")

# Random effect structure (from the first imputation's model)
re_sd <- attr(VarCorr(h1mod)$cond$pid, "stddev")
glue("Random intercept SD: {round(re_sd[1], 3)}")
if (length(re_sd) > 1) {
  glue("Random slope SD (game_ns_cw): {round(re_sd[2], 3)}")
}
```

```{r}
#| label: h2-diagnostics
#| code-summary: "Show code (H2 convergence, random effects, DHARMa residuals)"
#| fig-width: 8

# Convergence check across imputations
conv_summary <- tibble(
  imputation = seq_along(h2_fits),
  converged = map_lgl(h2_fits, ~ .x$fit$convergence == 0),
  warnings = map_chr(
    h2_fits,
    ~ {
      w <- .x$fit$warnings
      if (length(w) > 0) paste(w, collapse = "; ") else "None"
    }
  )
)
print(conv_summary)
glue("Converged: {sum(conv_summary$converged)}/{nrow(conv_summary)}")

# Random effect structure (first imputation's model)
re_sd <- attr(VarCorr(h2mod)$cond$pid, "stddev")
re_names <- names(re_sd)
walk2(re_names, re_sd, ~ glue("{.x} SD: {round(.y, 3)}"))

# Random intercept distribution (logit scale)
re_intercepts <- coef(h2mod)$cond$pid[, "(Intercept)"]
tibble(
  stat = c("Mean", "SD", "Min", "Max", "IQR_25%", "IQR_75%"),
  value = c(
    mean(re_intercepts),
    sd(re_intercepts),
    min(re_intercepts),
    max(re_intercepts),
    quantile(re_intercepts, 0.25),
    quantile(re_intercepts, 0.75)
  )
) |>
  mutate(value = round(value, 3)) |>
  print()

# Implied probability at fixed intercept
fixed_int <- fixef(h2mod)$cond["(Intercept)"]
glue("Pr(play) at population mean: {round(plogis(fixed_int), 3)}")

# DHARMa residual diagnostics
sim_resid <- simulateResiduals(h2mod, plot = FALSE)
plot(sim_resid, main = "H2 Model: DHARMa diagnostics")

list(
  dispersion = testDispersion(sim_resid),
  outliers = testOutliers(sim_resid),
  quantiles = testQuantiles(sim_resid)
) |>
  walk(print)

# Residuals vs. predictors
par(mfrow = c(2, 2))
walk2(
  c("game_ns_cw", "global_nf_cw", "game_ns_cb", "global_nf_cb"),
  c(
    "Game NS (within)",
    "Global NF (within)",
    "Game NS (between)",
    "Global NF (between)"
  ),
  ~ plotResiduals(sim_resid, form = h2mod$frame[[.x]], main = glue("vs. {.y}"))
)
par(mfrow = c(1, 1))

# Temporal autocorrelation (within-person lag-1)
acf_by_person <- h2mod$frame |>
  group_by(pid) |>
  arrange(wave) |>
  filter(n() >= 3) |>
  reframe(
    acf = cor(
      sim_resid$scaledResiduals[cur_group_rows()][-n()],
      sim_resid$scaledResiduals[cur_group_rows()][-1],
      use = "complete.obs"
    )
  ) |>
  pull(acf)

tibble(
  stat = c("Mean", "Median", "Min", "Max"),
  lag1_acf = c(
    mean(acf_by_person),
    median(acf_by_person),
    min(acf_by_person),
    max(acf_by_person)
  )
) |>
  mutate(lag1_acf = round(lag1_acf, 3)) |>
  print()

# Aggregated residuals
recalculateResiduals(sim_resid, group = h2mod$frame$wave) |>
  plot(main = "Residuals by wave")
recalculateResiduals(sim_resid, group = h2mod$frame$pid) |>
  plot(main = "Residuals by individual")
```

## Exported Objects

```{r}
#| label: export
#| code-summary: "Show code (Export objects for manuscript.qmd/supplement.qmd)"

source("R/targets/export.R")
dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  modelling_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(modelling_export_names)} objects to data/exports/"))
```
