---
title: "Modelling"
subtitle: "Primary hypothesis tests for 'All BANG, little buck'"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

This document fits every model reported in the manuscript and supplement:
the three primary hypothesis tests (H1-H3) here, and (in later pipeline
phases) Study B and the S1-S9 sensitivity analyses. It is its own `targets`
stage (`modelling_report`), separate from data loading and imputation -- so
fixing a model formula only reruns model fitting, not the imputation.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(glmmTMB)
library(mice)
library(broom.mixed)
library(future)
library(furrr)
library(targets)
```

```{r}
#| label: source-functions
#| code-summary: "Show code (Load pipeline functions)"

source("R/targets/models_main.R")
```

```{r}
#| label: load-inputs
#| code-summary: "Show code (Load imputation.qmd's exported objects)"

tar_load(c(dat, m_imputations))
```

## Primary Hypothesis Models

Each model is fit separately to all `r m_imputations` imputed datasets
(parallelized via `fit_mi_models()`) and pooled using Rubin's rules.

### H1: Game need satisfaction -> global need satisfaction

```{r}
#| label: h1-model
#| code-summary: "Show code (Fit H1 models: game NS -> global NS)"

h1_fits <- fit_mi_models(
  dat,
  global_ns ~ game_ns_cw + game_ns_cb + (1 + game_ns_cw | pid) + ar1(wave + 0 | pid),
  m = m_imputations
)
h1_pooled <- pool(h1_fits)
h1mod <- h1_fits[[1]]
```

### H2: Game need satisfaction + global need frustration -> play

```{r}
#| label: h2-model
#| code-summary: "Show code (Fit H2 models: game NS + global NF -> play)"

h2_fits <- fit_mi_models(
  dat,
  telemetry_played_any_24h ~
    game_ns_cw +
      game_ns_cb +
      global_nf_cw +
      global_nf_cb +
      (1 | pid) +
      ar1(wave + 0 | pid),
  m = m_imputations,
  family = binomial(link = "logit"),
  ziformula = ~0
)
h2_pooled <- pool(h2_fits)
h2mod <- h2_fits[[1]]
```

### H3: Displaced core domain -> global need satisfaction

```{r}
#| label: h3-model
#| code-summary: "Show code (Fit H3 models: displaced core domain -> global NS)"

h3_fits <- fit_mi_models(
  dat,
  global_ns ~
    displaced_core_domain + (1 + displaced_core_domain | pid) + ar1(wave + 0 | pid),
  m = m_imputations
)
h3_pooled <- pool(h3_fits)
h3mod <- h3_fits[[1]]
```

## Exported Objects

```{r}
#| label: export
#| code-summary: "Show code (Export objects for manuscript.qmd/supplement.qmd)"

source("R/targets/export.R")
dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  modelling_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(modelling_export_names)} objects to data/exports/"))
```
