---
title: "Preprocessing"
subtitle: "Data loading, cleaning, and enrichment for 'All BANG, little buck'"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

This document downloads and cleans the raw data: Zenodo download, telemetry
aggregation, and survey enrichment. It is registered as its own `targets`
target (`preprocessing_report`) in `_targets.R`. Multiple imputation happens
in `imputation.qmd`, and model fitting in `modelling.qmd` -- each is its own
pipeline stage, so editing one doesn't force the others to recompute.
`imputation.qmd` reads this document's exported objects via
`targets::tar_load()`/`targets::tar_read()`, not by re-running any of this
code.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
```

```{r}
#| label: source-functions
#| code-summary: "Show code (Load pipeline functions)"

source("R/targets/telemetry.R")
```

## Data Sources

We use two datasets: the Open Play daily-diary study (Study A, this section)
and PowerWash Simulator telemetry (Study B, added in a later pipeline phase).
Open Play data are downloaded from Zenodo on first run and cached locally.

```{r}
#| label: load-data
#| code-summary: "Show code (Download and load raw data from Zenodo)"

zenodo_url <- "https://zenodo.org/records/21986572/files/digital-wellbeing/open-play-v1.2.5.zip?download=1"
zip_path <- "data/open-play-v1.2.5.zip"

if (!file.exists(zip_path)) {
  dir.create(dirname(zip_path), showWarnings = FALSE, recursive = TRUE)
  options(timeout = max(600, getOption("timeout")))
  message("Downloading 194MB file from Zenodo (may take a few minutes)...")
  tryCatch(
    {
      download.file(zenodo_url, zip_path, mode = "wb", method = "libcurl")
      message("Download complete!")
    },
    error = function(e) {
      message("Download failed. Please download manually from:")
      message(zenodo_url)
      message(glue("And save to: {normalizePath(zip_path, mustWork = FALSE)}"))
      stop(e)
    }
  )
}

extract_dir <- "data/open-play-v1.2.5"
if (!dir.exists(extract_dir)) {
  message("Extracting zip archive...")
  unzip(zip_path, exdir = "data")
  extracted_folder <- list.dirs("data", recursive = FALSE, full.names = TRUE)
  extracted_folder <- extracted_folder[grepl(
    "digital-wellbeing-open-play",
    extracted_folder
  )]
  if (length(extracted_folder) == 1 && extracted_folder != extract_dir) {
    file.rename(extracted_folder, extract_dir)
  }
}

intake <- read_csv(
  file.path(extract_dir, "data/clean/survey_intake.csv.gz"),
  guess_max = 10000
)
surveys <- read_csv(file.path(
  extract_dir,
  "data/clean/survey_daily.csv.gz"
)) |>
  filter(pid %in% intake$pid)
xbox <- read_csv(file.path(extract_dir, "data/clean/xbox.csv.gz"))
nintendo <- read_csv(file.path(extract_dir, "data/clean/nintendo.csv.gz"))
steam <- read_csv(
  file.path(extract_dir, "data/clean/steam.csv.gz"),
  guess_max = 10000
)
```

## Telemetry Processing

Session-level Xbox/Nintendo/Steam logs are aggregated into hourly, daily, and
weekly playtime, with DST-aware local-time conversion (`get_dst_offset()`,
vendored from the Zenodo archive's own helpers in `R/targets/telemetry.R`).

```{r}
#| label: prepare-telemetry
#| code-summary: "Show code (Process telemetry into hourly playtime with timezone adjustments)"

tz_map <- intake |>
  mutate(
    pid = as.character(pid),
    country,
    local_timezone,
    .keep = "none"
  ) |>
  distinct(pid, .keep_all = TRUE)

sessions_telemetry <- bind_rows(
  xbox |> mutate(platform = "Xbox"),
  nintendo |> mutate(platform = "Nintendo")
) |>
  left_join(tz_map, by = "pid") |>
  filter(!is.na(local_timezone)) |>
  mutate(
    offset_start = get_dst_offset(session_start, country, local_timezone),
    offset_end = get_dst_offset(session_end, country, local_timezone),
    start_local = session_start + offset_start,
    end_local = session_end + offset_end,
    duration_min = as.numeric(difftime(
      session_end,
      session_start,
      units = "mins"
    ))
  ) |>
  filter(
    !is.na(session_start),
    !is.na(session_end),
    session_end > session_start,
    duration_min >= 1
  )

hourly_from_sessions <- sessions_telemetry |>
  filter(!is.na(start_local), !is.na(end_local)) |>
  mutate(
    h0_local = floor_date(start_local, "hour"),
    h1_local = floor_date(end_local - seconds(1), "hour"),
    n_hours = as.integer(difftime(h1_local, h0_local, units = "hours")) + 1
  ) |>
  filter(!is.na(n_hours), n_hours > 0) |>
  tidyr::uncount(n_hours, .remove = FALSE, .id = "k") |>
  mutate(
    hour_start_local = h0_local + hours(k - 1),
    minutes = pmax(
      0,
      as.numeric(difftime(
        pmin(end_local, hour_start_local + hours(1)),
        pmax(start_local, hour_start_local),
        units = "mins"
      ))
    ),
    hour_start_utc = with_tz(hour_start_local, tzone = "UTC")
  ) |>
  select(pid, platform, title_id, hour_start_local, hour_start_utc, minutes) |>
  group_by(pid, platform, title_id, hour_start_local, hour_start_utc) |>
  summarise(minutes = sum(minutes, na.rm = TRUE), .groups = "drop")

hourly_from_steam <- steam |>
  select(pid, title_id, datetime_hour_start, minutes) |>
  mutate(pid = as.character(pid)) |>
  left_join(tz_map, by = "pid") |>
  filter(!is.na(local_timezone)) |>
  mutate(
    platform = "Steam",
    hour_start_utc = datetime_hour_start,
    offset = get_dst_offset(datetime_hour_start, country, local_timezone),
    hour_start_local = datetime_hour_start + offset
  ) |>
  select(pid, platform, title_id, hour_start_local, hour_start_utc, minutes) |>
  group_by(pid, platform, title_id, hour_start_local, hour_start_utc) |>
  summarise(minutes = sum(minutes, na.rm = TRUE), .groups = "drop")

hourly_telemetry <- bind_rows(hourly_from_sessions, hourly_from_steam)

daily_telemetry <- hourly_telemetry |>
  mutate(day_local = as.Date(hour_start_local)) |>
  group_by(pid, platform, day_local) |>
  summarise(minutes = sum(minutes, na.rm = TRUE), .groups = "drop")

weekly_telemetry <- daily_telemetry |>
  mutate(week = floor_date(day_local, "week")) |>
  group_by(pid, platform, week) |>
  summarise(minutes = sum(minutes, na.rm = TRUE), .groups = "drop")

telemetry_spans <- daily_telemetry |>
  group_by(pid, platform) |>
  summarise(
    telemetry_start = min(day_local, na.rm = TRUE),
    telemetry_end = max(day_local, na.rm = TRUE) + hours(1),
    week = floor_date(telemetry_end, "week"),
    n_weeks = as.integer(difftime(
      telemetry_end,
      telemetry_start,
      units = "weeks"
    )) +
      1,
    .groups = "drop"
  )
```

## Survey Preparation

We calculate post-survey play windows (24h, 12h, 6h, and the 24h preceding
each survey) by joining hourly telemetry against survey timestamps, then
enrich the survey data with demographics and pre-classified activity
categories.

```{r}
#| label: prepare-survey
#| code-summary: "Show code (Prepare survey data and calculate play windows)"

surveys <- surveys |>
  filter(!bpnsfs_failed_att_check) |>
  mutate(wave = as.factor(wave))

play_24h <- surveys |>
  mutate(
    survey_time = as.POSIXct(date, tz = "UTC"),
    window_end = survey_time + hours(24)
  ) |>
  left_join(
    hourly_telemetry |> select(pid, hour_start_utc, minutes),
    by = join_by(
      pid,
      y$hour_start_utc >= x$survey_time,
      y$hour_start_utc < x$window_end
    )
  ) |>
  summarise(
    play_minutes_24h = sum(minutes, na.rm = TRUE),
    .by = c(pid, survey_time)
  )

play_12h <- surveys |>
  mutate(
    survey_time = as.POSIXct(date, tz = "UTC"),
    window_end = survey_time + hours(12)
  ) |>
  left_join(
    hourly_telemetry |> select(pid, hour_start_utc, minutes),
    by = join_by(
      pid,
      y$hour_start_utc >= x$survey_time,
      y$hour_start_utc < x$window_end
    )
  ) |>
  summarise(
    play_minutes_12h = sum(minutes, na.rm = TRUE),
    .by = c(pid, survey_time)
  )

play_6h <- surveys |>
  mutate(
    survey_time = as.POSIXct(date, tz = "UTC"),
    window_end = survey_time + hours(6)
  ) |>
  left_join(
    hourly_telemetry |> select(pid, hour_start_utc, minutes),
    by = join_by(
      pid,
      y$hour_start_utc >= x$survey_time,
      y$hour_start_utc < x$window_end
    )
  ) |>
  summarise(
    play_minutes_6h = sum(minutes, na.rm = TRUE),
    .by = c(pid, survey_time)
  )

play_24h_pre <- surveys |>
  mutate(
    survey_time = as.POSIXct(date, tz = "UTC"),
    window_start = survey_time - hours(24)
  ) |>
  left_join(
    hourly_telemetry |> select(pid, hour_start_utc, minutes),
    by = join_by(
      pid,
      y$hour_start_utc >= x$window_start,
      y$hour_start_utc < x$survey_time
    )
  ) |>
  summarise(
    play_minutes_24h_pre = sum(minutes, na.rm = TRUE),
    .by = c(pid, survey_time)
  )

intake_aux <- intake |>
  mutate(
    gender = ifelse(gender %in% c("Man", "Woman"), gender, "Non-binary/other"),
    across(wemwbs_1:wemwbs_7, ~ as.numeric(str_extract(.x, "^\\d+"))),
    wemwbs = rowMeans(pick(wemwbs_1:wemwbs_7), na.rm = TRUE)
  ) |>
  select(
    pid,
    age,
    gender,
    edu_level,
    employment,
    marital_status,
    wemwbs,
    diaries_completed,
    self_reported_weekly_play
  )

activity_categories <- read_csv("data/activity_categories.csv") |>
  mutate(wave = as.factor(wave))

surveys <- surveys |>
  mutate(survey_time = as.POSIXct(date, tz = "UTC")) |>
  left_join(play_24h, by = c("pid", "survey_time")) |>
  left_join(play_12h, by = c("pid", "survey_time")) |>
  left_join(play_6h, by = c("pid", "survey_time")) |>
  left_join(play_24h_pre, by = c("pid", "survey_time")) |>
  left_join(intake_aux, by = "pid") |>
  left_join(activity_categories, by = c("pid", "wave")) |>
  mutate(
    self_reported_played_24h = played24hr,
    telemetry_played_any_24h = play_minutes_24h > 0,
    telemetry_played_any_12h = play_minutes_12h > 0,
    telemetry_played_any_6h = play_minutes_6h > 0,
    telemetry_played_any_24h_pre = play_minutes_24h_pre > 0
  ) |>
  select(
    pid,
    wave,
    date,
    age,
    gender,
    edu_level,
    employment,
    marital_status,
    wemwbs,
    diaries_completed,
    self_reported_weekly_play,
    self_reported_played_24h,
    life_sat,
    bpnsfs_1,
    bpnsfs_2,
    bpnsfs_3,
    bpnsfs_4,
    bpnsfs_5,
    bpnsfs_6,
    bangs_1,
    bangs_2,
    bangs_3,
    bangs_4,
    bangs_5,
    bangs_6,
    displaced_core_domain,
    telemetry_played_any_24h,
    play_minutes_24h,
    telemetry_played_any_12h,
    play_minutes_12h,
    telemetry_played_any_6h,
    play_minutes_6h,
    telemetry_played_any_24h_pre,
    play_minutes_24h_pre
  )
```

## Exported Objects

The objects downstream pipeline stages need (`imputation.qmd`) are written
out here and re-exposed as individually `targets::tar_read()`-able targets in
`_targets.R` (see `R/targets/export.R` for the shared name list).

```{r}
#| label: export
#| code-summary: "Show code (Export objects for imputation.qmd)"

source("R/targets/export.R")
dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  preprocessing_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(preprocessing_export_names)} objects to data/exports/"))
```
