---
title: "Sensitivity analyses (computation)"
subtitle: "Fits the S1--S9 sensitivity models for 'All BANG, little buck'"
format:
  html:
    toc: true
    code-fold: true
    code-summary: "Show code"
knitr:
  opts_chunk:
    warning: false
    message: false
---

Fits every model behind the S1--S9 sensitivity analyses -- temporal-window
variants, a Bayesian random-slopes model, a continuous-outcome model, the
survey-completion-threshold sweep (S4), an interaction model, natural-spline
models, per-component and need-frustration models, and per-domain
displacement models. All run on the primary (full) sample except S2, which
stays on the >=15-survey subsample (see that chunk). The complete-case and
>=15-subsample H2 fits used by S4 come from `modelling.qmd`
(`h2_cc_pooled`, `h2_restricted_pooled`). Each fit is cached under
`data/models/`. The pooled results are read by the manuscript's appendix.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(glmmTMB)
library(lme4)
library(mice)
library(brms)
library(broom.mixed)
library(splines)
library(scales)
library(janitor)
library(targets)
```

```{r}
#| label: setup
#| code-summary: "Show code (Pipeline inputs)"

source("R/targets/export.R")
tar_load(c(
  dat,
  dat_restricted,
  dat_restricted_complete,
  m_imputations,
  surveys,
  activity_categories,
  h2_pooled,
  h2_restricted_pooled,
  h2_cc_pooled
))
```

## S1--S9 model fits
```{r}
#| label: s1-12h-model
#| output: false
#| code-summary: "Show code (S1: Fit models with 12-hour play window)"

# File-based caching to avoid re-running across multiple output formats
sens1_cache_file <- "data/models/sens1_fits.rds"
sens1_pooled_file <- "data/models/sens1_pooled.rds"

if (file.exists(sens1_cache_file) && file.exists(sens1_pooled_file)) {
  message("Loading cached S1 model fits")
  sens1_fits <- readRDS(sens1_cache_file)
  sens1_pooled <- readRDS(sens1_pooled_file)
} else {
  message("Fitting S1 models...")

  sens1_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S1 model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_12h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens1_pooled <- pool(sens1_fits)

  # Save to cache
  saveRDS(sens1_fits, sens1_cache_file)
  saveRDS(sens1_pooled, sens1_pooled_file)
  message("S1 models saved to cache")
}
```
```{r}
#| label: s1b-6h-model
#| output: false
#| code-summary: "Show code (S1b: Fit models with 6-hour play window)"

# File-based caching to avoid re-running across multiple output formats
sens1b_cache_file <- "data/models/sens1b_fits.rds"
sens1b_pooled_file <- "data/models/sens1b_pooled.rds"

if (file.exists(sens1b_cache_file) && file.exists(sens1b_pooled_file)) {
  message("Loading cached S1b model fits")
  sens1b_fits <- readRDS(sens1b_cache_file)
  sens1b_pooled <- readRDS(sens1b_pooled_file)
} else {
  message("Fitting S1b models...")

  sens1b_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S1b model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_6h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens1b_pooled <- pool(sens1b_fits)

  # Save to cache
  saveRDS(sens1b_fits, sens1b_cache_file)
  saveRDS(sens1b_pooled, sens1b_pooled_file)
  message("S1b models saved to cache")
}
```
```{r}
#| label: s1c-pre-model
#| output: false
#| code-summary: "Show code (S1c: Fit models with 24-hour pre-survey play window)"

# File-based caching to avoid re-running across multiple output formats
sens1c_cache_file <- "data/models/sens1c_fits.rds"
sens1c_pooled_file <- "data/models/sens1c_pooled.rds"

if (file.exists(sens1c_cache_file) && file.exists(sens1c_pooled_file)) {
  message("Loading cached S1c model fits")
  sens1c_fits <- readRDS(sens1c_cache_file)
  sens1c_pooled <- readRDS(sens1c_pooled_file)
} else {
  message("Fitting S1c models...")

  sens1c_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S1c model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h_pre ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens1c_pooled <- pool(sens1c_fits)

  # Save to cache
  saveRDS(sens1c_fits, sens1c_cache_file)
  saveRDS(sens1c_pooled, sens1c_pooled_file)
  message("S1c models saved to cache")
}
```
```{r}
#| label: s2-brms-model
#| output: false
#| code-summary: "Show code (S2: Fit Bayesian model with random slopes)"

# S2 probes the random-effects specification (the frequentist H2 could only
# fit random intercepts), not sample construction. It is therefore the one
# sensitivity analysis kept on the >=15-survey subsample: a full Bayesian
# multiple-imputation refit with random slopes over participants who completed
# a handful of surveys is disproportionate and prone to divergence.

# File-based caching to avoid re-running across multiple output formats
sens2_cache_file <- "data/models/sens2_fit.rds"

if (file.exists(sens2_cache_file)) {
  message("Loading cached S2 model fit")
  sens2_fit <- readRDS(sens2_cache_file)
} else {
  message("Fitting S2 Bayesian model...")

  # Complete cases from the >=15-survey subsample
  dat_cc <- dat_restricted_complete |>
    filter(
      !is.na(global_ns),
      !is.na(global_nf),
      !is.na(game_ns),
      !is.na(game_nf),
      !is.na(telemetry_played_any_24h)
    )

  # Fit Bayesian model with random slopes
  sens2_fit <- brm(
    telemetry_played_any_24h ~
      game_ns_cw +
      game_ns_cb +
      global_nf_cw +
      global_nf_cb +
      (1 + game_ns_cw + global_nf_cw | pid),
    family = bernoulli(),
    data = dat_cc,
    chains = 4,
    cores = 4,
    iter = 5000,
    warmup = 1000,
    seed = 8675309
  )

  # Save to cache
  saveRDS(sens2_fit, sens2_cache_file)
  message("S2 model saved to cache")
}
```

```{r}
#| label: s2-bayes-extract
#| output: false
#| code-summary: "Show code (Extract Bayesian fixed effects for the S2 table)"

s2_bayes_fixed <- summary(sens2_fit)$fixed |> as_tibble(rownames = "term")
```

```{r}
#| label: s2-oneslope-models
#| output: false
#| code-summary: "Show code (S2: Fit H2 models with one random slope at a time)"

# File-based caching to avoid re-running across multiple output formats
sens2_h2a_cache <- "data/models/sens2_h2a_fits.rds"
sens2_h2a_pooled_cache <- "data/models/sens2_h2a_pooled.rds"
sens2_h2b_cache <- "data/models/sens2_h2b_fits.rds"
sens2_h2b_pooled_cache <- "data/models/sens2_h2b_pooled.rds"

if (
  file.exists(sens2_h2a_cache) &&
    file.exists(sens2_h2a_pooled_cache) &&
    file.exists(sens2_h2b_cache) &&
    file.exists(sens2_h2b_pooled_cache)
) {
  message("Loading cached S2 one-slope model fits")
  s2_h2a_fits <- readRDS(sens2_h2a_cache)
  s2_h2a_pooled <- readRDS(sens2_h2a_pooled_cache)
  s2_h2b_fits <- readRDS(sens2_h2b_cache)
  s2_h2b_pooled <- readRDS(sens2_h2b_pooled_cache)
} else {
  message("Fitting S2 one-slope models...")

  # H2a: Random slope for game_ns_cw only (>=15-survey subsample, as above)
  message("Fitting S2 H2a models...")
  s2_h2a_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S2 H2a model to imputation {i} of {m_imputations}"))
    dat_i <- dat_restricted |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 + game_ns_cw | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  s2_h2a_pooled <- pool(s2_h2a_fits)

  # H2b: Random slope for global_nf_cw only (>=15-survey subsample, as above)
  message("Fitting S2 H2b models...")
  s2_h2b_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S2 H2b model to imputation {i} of {m_imputations}"))
    dat_i <- dat_restricted |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 + global_nf_cw | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  s2_h2b_pooled <- pool(s2_h2b_fits)

  # Save to cache
  saveRDS(s2_h2a_fits, sens2_h2a_cache)
  saveRDS(s2_h2a_pooled, sens2_h2a_pooled_cache)
  saveRDS(s2_h2b_fits, sens2_h2b_cache)
  saveRDS(s2_h2b_pooled, sens2_h2b_pooled_cache)
  message("S2 one-slope models saved to cache")
}
```
```{r}
#| label: s3-playvolume-model
#| output: false
#| code-summary: "Show code (S3: Fit models predicting continuous play volume)"

# File-based caching to avoid re-running across multiple output formats
sens3_cache_file <- "data/models/sens3_fits.rds"
sens3_pooled_file <- "data/models/sens3_pooled.rds"

if (file.exists(sens3_cache_file) && file.exists(sens3_pooled_file)) {
  message("Loading cached S3 model fits")
  sens3_fits <- readRDS(sens3_cache_file)
  sens3_pooled <- readRDS(sens3_pooled_file)
} else {
  message("Fitting S3 models...")

  # Fit model to each imputed dataset
  sens3_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S3 model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      play_minutes_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = gaussian()
    )
  })

  sens3_pooled <- pool(sens3_fits)

  # Save to cache
  saveRDS(sens3_fits, sens3_cache_file)
  saveRDS(sens3_pooled, sens3_pooled_file)
  message("S3 models saved to cache")
}
```
```{r}
#| label: threshold-imputations
#| output: false
#| code-summary: "Show code (S4: Run imputations across completion thresholds)"

# Imputation function for threshold sensitivity analysis (S6)
# Replicates primary imputation pipeline for a given min-waves cutoff
# M=10 is sufficient for a robustness check; results cached per threshold
run_threshold <- function(min_waves, m = 10) {
  cache_file <- glue("data/models/threshold_{min_waves}_imp.csv.gz")

  if (file.exists(cache_file)) {
    message(glue("Loading threshold={min_waves} imputation from cache"))
    return(read_csv(cache_file, show_col_types = FALSE) |> as.mids())
  }

  message(glue(
    "Running imputation for threshold={min_waves} (M={m}), started {Sys.time()}"
  ))

  sw <- surveys |>
    filter(diaries_completed >= min_waves) |>
    select(
      pid,
      wave,
      age,
      gender,
      edu_level,
      employment,
      marital_status,
      wemwbs,
      diaries_completed,
      self_reported_weekly_play,
      self_reported_played_24h,
      displaced_core_domain,
      bpnsfs_1,
      bpnsfs_2,
      bpnsfs_3,
      bpnsfs_4,
      bpnsfs_5,
      bpnsfs_6,
      bangs_1,
      bangs_2,
      bangs_3,
      bangs_4,
      bangs_5,
      bangs_6
    ) |>
    pivot_wider(
      id_cols = c(
        pid,
        age,
        gender,
        edu_level,
        employment,
        marital_status,
        wemwbs,
        diaries_completed,
        self_reported_weekly_play
      ),
      names_from = wave,
      values_from = c(
        self_reported_played_24h,
        displaced_core_domain,
        bpnsfs_1,
        bpnsfs_2,
        bpnsfs_3,
        bpnsfs_4,
        bpnsfs_5,
        bpnsfs_6,
        bangs_1,
        bangs_2,
        bangs_3,
        bangs_4,
        bangs_5,
        bangs_6
      ),
      names_sep = "_w"
    )

  played_vars_t <- grep("^self_reported_played_24h_w", names(sw), value = TRUE)
  bpnsfs_vars_t <- grep("^bpnsfs_[1-6]_w", names(sw), value = TRUE)
  bangs_vars_t <- grep("^bangs_[1-6]_w", names(sw), value = TRUE)
  displaced_vars_t <- grep("^displaced_core_domain_w", names(sw), value = TRUE)

  methods_t <- setNames(rep("", ncol(sw)), names(sw))
  methods_t[played_vars_t] <- "logreg"
  methods_t[c(bpnsfs_vars_t, bangs_vars_t, displaced_vars_t)] <- "pmm"
  methods_t[c(
    "pid",
    "age",
    "gender",
    "edu_level",
    "employment",
    "marital_status",
    "wemwbs",
    "diaries_completed",
    "self_reported_weekly_play"
  )] <- ""

  where_t <- is.na(sw)
  for (bv in bangs_vars_t) {
    wave_num <- str_extract(bv, "\\d+$")
    pv <- paste0("self_reported_played_24h_w", wave_num)
    if (pv %in% names(sw)) {
      where_t[sw[[pv]] == "No" & is.na(sw[[bv]]), bv] <- FALSE
    }
  }

  pred_t <- quickpred(
    sw,
    mincor = 0.3,
    minpuc = 0.3,
    include = c("age", "wemwbs", "self_reported_weekly_play"),
    exclude = c(
      "pid",
      "gender",
      "edu_level",
      "employment",
      "marital_status",
      "diaries_completed"
    )
  )

  imp_t <- futuremice(
    data = sw,
    m = m,
    method = methods_t,
    predictorMatrix = pred_t,
    where = where_t,
    maxit = 5,
    n.core = parallel::detectCores() - 1,
    parallelseed = 8675309
  )

  message(glue("Completed threshold={min_waves} imputation {Sys.time()}"))
  imp_long_t <- complete(imp_t, action = "long", include = TRUE)
  dir.create("data/models", showWarnings = FALSE, recursive = TRUE)
  write_csv(imp_long_t, cache_file)
  as.mids(imp_long_t)
}

threshold_values <- c(10, 12, 15, 18, 20, 24)
threshold_imps <- map(threshold_values, run_threshold)
names(threshold_imps) <- threshold_values
```
```{r}
#| label: s4-threshold-models
#| output: false
#| code-summary: "Show code (S4: Fit H2 models across completion thresholds)"

# Post-process each threshold's imputation: composites, centering, telemetry join
process_threshold <- function(imp_t, min_waves) {
  telemetry_t <- surveys |>
    filter(diaries_completed >= min_waves) |>
    select(
      pid,
      wave,
      telemetry_played_any_24h,
      play_minutes_24h,
      telemetry_played_any_12h,
      play_minutes_12h,
      telemetry_played_any_6h,
      play_minutes_6h,
      telemetry_played_any_24h_pre,
      play_minutes_24h_pre
    )

  complete(imp_t, action = "long", include = TRUE) |>
    pivot_longer(
      cols = -c(
        .imp,
        .id,
        pid,
        age,
        gender,
        edu_level,
        employment,
        marital_status,
        wemwbs,
        diaries_completed,
        self_reported_weekly_play
      ),
      names_to = c(".value", "wave"),
      names_pattern = "(.+)_w(.+)"
    ) |>
    mutate(wave = as.factor(wave)) |>
    mutate(
      global_ns = rowMeans(pick(bpnsfs_1, bpnsfs_3, bpnsfs_5), na.rm = TRUE),
      global_nf = rowMeans(pick(bpnsfs_2, bpnsfs_4, bpnsfs_6), na.rm = TRUE),
      game_ns = rowMeans(pick(bangs_1, bangs_3, bangs_5), na.rm = TRUE),
      game_nf = rowMeans(pick(bangs_2, bangs_4, bangs_6), na.rm = TRUE)
    ) |>
    left_join(telemetry_t, by = c("pid", "wave")) |>
    group_by(.imp, pid) |>
    mutate(
      global_ns_pm = mean(global_ns, na.rm = TRUE),
      global_nf_pm = mean(global_nf, na.rm = TRUE),
      game_ns_pm = mean(game_ns, na.rm = TRUE)
    ) |>
    ungroup() |>
    group_by(.imp) |>
    mutate(
      global_ns_gm = mean(global_ns_pm, na.rm = TRUE),
      global_nf_gm = mean(global_nf_pm, na.rm = TRUE),
      game_ns_gm = mean(game_ns_pm, na.rm = TRUE),
      global_ns_cw = global_ns - global_ns_pm,
      global_nf_cw = global_nf - global_nf_pm,
      game_ns_cw = game_ns - game_ns_pm,
      global_ns_cb = global_ns_pm - global_ns_gm,
      global_nf_cb = global_nf_pm - global_nf_gm,
      game_ns_cb = game_ns_pm - game_ns_gm
    ) |>
    ungroup() |>
    filter(.imp > 0)
}

# Fit the primary H2 model on each threshold's data and pool
fit_h2_threshold <- function(dat_t, min_waves) {
  cache_file <- glue("data/models/threshold_{min_waves}_h2_pooled.rds")

  if (file.exists(cache_file)) {
    message(glue("Loading threshold={min_waves} H2 pooled from cache"))
    return(readRDS(cache_file))
  }

  m <- max(as.integer(dat_t$.imp))
  fits <- lapply(1:m, function(i) {
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = filter(dat_t, .imp == i),
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  pooled <- pool(fits)
  saveRDS(pooled, cache_file)
  pooled
}

threshold_results <- map2(
  threshold_imps,
  threshold_values,
  function(imp_t, min_waves) {
    dat_t <- process_threshold(imp_t, min_waves)
    pooled_t <- fit_h2_threshold(dat_t, min_waves)

    summary(pooled_t) |>
      as_tibble() |>
      filter(term %in% c("game_ns_cw", "global_nf_cw")) |>
      mutate(
        min_waves = min_waves,
        lo = estimate - 1.96 * std.error,
        hi = estimate + 1.96 * std.error,
        coefficient = case_when(
          term == "game_ns_cw" ~ "H2a: Game need satisfaction",
          term == "global_nf_cw" ~ "H2b: Global need frustration"
        )
      )
  }
) |>
  list_rbind()
```
```{r}
#| label: s4-combined-results
#| code-summary: "Show code (S4: Combine sample-robustness results into one set of estimates)"

# Pull the two focal H2 coefficients from a pooled model, in a common format
extract_h2_terms <- function(pooled) {
  summary(pooled) |>
    as_tibble() |>
    filter(term %in% c("game_ns_cw", "global_nf_cw")) |>
    mutate(
      coefficient = case_when(
        term == "game_ns_cw" ~ "H2a: Game need satisfaction",
        term == "global_nf_cw" ~ "H2b: Global need frustration"
      ),
      lo = estimate - 1.96 * std.error,
      hi = estimate + 1.96 * std.error
    ) |>
    select(
      term,
      coefficient,
      estimate,
      std.error,
      statistic,
      df,
      p.value,
      lo,
      hi
    )
}

spec_levels <- c(
  "Complete cases",
  "10",
  "12",
  ">=15 subsample",
  "18",
  "20",
  "24",
  "Full sample (primary)"
)

sample_results <- bind_rows(
  # Complete-case and >=15-subsample H2 fits come from modelling.qmd (M=27),
  # so they match what the main text reports; the threshold sweep is a lighter
  # M=10 refit that only needs to show the estimate is flat across cutoffs.
  extract_h2_terms(h2_cc_pooled) |> mutate(spec = "Complete cases"),
  threshold_results |>
    filter(min_waves != 15) |>
    mutate(spec = as.character(min_waves)) |>
    select(
      term,
      coefficient,
      estimate,
      std.error,
      statistic,
      df,
      p.value,
      lo,
      hi,
      spec
    ),
  extract_h2_terms(h2_restricted_pooled) |> mutate(spec = ">=15 subsample"),
  extract_h2_terms(h2_pooled) |> mutate(spec = "Full sample (primary)")
) |>
  mutate(
    spec = factor(spec, levels = spec_levels),
    is_primary = spec == "Full sample (primary)"
  )
```
```{r}
#| label: s5-interaction-model
#| output: false
#| code-summary: "Show code (S5: Fit models with game NS × global NF interaction)"

# File-based caching to avoid re-running across multiple output formats
sens5b_cache_file <- "data/models/sens5b_fits.rds"
sens5b_pooled_file <- "data/models/sens5b_pooled.rds"

if (file.exists(sens5b_cache_file) && file.exists(sens5b_pooled_file)) {
  message("Loading cached S5 model fits")
  sens5b_fits <- readRDS(sens5b_cache_file)
  sens5b_pooled <- readRDS(sens5b_pooled_file)
} else {
  message("Fitting S5 models...")

  sens5b_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S5 model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        game_ns_cw:global_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens5b_pooled <- pool(sens5b_fits)

  # Save to cache
  saveRDS(sens5b_fits, sens5b_cache_file)
  saveRDS(sens5b_pooled, sens5b_pooled_file)
  message("S5 models saved to cache")
}
```
```{r}
#| label: s6-spline-model
#| output: false
#| code-summary: "Show code (S6: Fit H2 model with natural splines)"

# First imputation only (the linear-vs-spline comparison is illustrative).
# Created outside caching so it's available for plotting.
dat_imp1 <- dat |>
  filter(.imp == 1) |>
  select(
    pid,
    wave,
    date,
    telemetry_played_any_24h,
    game_ns_cw,
    game_ns_cb,
    global_nf_cw,
    global_nf_cb
  ) |>
  filter(complete.cases(pick(everything())))

# File-based caching
sens8_linear_file <- "data/models/sens8_linear.rds"
sens8_spline_file <- "data/models/sens8_spline.rds"

if (file.exists(sens8_linear_file) && file.exists(sens8_spline_file)) {
  message("Loading cached S6 models")
  sens8_linear <- readRDS(sens8_linear_file)
  sens8_spline <- readRDS(sens8_spline_file)
} else {
  message("Fitting S6 models (linear vs spline)...")

  # Linear model (for comparison)
  sens8_linear <- glmmTMB(
    telemetry_played_any_24h ~
      game_ns_cw +
      game_ns_cb +
      global_nf_cw +
      global_nf_cb +
      (1 | pid) +
      ar1(factor(wave) + 0 | pid),
    data = dat_imp1,
    family = binomial(link = "logit")
  )

  # Spline model with natural splines (3 df) on within-person predictors
  sens8_spline <- glmmTMB(
    telemetry_played_any_24h ~
      ns(game_ns_cw, df = 3) +
      game_ns_cb +
      ns(global_nf_cw, df = 3) +
      global_nf_cb +
      (1 | pid) +
      ar1(factor(wave) + 0 | pid),
    data = dat_imp1,
    family = binomial(link = "logit")
  )

  # Cache results
  dir.create("data/models", showWarnings = FALSE, recursive = TRUE)
  saveRDS(sens8_linear, sens8_linear_file)
  saveRDS(sens8_spline, sens8_spline_file)
}
```
```{r}
#| label: s7-components-prep
#| code-summary: "Show code (Prepare data with separate needs components)"
#| output: false

# File-based caching to avoid re-running across multiple output formats
sens9_cache_file <- "data/models/sens9_models.rds"

if (file.exists(sens9_cache_file)) {
  message("Loading cached S7 model fits")
  sens9_cached <- readRDS(sens9_cache_file)
  sens9_h2_aut <- sens9_cached$h2_aut
  sens9_h2_com <- sens9_cached$h2_com
  sens9_h2_rel <- sens9_cached$h2_rel
} else {
  message("Fitting S7 models...")

  # Prepare component-level data for each imputation
  sens9_data <- lapply(1:m_imputations, function(i) {
    message(glue("Preparing S7 data for imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)

    # Calculate person means for each component (game and global)
    dat_i <- dat_i |>
      group_by(pid) |>
      mutate(
        # Game needs
        game_aut_pm = mean(bangs_1, na.rm = TRUE),
        game_com_pm = mean(bangs_3, na.rm = TRUE),
        game_rel_pm = mean(bangs_5, na.rm = TRUE),
        # Global need frustration
        global_aut_nf_pm = mean(bpnsfs_2, na.rm = TRUE),
        global_com_nf_pm = mean(bpnsfs_4, na.rm = TRUE),
        global_rel_nf_pm = mean(bpnsfs_6, na.rm = TRUE)
      ) |>
      ungroup() |>
      # Calculate grand means
      mutate(
        # Game needs
        game_aut_gm = mean(game_aut_pm, na.rm = TRUE),
        game_com_gm = mean(game_com_pm, na.rm = TRUE),
        game_rel_gm = mean(game_rel_pm, na.rm = TRUE),
        # Global need frustration
        global_aut_nf_gm = mean(global_aut_nf_pm, na.rm = TRUE),
        global_com_nf_gm = mean(global_com_nf_pm, na.rm = TRUE),
        global_rel_nf_gm = mean(global_rel_nf_pm, na.rm = TRUE)
      ) |>
      # Within/between centering
      mutate(
        # Game needs
        game_aut_cw = bangs_1 - game_aut_pm,
        game_aut_cb = game_aut_pm - game_aut_gm,
        game_com_cw = bangs_3 - game_com_pm,
        game_com_cb = game_com_pm - game_com_gm,
        game_rel_cw = bangs_5 - game_rel_pm,
        game_rel_cb = game_rel_pm - game_rel_gm,
        # Global need frustration
        global_aut_nf_cw = bpnsfs_2 - global_aut_nf_pm,
        global_aut_nf_cb = global_aut_nf_pm - global_aut_nf_gm,
        global_com_nf_cw = bpnsfs_4 - global_com_nf_pm,
        global_com_nf_cb = global_com_nf_pm - global_com_nf_gm,
        global_rel_nf_cw = bpnsfs_6 - global_rel_nf_pm,
        global_rel_nf_cb = global_rel_nf_pm - global_rel_nf_gm
      )

    return(dat_i)
  })

  # H2 models: game component + matching global NF component → play
  message("Fitting S7 H2 autonomy models...")
  sens9_h2_aut <- pool(lapply(sens9_data, function(dat) {
    glmmTMB(
      telemetry_played_any_24h ~ game_aut_cw +
        global_aut_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  }))

  message("Fitting S7 H2 competence models...")
  sens9_h2_com <- pool(lapply(sens9_data, function(dat) {
    glmmTMB(
      telemetry_played_any_24h ~ game_com_cw +
        global_com_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  }))

  message("Fitting S7 H2 relatedness models...")
  sens9_h2_rel <- pool(lapply(sens9_data, function(dat) {
    glmmTMB(
      telemetry_played_any_24h ~ game_rel_cw +
        global_rel_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  }))

  # Save to cache
  saveRDS(
    list(
      h2_aut = sens9_h2_aut,
      h2_com = sens9_h2_com,
      h2_rel = sens9_h2_rel
    ),
    sens9_cache_file
  )
  message("S7 models saved to cache")
}
```
```{r}
#| label: s8-game-nf-model
#| output: false
#| code-summary: "Show code (S8: Fit model with game NF predicting play)"

# File-based caching
sens10_cache_file <- "data/models/sens10_fits.rds"
sens10_pooled_file <- "data/models/sens10_pooled.rds"

if (file.exists(sens10_pooled_file)) {
  message("Loading cached S8 pooled results")
  sens10_pooled <- readRDS(sens10_pooled_file)
} else {
  message("Fitting S8 models...")

  # Prepare data with game_nf centered
  sens10_data <- lapply(1:m_imputations, function(i) {
    dat_i <- dat |> filter(.imp == i)

    dat_i |>
      group_by(pid) |>
      mutate(
        game_nf_pm = mean(game_nf, na.rm = TRUE)
      ) |>
      ungroup() |>
      mutate(
        game_nf_gm = mean(game_nf_pm, na.rm = TRUE),
        game_nf_cw = game_nf - game_nf_pm,
        game_nf_cb = game_nf_pm - game_nf_gm
      )
  })

  # Fit models
  sens10_fits <- lapply(sens10_data, function(dat_i) {
    glmmTMB::glmmTMB(
      telemetry_played_any_24h ~
        game_nf_cw +
        game_nf_cb +
        (1 | pid),
      family = binomial(link = "logit"),
      data = dat_i,
      control = glmmTMBControl(
        optimizer = optim,
        optArgs = list(method = "BFGS")
      )
    )
  })

  # Pool results
  sens10_pooled <- pool(sens10_fits)

  # Save to cache
  saveRDS(sens10_fits, sens10_cache_file)
  saveRDS(sens10_pooled, sens10_pooled_file)
  message("S8 models saved to cache")
}
```
```{r}
#| label: s9-h3-by-domain-prep
#| code-summary: "Show code (S9: Prepare domain-specific displacement indicators)"

# Create domain-specific displacement indicators
dat_domains <- dat |>
  left_join(
    activity_categories |> select(pid, wave, activity_label),
    by = c("pid", "wave")
  ) |>
  mutate(
    displaced_work_school = activity_label == "work_school",
    displaced_social = activity_label == "social_engagement",
    displaced_health_sleep = activity_label == "sleep_eat_fitness",
    displaced_caretaking = activity_label == "caretaking"
  )
```
```{r}
#| label: s9-h3-by-domain-models
#| output: false
#| code-summary: "Show code (S9: Fit H3 models for each core life domain)"

# File-based caching
s10_cache_file <- "data/models/s11_fits.rds"
s10_pooled_file <- "data/models/s11_pooled.rds"

if (file.exists(s10_cache_file) && file.exists(s10_pooled_file)) {
  message("Loading cached S9 model fits")
  s10_fits <- readRDS(s10_cache_file)
  s10_pooled <- readRDS(s10_pooled_file)
} else {
  message("Fitting S9 models...")

  # Fit separate model for each domain
  domains <- c(
    "displaced_work_school",
    "displaced_social",
    "displaced_health_sleep",
    "displaced_caretaking"
  )

  s10_fits <- list()
  s10_pooled <- list()

  for (domain in domains) {
    message(glue("Fitting model for {domain}"))

    # Filter to only observations where this specific domain could be displaced
    # (i.e., where the activity_label indicates this domain or other)
    domain_fits <- lapply(1:m_imputations, function(i) {
      dat_i <- dat_domains |>
        filter(.imp == i, !is.na(!!sym(domain)))

      glmmTMB(
        as.formula(glue(
          "global_ns ~ {domain} + (1 + {domain} | pid) + ar1(wave + 0 | pid)"
        )),
        data = dat_i
      )
    })

    s10_fits[[domain]] <- domain_fits
    s10_pooled[[domain]] <- pool(domain_fits)
  }

  # Save to cache
  dir.create("data/models", showWarnings = FALSE, recursive = TRUE)
  saveRDS(s10_fits, s10_cache_file)
  saveRDS(s10_pooled, s10_pooled_file)
  message("S9 models saved to cache")
}
```

## Exported Objects

```{r}
#| label: export
#| code-summary: "Show code (Export pooled results for the manuscript appendix)"

dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  sensitivity_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(sensitivity_export_names)} objects to data/exports/"))
```
