---
title: "Study B: PowerWash Simulator"
subtitle: "Session data preparation and behavioural models for 'All BANG, little buck'"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

Prepares the *PowerWash Simulator* (PWS) session data -- OSF download,
segmentation of in-game experience prompts into play sessions, and
within/between-person centering of session-level need satisfaction -- and
fits the two exploratory behavioural models for Study B: session length and
time to the next session. PWS is a separate dataset from Study A and shares
no data with it.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(lme4)
library(janitor)
```

```{r}
#| label: source-functions
#| code-summary: "Show code (Load pipeline functions)"

source("R/targets/export.R")
```

## Data Sources

PWS data are downloaded from OSF on first run and cached locally (the archive
is large, ~800 MB). Only `study_prompt_answered.csv` is extracted.

```{r}
#| label: data-download
#| code-summary: "Show code (Download PWS data from OSF)"

path_pws <- "data/pws/pws_data.zip"
if (!file.exists(path_pws)) {
  dir.create("data/pws", showWarnings = FALSE, recursive = TRUE)
  options(timeout = max(600, getOption("timeout")))
  download.file(
    url = "https://osf.io/download/j48qf/",
    destfile = path_pws
  )
}

# Extract only the study_prompt_answered.csv file we need
if (!file.exists("data/pws/study_prompt_answered.csv")) {
  unzip(
    zipfile = path_pws,
    files = "data/study_prompt_answered.csv",
    exdir = "data/pws",
    junkpaths = TRUE
  )
}
```

## Session Preparation

In-game experience prompts are grouped into play sessions (continuous
activity separated by gaps of at least 30 minutes), each session's autonomy
and competence ratings averaged into a single game need-satisfaction
indicator, and session length / session gap derived from the timestamps.
Need satisfaction is then decomposed into within- and between-person
components. The processed session table is cached to
`data/pws/pws_sessions.csv`.

```{r}
#| label: session-prep
#| code-summary: "Show code (Prepare PWS session data)"

if (!file.exists("data/pws/pws_sessions.csv")) {
  # Load and process prompts
  pws_raw <- read_csv(
    "data/pws/study_prompt_answered.csv",
    col_select = c(
      pid,
      time = Time_utc,
      duration = CurrentSessionLength,
      prompt = LastStudyPromptType,
      response
    ),
    show_col_types = FALSE
  ) |>
    mutate(
      pid = factor(pid),
      # The raw VAS responses are stored on a 0-1000 internal scale (not the
      # documented 0-100 -- confirmed via schema.sql and the observed range/
      # granularity of `response`, consistent across all six prompt types),
      # so we divide by 1000 to recover a 0-1 fraction, then rescale that to
      # a 1-7 scale matching Study A's BANGS items.
      response = 1 + (response / 1000) * 6
    ) |>
    arrange(pid, time) |>
    mutate(
      # Calculate time since last prompt in minutes
      time_since_last = as.numeric(
        difftime(
          time,
          lag(time, 1, default = as_datetime("1970-01-01")),
          units = "mins"
        )
      ),
      # New session if gap > 30 minutes
      new_session = time_since_last > 30,
      session = cumsum(new_session),
      .by = pid
    ) |>
    select(-time_since_last)

  # Save prompt-level data for troubleshooting (includes all prompt times)
  pws_prompts_detail <- pws_raw |>
    select(-new_session) |>
    group_by(pid, session) |>
    filter(n() > 1) |>
    mutate(
      prompt_time = time,
      first_time = first(time),
      first_duration = first(duration),
      startTime = if_else(
        first_duration < 15,
        first_time - first_duration * 60,
        first_time
      ),
      startTime = min(startTime),
      endTime = max(time),
      sessionLength = round(as.integer(endTime - startTime) / 60, 2)
    ) |>
    ungroup() |>
    select(
      pid,
      session,
      prompt_time,
      prompt,
      response,
      duration,
      startTime,
      endTime,
      sessionLength
    )

  # Summarize for analysis
  pws_prompts <- pws_raw |>
    select(-new_session) |>
    group_by(pid, session) |>
    filter(n() > 1) |>
    mutate(
      first_time = first(time),
      first_duration = first(duration),
      startTime = if_else(
        first_duration < 15,
        first_time - first_duration * 60,
        first_time
      ),
      startTime = min(startTime),
      endTime = max(time)
    ) |>
    select(-first_time, -first_duration) |>
    group_by(pid, session, prompt) |>
    summarise(
      numPrompts = n(),
      mean = mean(response, na.rm = TRUE),
      startTime = first(startTime),
      endTime = first(endTime),
      .groups = "drop"
    ) |>
    mutate(
      sessionLength = round(as.integer(endTime - startTime) / 60, 2),
      mean = ifelse(is.nan(mean), NA_real_, mean)
    )

  # Convert to wide format
  pws_wide <- pws_prompts |>
    filter(sessionLength > 5 & sessionLength < 480) |>
    pivot_wider(
      id_cols = c(pid, session, startTime, endTime, sessionLength),
      names_from = prompt,
      values_from = c(numPrompts, mean),
      names_sort = TRUE
    ) |>
    select(-contains("_NA")) |>
    janitor::clean_names() |>
    group_by(pid) |>
    mutate(
      session_gap = lead(start_time, 1) - end_time,
      session_gap = round(as.integer(session_gap) / 60 / 60, 2),
      prev_session_length = lag(session_length, 1),
      prev_session_gap = lag(session_gap, 1),
      # Combine autonomy and competence into game need satisfaction
      game_ns = (mean_autonomy + mean_competence) / 2,
      # Calculate person means
      game_ns_pm = mean(game_ns, na.rm = TRUE),
      session_length_pm = mean(session_length, na.rm = TRUE),
      session_gap_pm = mean(session_gap, na.rm = TRUE)
    ) |>
    ungroup() |>
    # Calculate grand means and centered values
    mutate(
      game_ns_gm = mean(game_ns_pm, na.rm = TRUE),
      session_length_gm = mean(session_length_pm, na.rm = TRUE),
      session_gap_gm = mean(session_gap_pm, na.rm = TRUE),
      # Within-person centered (deviation from person mean)
      game_ns_cw = game_ns - game_ns_pm,
      session_length_cw = session_length - session_length_pm,
      session_gap_cw = session_gap - session_gap_pm,
      # Between-person centered (person mean - grand mean)
      game_ns_cb = game_ns_pm - game_ns_gm,
      session_length_cb = session_length_pm - session_length_gm,
      session_gap_cb = session_gap_pm - session_gap_gm
    ) |>
    select(
      pid,
      session,
      session_length,
      session_gap,
      prev_session_length,
      prev_session_gap,
      everything()
    )

  write_csv(pws_wide, "data/pws/pws_sessions.csv")
  write_csv(pws_prompts_detail, "data/pws/pws_prompts_detail.csv")
} else {
  pws_wide <- read_csv("data/pws/pws_sessions.csv", show_col_types = FALSE)
  pws_prompts_detail <- read_csv(
    "data/pws/pws_prompts_detail.csv",
    show_col_types = FALSE
  )
}

pws_n_players <- length(unique(pws_wide$pid))
pws_n_sessions <- nrow(pws_wide)

message(glue(
  "PWS sessions: {pws_n_sessions} sessions across {pws_n_players} players"
))
```

## Behavioural Models

Two linear mixed models (log outcomes, random intercepts and slopes for
within-person need satisfaction), each controlling for the previous session's
value of the outcome. Pooling/prediction and inline reporting happen in the
manuscript.

```{r}
#| label: models
#| code-summary: "Show code (Fit PWS session-length and session-gap models)"

# Model 1: Session length ~ game need satisfaction
pws_m1 <- lme4::lmer(
  log(session_length) ~
    game_ns_cw +
    game_ns_cb +
    prev_session_length +
    (1 + game_ns_cw | pid),
  data = pws_wide
)

# Model 2: Session gap ~ game need satisfaction
pws_m2 <- lme4::lmer(
  log(session_gap) ~
    game_ns_cw +
    game_ns_cb +
    prev_session_gap +
    (1 + game_ns_cw | pid),
  data = pws_wide |> filter(!is.na(session_gap))
)
```

## Exported Objects

```{r}
#| label: export
#| code-summary: "Show code (Export objects for the manuscript and supplement)"

dir.create("data/exports", showWarnings = FALSE, recursive = TRUE)
walk(
  studyb_export_names,
  ~ saveRDS(get(.x), file.path("data/exports", paste0(.x, ".rds")))
)
message(glue("Exported {length(studyb_export_names)} objects to data/exports/"))
```
