---
title: "Supplement"
subtitle: "Appendix, full model outputs, and sensitivity analyses for 'All BANG, little buck'"
bibliography: references.bib
csl: https://www.zotero.org/styles/apa
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    number-sections: true
    embed-resources: false
knitr:
  opts_chunk:
    warning: false
    message: false
---

This document holds everything the manuscript defers to the appendix: the
Stage 1 design table, complete model summaries, imputation diagnostics, and
the S1--S9 sensitivity analyses. It is its own `targets` stage
(`supplement_report`) and reads the fitted models and analysis datasets from
the pipeline via `targets::tar_load()`.

The sensitivity analyses fit a large number of models (including a Bayesian
`brms` model and several imputation variants). Each keeps its own
file-based cache under `data/models/`, so a prose edit re-renders in seconds
without refitting; only a deleted cache triggers a re-fit.

```{r}
#| label: libraries
#| code-summary: "Show code (Load required packages)"

library(tidyverse)
library(glue)
library(glmmTMB)
library(lme4)
library(mice)
library(brms)
library(broom.mixed)
library(marginaleffects)
library(modelsummary)
library(tinytable)
library(splines)
library(patchwork)
library(scales)
library(janitor)
library(targets)
```

```{r}
#| label: setup
#| code-summary: "Show code (Presentation constants and pipeline inputs)"

source("R/helpers.R") # labels, clean_results()

tar_load(c(
  dat, dat_desc, dat_observed, m_imputations,
  surveys, activity_categories,
  h1mod, h2mod, h3mod, h1_pooled, h2_pooled, h3_pooled,
  pws_m1, pws_m2
))

# Derived from surveys (not exported separately): every participant with any
# enriched survey data, before the >=15-wave analytical-sample filter.
full_eligible_pids <- unique(surveys$pid)
```

# Appendix

## Design Table

The following is the Design Table from the Stage 1 Registered Report [@BallouEtAl2025Psychological], reproduced verbatim with the addition of an Observed Outcome column. 

```{r}
#| label: tbl-design
#| tbl-cap: "Study A design table"
#| code-summary: "Show code (Design table)"

tibble(
  `Research Question` = c(
    "Does in-game need satisfaction contribute to overall need satisfaction?",
    "Do positive play experiences result in more frequent future play behavior?",
    "Do players compensate for frustrated needs using games?",
    "Is the displacement of core life domains more associated with harm than non-core domains?"
  ),
  Hypothesis = c(
    "H1. When individuals' in-game needs are better satisfied, they report greater global need satisfaction.",
    "H2a. When individuals' in-game need satisfaction is higher, they are more likely to play video games in the 24-hour period after survey completion.",
    "H2b. When individuals' global need frustration is higher, they are more likely to play video games in the 24-hour period after survey completion.",
    "H3. When a person's most recent gaming displaced a core life domain (work/school, social engagements, sleep/eating/fitness, or caretaking), their global need satisfaction will be lower."
  ),
  `Sampling Plan` = c(
    "1,000 US adults, completing a diary study over 30 days. The hypotheses in Study A are better-suited to the diary study data, and therefore do not use the panel data (and by extension, the UK sample). The telemetry data in Study A consists of Xbox, Nintendo, and Steam.",
    "",
    "",
    ""
  ),
  `Analysis Plan†` = c(
    "Multilevel within-between linear regression whereby within-person centered game-level need satisfaction (gameNS_cw) predicts deviation from a person's typical global need satisfaction (globalNS). glmmTMB(globalNS ~ gameNS_cw + gameNS_cb + (1 + gameNS_cw | pid) + ar1(day + 0 | pid))",
    "Multilevel logistic regression with the binary presence or absence of playtime in the subsequent 24 hours from survey completion as the outcome (playedLater), predicted by within-person centered in-game need satisfaction (gameNS_cw; H2a) and global need frustration (globalNF_cw; H2b). glmmTMB(playedLater ~ gameNS_cw + gameNS_cb + globalNF_cw + globalNF_cb + (1 + gameNS_cw + globalNF_cw | pid) + ar1(day + 0 | pid), family = binomial(link = \"logit\"))",
    "",
    "Multilevel linear regression predicting global need satisfaction (globalNS) from the presence or absence of the player's most recent gaming session having displaced a core life domain (displacedCoreDomain). glmmTMB(globalNS ~ displacedCoreDomain + (1 + displacedCoreDomain | pid) + ar1(day + 0 | pid))"
  ),
  `Rationale for deciding the sensitivity of the test for confirming or disconfirming the hypothesis` = c(
    "We did not conduct an a priori power analysis, as resource constraints dictated the maximum sample we could collect. The complexity of the data structure and lack of prior information about within-person playtime variance across days, effect size expectations, or meaningful smallest effect sizes of interests (SESOIs). Instead, we used simulated data to establish the approximate precision with which coefficients will eventually be estimated. In our assessment, these are sufficiently precise to be valuable and to differentiate statistical vs practical significance (see column right), but we leave further judgement to the reader.",
    "",
    "",
    ""
  ),
  `Interpretation given different outcomes` = c(
    "We will only interpret results subject to the data meeting the relevant positive controls specified: (1) a significant positive correlation between self-reported playtime and digital trace playtime, (2) no overlapping game sessions for a given individual on a particular platform, and (3) a significant positive correlation between global need satisfaction and life satisfaction. We will use statistical significance to determine whether the results support (p < .05) or fail to support (p > .05) the hypothesis. However, much greater emphasis will be placed on marginal outcomes, which we will contextualize in real-world terms so as to let readers make judgements about whether any statistically significant results are also practically significant.",
    "",
    "",
    ""
  ),
  `Theory that could be shown wrong by the outcomes` = c(
    "H6 in BANG",
    "H8 in BANG",
    "H9 in BANG",
    "H5 in BANG"
  ),
  `Observed Outcome` = c(
    "Supported; in-game need satisfaction was positively related to global need satisfaction.",
    "Unsupported; in-game need satisfaction was not related to probability of play in the subsequent 24 hours.",
    "Unsupported; global need frustration was not related to probability of play in the subsequent 24 hours.",
    "Unsupported; self-reported displacement of a core life domain was not associated with lower global need satisfaction."
  )
) |>
  tt(
    notes = "†All multilevel models in Study A include random slopes and intercepts by participant (pid) for the predictor of interest, and an AR(1) autocorrelation structure for outcome measures. Between-person centered predictors (†\\_cb) are included for debiasing the within-person coefficient of interest, but are not used as part of the primary hypothesis test."
  ) |>
  style_tt(i = 1, j = 3, rowspan = 4, alignv = "m") |>
  style_tt(i = 1, j = 5, rowspan = 4, alignv = "m") |>
  style_tt(i = 1, j = 6, rowspan = 4, alignv = "m") |>
  style_tt(i = 2, j = 4, rowspan = 2, alignv = "m") |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

## Full Model Outputs

This section provides complete model summaries for the three main hypothesis tests (H1-H3), including all fixed effects, random effects, and autocorrelation parameters.

### H1: Game need satisfaction is related to global need satisfaction

```{r}
#| label: tbl-full-h1
#| tbl-cap: "H1: Complete model summary for game NS → global NS"
#| code-summary: "Show code (Full H1 model output)"

# Use first imputation model for complete summary
modelsummary(
  list("H1: Game NS positively associated with Global NS" = h1mod),
  coef_rename = labels,
  statistic = c(
    "conf.int",
    "s.e. = {std.error}",
    "t = {statistic}",
    "p = {p.value}"
  ),
  coef_omit = "wave", # Omit individual AR(1) wave parameters
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### H2: Need satisfaction and frustration is related to subsequent play

```{r}
#| label: tbl-full-h2
#| tbl-cap: "H2: Complete model summary for game NS + global NF → play"
#| code-summary: "Show code (Full H2 model output)"

# Use first imputation model for complete summary
# modelsummary(
#   h2mod,
#   coef_rename = labels,
#   statistic = c(
#     "conf.int",
#     "s.e. = {std.error}",
#     "t = {statistic}",
#     "p = {p.value}"
#   ),
#   coef_omit = "wave", # Omit individual AR(1) wave parameters
# ) |>
#   style_tt(fontsize = 0.7) |>
#   style_tt(i = 0, bold = TRUE)

## 1) Pre-tidy with CIs
tt <- tidy(h2mod, effects = "fixed", conf.int = TRUE)

## 2) Optional: rename coefficients manually now
tt <- tt |>
  mutate(
    term = dplyr::recode(term, !!!labels)
  )

## 3) Pre-compute glance once
gl <- glance(h2mod)

## 4) Wrap as a modelsummary_list (no further introspection)
mod_obj <- structure(
  list(
    tidy = tt,
    glance = gl
  ),
  class = "modelsummary_list"
)

## 5) Now call modelsummary on this object
modelsummary(
  list("H2: NS & NF associated with likelihood of subsequent play" = mod_obj),
  statistic = c(
    "CI = [{conf.low}, {conf.high}]",
    "s.e. = {std.error}",
    "z = {statistic}",
    "p = {p.value}"
  ),
  coef_omit = "wave",
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### H3: Displacing core domains is associated with lower global need satisfaction

```{r}
#| label: tbl-full-h3
#| tbl-cap: "H3: Complete model summary for displaced core → global NS"
#| code-summary: "Show code (Full H3 model output)"

# Use first imputation model for complete summary
modelsummary(
  list(
    "H3: Displacement of core life domain associated with lower Global NF" = h3mod
  ),
  coef_rename = labels,
  statistic = c(
    "conf.int",
    "s.e. = {std.error}",
    "t = {statistic}",
    "p = {p.value}"
  ),
  coef_omit = "wave", # Omit individual AR(1) wave parameters
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### Study B: Game need satisfaction and play behavior in PowerWash Simulator

```{r}
#| label: tbl-full-study2
#| tbl-cap: "Study B: Complete model summaries for game NS → play behavior"
#| code-summary: "Show code (Full Study B model output)"

# Create model summaries for both Study B models
modelsummary(
  list(
    "Session Length" = pws_m1,
    "Time to Next Session" = pws_m2
  ),
  coef_rename = labels,
  statistic = c(
    "conf.int",
    "s.e. = {std.error}",
    "t = {statistic}",
    "p = {p.value}"
  )
) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

## Diagnostics

```{r}
#| label: fig-imputation
#| fig-cap: "Imputed vs observed distributions for need satisfaction/frustration variables"
#| fig-height: 3
#| fig-width: 12

# Compare observed vs imputed distributions (pooled across waves)
bind_rows(dat_observed, dat) |>
  pivot_longer(
    c(global_ns, global_nf, game_ns),
    names_to = "variable",
    values_to = "value"
  ) |>
  filter(!is.na(value)) |>
  mutate(
    data_type = if_else(.imp == 0, "Observed", "Imputed"),
    data_type = factor(data_type, levels = c("Observed", "Imputed")),
    variable = factor(
      variable,
      levels = c("game_ns", "global_ns", "global_nf"),
      labels = c(labels["game_ns"], labels["global_ns"], labels["global_nf"])
    )
  ) |>
  ggplot(aes(x = value, color = data_type, group = .imp)) +
  geom_density(linewidth = 0.7) +
  scale_color_manual(
    values = c("Observed" = "black", "Imputed" = "steelblue")
  ) +
  facet_wrap(~variable, scales = "free", nrow = 1) +
  labs(color = NULL, x = "Value", y = "Density") +
  theme(legend.position = "bottom")
```

## Sensitivity Analyses

We conducted several sensitivity analyses to assess the robustness of our findings regarding the relationship between need satisfaction/frustration and subsequent play behavior.

### S1: Temporal window robustness

Testing whether the temporal window affects results of H2a (game need satisfation) and H2b (global need frustration). The main analysis used 24 hours post-survey. Here we test: (a) 24 hours pre-survey (reverse temporal ordering to test bidirectionality), (b) 6 hours post-survey, (c) 12 hours post-survey, and (d) 24 hours post-survey (preregistered analysis).

```{r}
#| label: s1-12h-model
#| output: false
#| code-summary: "Show code (S1: Fit models with 12-hour play window)"

# File-based caching to avoid re-running across multiple output formats
sens1_cache_file <- "data/models/sens1_fits.rds"
sens1_pooled_file <- "data/models/sens1_pooled.rds"

if (file.exists(sens1_cache_file) && file.exists(sens1_pooled_file)) {
  message("Loading cached S1 model fits")
  sens1_fits <- readRDS(sens1_cache_file)
  sens1_pooled <- readRDS(sens1_pooled_file)
} else {
  message("Fitting S1 models...")

  sens1_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S1 model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_12h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens1_pooled <- pool(sens1_fits)

  # Save to cache
  saveRDS(sens1_fits, sens1_cache_file)
  saveRDS(sens1_pooled, sens1_pooled_file)
  message("S1 models saved to cache")
}
```

```{r}
#| label: s1b-6h-model
#| output: false
#| code-summary: "Show code (S1b: Fit models with 6-hour play window)"

# File-based caching to avoid re-running across multiple output formats
sens1b_cache_file <- "data/models/sens1b_fits.rds"
sens1b_pooled_file <- "data/models/sens1b_pooled.rds"

if (file.exists(sens1b_cache_file) && file.exists(sens1b_pooled_file)) {
  message("Loading cached S1b model fits")
  sens1b_fits <- readRDS(sens1b_cache_file)
  sens1b_pooled <- readRDS(sens1b_pooled_file)
} else {
  message("Fitting S1b models...")

  sens1b_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S1b model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_6h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens1b_pooled <- pool(sens1b_fits)

  # Save to cache
  saveRDS(sens1b_fits, sens1b_cache_file)
  saveRDS(sens1b_pooled, sens1b_pooled_file)
  message("S1b models saved to cache")
}
```

```{r}
#| label: s1c-pre-model
#| output: false
#| code-summary: "Show code (S1c: Fit models with 24-hour pre-survey play window)"

# File-based caching to avoid re-running across multiple output formats
sens1c_cache_file <- "data/models/sens1c_fits.rds"
sens1c_pooled_file <- "data/models/sens1c_pooled.rds"

if (file.exists(sens1c_cache_file) && file.exists(sens1c_pooled_file)) {
  message("Loading cached S1c model fits")
  sens1c_fits <- readRDS(sens1c_cache_file)
  sens1c_pooled <- readRDS(sens1c_pooled_file)
} else {
  message("Fitting S1c models...")

  sens1c_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S1c model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h_pre ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens1c_pooled <- pool(sens1c_fits)

  # Save to cache
  saveRDS(sens1c_fits, sens1c_cache_file)
  saveRDS(sens1c_pooled, sens1c_pooled_file)
  message("S1c models saved to cache")
}
```

```{r}
#| label: tbl-s1-temporal-windows
#| tbl-cap: "S1: H2 associations across different temporal windows. Main analysis (24h post-survey) shown for comparison. Pre-survey window tests reverse temporal ordering."
#| code-summary: "Show code (Create combined temporal windows table)"

# Combine all results
bind_rows(
  clean_results(sens1c_pooled, "24h pre"),
  clean_results(sens1b_pooled, "6h post"),
  clean_results(sens1_pooled, "12h post"),
  clean_results(h2_pooled, "24h post")
) |>
  pivot_wider(
    names_from = window,
    values_from = result,
    names_sort = FALSE
  ) |>
  rename(Parameter = term) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

Results indicate that shorter windows post-survey are still unassociated with play likelihood, but that video game play is more likely in the day preceding a report of high in-game need satisfaction or high general need frustration. 

### S2: Random effects specification robustness

Random slopes allow associations to vary across individuals, which is theoretically appropriate for these constructs. The main analysis used a random intercept only model due to convergence issues in frequentist estimation. Here we test whether this simplification affects fixed effect estimates by comparing four specifications: (a) no random slopes (main model), (b) random slope for game NS within-person only, (c) random slope for global NF within-person only, and (d) both random slopes simultaneously using Bayesian estimation (which handles complex random effects more robustly).

```{r}
#| label: s2-brms-model
#| output: false
#| code-summary: "Show code (S2: Fit Bayesian model with random slopes)"

# File-based caching to avoid re-running across multiple output formats
sens2_cache_file <- "data/models/sens2_fit.rds"

if (file.exists(sens2_cache_file)) {
  message("Loading cached S2 model fit")
  sens2_fit <- readRDS(sens2_cache_file)
} else {
  message("Fitting S2 Bayesian model...")

  # Use complete cases only
  dat_complete <- dat_observed |>
    filter(
      !is.na(global_ns),
      !is.na(global_nf),
      !is.na(game_ns),
      !is.na(game_nf),
      !is.na(telemetry_played_any_24h)
    )

  # Fit Bayesian model with random slopes
  sens2_fit <- brm(
    telemetry_played_any_24h ~
      game_ns_cw +
      game_ns_cb +
      global_nf_cw +
      global_nf_cb +
      (1 + game_ns_cw + global_nf_cw | pid),
    family = bernoulli(),
    data = dat_complete,
    chains = 4,
    cores = 4,
    iter = 5000,
    warmup = 1000,
    seed = 8675309
  )

  # Save to cache
  saveRDS(sens2_fit, sens2_cache_file)
  message("S2 model saved to cache")
}
```

```{r}
#| label: s2-oneslope-models
#| output: false
#| code-summary: "Show code (S2: Fit H2 models with one random slope at a time)"

# File-based caching to avoid re-running across multiple output formats
sens2_h2a_cache <- "data/models/sens2_h2a_fits.rds"
sens2_h2a_pooled_cache <- "data/models/sens2_h2a_pooled.rds"
sens2_h2b_cache <- "data/models/sens2_h2b_fits.rds"
sens2_h2b_pooled_cache <- "data/models/sens2_h2b_pooled.rds"

if (
  file.exists(sens2_h2a_cache) &&
    file.exists(sens2_h2a_pooled_cache) &&
    file.exists(sens2_h2b_cache) &&
    file.exists(sens2_h2b_pooled_cache)
) {
  message("Loading cached S2 one-slope model fits")
  s2_h2a_fits <- readRDS(sens2_h2a_cache)
  s2_h2a_pooled <- readRDS(sens2_h2a_pooled_cache)
  s2_h2b_fits <- readRDS(sens2_h2b_cache)
  s2_h2b_pooled <- readRDS(sens2_h2b_pooled_cache)
} else {
  message("Fitting S2 one-slope models...")

  # H2a: Random slope for game_ns_cw only
  message("Fitting S2 H2a models...")
  s2_h2a_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S2 H2a model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 + game_ns_cw | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  s2_h2a_pooled <- pool(s2_h2a_fits)

  # H2b: Random slope for global_nf_cw only
  message("Fitting S2 H2b models...")
  s2_h2b_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S2 H2b model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 + global_nf_cw | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  s2_h2b_pooled <- pool(s2_h2b_fits)

  # Save to cache
  saveRDS(s2_h2a_fits, sens2_h2a_cache)
  saveRDS(s2_h2a_pooled, sens2_h2a_pooled_cache)
  saveRDS(s2_h2b_fits, sens2_h2b_cache)
  saveRDS(s2_h2b_pooled, sens2_h2b_pooled_cache)
  message("S2 one-slope models saved to cache")
}
```

```{r}
#| label: tbl-s2-specification-comparison
#| tbl-cap: "S2: H2 fixed effect estimates across random effects specifications. Frequentist estimates (first three columns) show estimate (p-value). Bayesian estimates show estimate [95% credible interval]."
#| code-summary: "Show code (Create S2 combined specification comparison table)"

# Extract estimates from main H2 model (no random slopes)
h2_simple <- summary(h2_pooled) |>
  as_tibble() |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    result = glue(
      "{round(estimate, 3)} ({ifelse(p.value < 0.001, '<.001', round(p.value, 3))})"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "No slopes")

# Extract estimates from one-slope models
h2a_est <- summary(s2_h2a_pooled) |>
  as_tibble() |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    result = glue(
      "{round(estimate, 3)} ({ifelse(p.value < 0.001, '<.001', round(p.value, 3))})"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "RS: game NS")

h2b_est <- summary(s2_h2b_pooled) |>
  as_tibble() |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    result = glue(
      "{round(estimate, 3)} ({ifelse(p.value < 0.001, '<.001', round(p.value, 3))})"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "RS: global NF")

# Extract estimates from Bayesian model with both slopes
sens2_est <- summary(sens2_fit)$fixed |>
  as_tibble(rownames = "term") |>
  filter(
    term %in% c("game_ns_cw", "global_nf_cw")
  ) |>
  mutate(
    # Bayesian doesn't have p-values, show 95% CI instead
    result = glue(
      "{round(Estimate, 3)} [{round(`l-95% CI`, 3)}, {round(`u-95% CI`, 3)}]"
    )
  ) |>
  select(term, result) |>
  mutate(specification = "Both slopes (Bayesian)")

# Combine all specifications
bind_rows(h2_simple, h2a_est, h2b_est, sens2_est) |>
  mutate(
    term = ifelse(term %in% names(labels), labels[term], term)
  ) |>
  pivot_wider(names_from = specification, values_from = result) |>
  rename(Parameter = term) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

All results vary minimally and can be considered robust to the decision to drop random slopes from the main models.  

### S3: Play volume (continuous outcome)

Here we test whether the predictors have a linear association with play volume in minutes, rather than binary play occurrence.

```{r}
#| label: s3-playvolume-model
#| output: false
#| code-summary: "Show code (S3: Fit models predicting continuous play volume)"

# File-based caching to avoid re-running across multiple output formats
sens3_cache_file <- "data/models/sens3_fits.rds"
sens3_pooled_file <- "data/models/sens3_pooled.rds"

if (file.exists(sens3_cache_file) && file.exists(sens3_pooled_file)) {
  message("Loading cached S3 model fits")
  sens3_fits <- readRDS(sens3_cache_file)
  sens3_pooled <- readRDS(sens3_pooled_file)
} else {
  message("Fitting S3 models...")

  # Fit model to each imputed dataset
  sens3_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S3 model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      play_minutes_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = gaussian()
    )
  })

  sens3_pooled <- pool(sens3_fits)

  # Save to cache
  saveRDS(sens3_fits, sens3_cache_file)
  saveRDS(sens3_pooled, sens3_pooled_file)
  message("S3 models saved to cache")
}
```

```{r}
#| label: tbl-s3-results
#| tbl-cap: "S3: H2 with continuous play volume (minutes) as the outcome, rather than binary play"
#| code-summary: "Show code (Create S3 results table)"

summary(sens3_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    term = ifelse(term %in% names(labels), labels[term], term),
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  rename(
    Parameter = term,
    Estimate = estimate,
    SE = std.error,
    t = statistic,
    p = p.value
  ) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```



```{r}
#| label: threshold-imputations
#| output: false
#| code-summary: "Show code (S4: Run imputations across completion thresholds)"

#| code-summary: "Show code (Run imputations for threshold sensitivity, S6)"

# Imputation function for threshold sensitivity analysis (S6)
# Replicates primary imputation pipeline for a given min-waves cutoff
# M=10 is sufficient for a robustness check; results cached per threshold
run_threshold <- function(min_waves, m = 10) {
  cache_file <- glue("data/models/threshold_{min_waves}_imp.csv.gz")

  if (file.exists(cache_file)) {
    message(glue("Loading threshold={min_waves} imputation from cache"))
    return(read_csv(cache_file, show_col_types = FALSE) |> as.mids())
  }

  message(glue(
    "Running imputation for threshold={min_waves} (M={m}), started {Sys.time()}"
  ))

  sw <- surveys |>
    filter(diaries_completed >= min_waves) |>
    select(
      pid,
      wave,
      age,
      gender,
      edu_level,
      employment,
      marital_status,
      wemwbs,
      diaries_completed,
      self_reported_weekly_play,
      self_reported_played_24h,
      displaced_core_domain,
      bpnsfs_1,
      bpnsfs_2,
      bpnsfs_3,
      bpnsfs_4,
      bpnsfs_5,
      bpnsfs_6,
      bangs_1,
      bangs_2,
      bangs_3,
      bangs_4,
      bangs_5,
      bangs_6
    ) |>
    pivot_wider(
      id_cols = c(
        pid,
        age,
        gender,
        edu_level,
        employment,
        marital_status,
        wemwbs,
        diaries_completed,
        self_reported_weekly_play
      ),
      names_from = wave,
      values_from = c(
        self_reported_played_24h,
        displaced_core_domain,
        bpnsfs_1,
        bpnsfs_2,
        bpnsfs_3,
        bpnsfs_4,
        bpnsfs_5,
        bpnsfs_6,
        bangs_1,
        bangs_2,
        bangs_3,
        bangs_4,
        bangs_5,
        bangs_6
      ),
      names_sep = "_w"
    )

  played_vars_t <- grep("^self_reported_played_24h_w", names(sw), value = TRUE)
  bpnsfs_vars_t <- grep("^bpnsfs_[1-6]_w", names(sw), value = TRUE)
  bangs_vars_t <- grep("^bangs_[1-6]_w", names(sw), value = TRUE)
  displaced_vars_t <- grep("^displaced_core_domain_w", names(sw), value = TRUE)

  methods_t <- setNames(rep("", ncol(sw)), names(sw))
  methods_t[played_vars_t] <- "logreg"
  methods_t[c(bpnsfs_vars_t, bangs_vars_t, displaced_vars_t)] <- "pmm"
  methods_t[c(
    "pid",
    "age",
    "gender",
    "edu_level",
    "employment",
    "marital_status",
    "wemwbs",
    "diaries_completed",
    "self_reported_weekly_play"
  )] <- ""

  where_t <- is.na(sw)
  for (bv in bangs_vars_t) {
    wave_num <- str_extract(bv, "\\d+$")
    pv <- paste0("self_reported_played_24h_w", wave_num)
    if (pv %in% names(sw)) {
      where_t[sw[[pv]] == "No" & is.na(sw[[bv]]), bv] <- FALSE
    }
  }

  pred_t <- quickpred(
    sw,
    mincor = 0.3,
    minpuc = 0.3,
    include = c("age", "wemwbs", "self_reported_weekly_play"),
    exclude = c(
      "pid",
      "gender",
      "edu_level",
      "employment",
      "marital_status",
      "diaries_completed"
    )
  )

  imp_t <- futuremice(
    data = sw,
    m = m,
    method = methods_t,
    predictorMatrix = pred_t,
    where = where_t,
    maxit = 5,
    n.core = parallel::detectCores() - 1,
    parallelseed = 8675309
  )

  message(glue("Completed threshold={min_waves} imputation {Sys.time()}"))
  imp_long_t <- complete(imp_t, action = "long", include = TRUE)
  dir.create("data/models", showWarnings = FALSE, recursive = TRUE)
  write_csv(imp_long_t, cache_file)
  as.mids(imp_long_t)
}

threshold_values <- c(10, 12, 15, 18, 20, 24)
threshold_imps <- map(threshold_values, run_threshold)
names(threshold_imps) <- threshold_values
```

```{r}
```

### S4: Sample construction and imputation robustness

The primary H2 analysis rests on a few choices about how the analytic sample was built: a non-preregistered ≥15 completed-surveys inclusion threshold, and multiple imputation (M=27) restricted to that analytical sample rather than all eligible participants (the preregistered approach). Here we test whether the H2a/H2b estimates depend on these choices by refitting the model under complete cases only (no imputation), the ≥15-wave threshold swept across a range of plausible cutoffs (10-24 completed surveys), and imputation of the full eligible sample rather than just the analytical sample.

```{r}
#| label: s4-complete-model
#| output: false
#| code-summary: "Show code (S4: Fit model on complete cases only)"

# File-based caching to avoid re-running across multiple output formats
sens4_cache_file <- "data/models/sens4_pooled.rds"

if (file.exists(sens4_cache_file)) {
  message("Loading cached S4 pooled model")
  sens4_pooled <- readRDS(sens4_cache_file)
} else {
  message("Fitting S4 model...")

  # Use .imp == 0 (original data with missingness)
  # Filter to complete cases on key variables
  dat_complete <- dat_observed |>
    filter(
      !is.na(global_ns),
      !is.na(global_nf),
      !is.na(game_ns),
      !is.na(game_nf),
      !is.na(telemetry_played_any_24h)
    )

  sens4_fit <- glmmTMB(
    telemetry_played_any_24h ~
      game_ns_cw +
      game_ns_cb +
      global_nf_cw +
      global_nf_cb +
      (1 | pid) +
      ar1(wave + 0 | pid),
    data = dat_complete,
    family = binomial(link = "logit"),
    ziformula = ~0
  )

  # Complete cases has no missing data to impute, so pooling M identical
  # fits via mice::pool() reproduces the same estimate/SE as the single fit
  # (only the Rubin's-rules df differs slightly). Done so this specification
  # yields the same pooled-summary structure as every other row below.
  sens4_pooled <- pool(rep(list(sens4_fit), 10))

  # Save to cache
  saveRDS(sens4_pooled, sens4_cache_file)
  message("S4 model saved to cache")
}
```

```{r}
#| label: s4-full-imputation
#| output: false
#| code-summary: "Show code (S4: Run imputation on full sample)"
#| eval: !expr '!file.exists("data/models/sens5_pooled.rds")'

M_FULL_SAMPLE <- 27

message("=== FULL SAMPLE IMPUTATION (PREREGISTERED) ===")
message(glue(
  "Imputing all {length(full_eligible_pids)} participants with M={M_FULL_SAMPLE}"
))

# Separate telemetry (no missing data) - use full sample
telemetry_vars_full <- surveys |>
  select(
    pid,
    wave,
    date,
    telemetry_played_any_24h,
    play_minutes_24h,
    telemetry_played_any_12h,
    play_minutes_12h,
    telemetry_played_any_6h,
    play_minutes_6h,
    telemetry_played_any_24h_pre,
    play_minutes_24h_pre
  )

# Convert to wide format for imputation - NO FILTER
surveys_wide_full <- surveys |>
  select(
    pid,
    wave,
    age,
    gender,
    edu_level,
    employment,
    marital_status,
    wemwbs,
    diaries_completed,
    self_reported_weekly_play,
    self_reported_played_24h,
    displaced_core_domain,
    bpnsfs_1,
    bpnsfs_2,
    bpnsfs_3,
    bpnsfs_4,
    bpnsfs_5,
    bpnsfs_6,
    bangs_1,
    bangs_2,
    bangs_3,
    bangs_4,
    bangs_5,
    bangs_6
  ) |>
  pivot_wider(
    id_cols = c(
      pid,
      age,
      gender,
      edu_level,
      employment,
      marital_status,
      wemwbs,
      diaries_completed,
      self_reported_weekly_play
    ),
    names_from = wave,
    values_from = c(
      self_reported_played_24h,
      displaced_core_domain,
      bpnsfs_1,
      bpnsfs_2,
      bpnsfs_3,
      bpnsfs_4,
      bpnsfs_5,
      bpnsfs_6,
      bangs_1,
      bangs_2,
      bangs_3,
      bangs_4,
      bangs_5,
      bangs_6
    ),
    names_sep = "_w"
  )

# Set up imputation methods (same as analytical sample)
played_vars_full <- names(surveys_wide_full)[grepl(
  "^self_reported_played_24h_w",
  names(surveys_wide_full)
)]
bpnsfs_vars_full <- names(surveys_wide_full)[grepl(
  "^bpnsfs_[1-6]_w",
  names(surveys_wide_full)
)]
bangs_vars_full <- names(surveys_wide_full)[grepl(
  "^bangs_[1-6]_w",
  names(surveys_wide_full)
)]
displaced_vars_full <- names(surveys_wide_full)[grepl(
  "^displaced_core_domain_w",
  names(surveys_wide_full)
)]

methods_full <- setNames(
  rep("", ncol(surveys_wide_full)),
  names(surveys_wide_full)
)
methods_full[played_vars_full] <- "logreg"
methods_full[c(bpnsfs_vars_full, bangs_vars_full, displaced_vars_full)] <- "pmm"

person_level_vars <- c(
  "pid",
  "age",
  "gender",
  "edu_level",
  "employment",
  "marital_status",
  "wemwbs",
  "diaries_completed",
  "self_reported_weekly_play"
)
methods_full[person_level_vars] <- ""

# Create WHERE matrix (same conditional imputation logic)
where_matrix_full <- is.na(surveys_wide_full)

for (bangs_var in bangs_vars_full) {
  wave_num <- str_extract(bangs_var, "\\d+$")
  played_var <- paste0("self_reported_played_24h_w", wave_num)

  if (played_var %in% names(surveys_wide_full)) {
    no_play <- surveys_wide_full[[played_var]] == "No" &
      is.na(surveys_wide_full[[bangs_var]])
    where_matrix_full[no_play, bangs_var] <- FALSE
  }
}

# Sparse predictor matrix (same settings as analytical)
pred_full <- quickpred(
  surveys_wide_full,
  mincor = 0.3,
  minpuc = 0.3,
  include = c("age", "wemwbs", "self_reported_weekly_play"),
  exclude = c(
    "pid",
    "gender",
    "edu_level",
    "employment",
    "marital_status",
    "diaries_completed"
  )
)

# Check if imputation already exists
imp_file_full <- "data/imputation_full.csv.gz"

if (file.exists(imp_file_full)) {
  message(glue("Loading existing full sample imputation from {imp_file_full}"))
  imp_long_full <- read_csv(imp_file_full, show_col_types = FALSE)
  imp_full <- as.mids(imp_long_full)
  message(glue("Loaded imputation object (M={imp_full$m})"))
} else {
  message(glue("No existing imputation found - running MICE on full sample"))

  message(glue(
    "Running MICE: M={M_FULL_SAMPLE}, N={nrow(surveys_wide_full)}, started {Sys.time()}"
  ))

  imp_full <- futuremice(
    data = surveys_wide_full,
    m = M_FULL_SAMPLE,
    method = methods_full,
    predictorMatrix = pred_full,
    where = where_matrix_full,
    maxit = 5,
    n.core = parallel::detectCores() - 1,
    parallelseed = 8675309
  )

  message(glue("Completed {Sys.time()}"))

  # Save imputation results
  imp_long_full <- complete(imp_full, action = "long", include = TRUE)
  write_csv(imp_long_full, imp_file_full)
  message(glue("Saved full sample imputation to {imp_file_full}"))

  if (nrow(imp_full$loggedEvents) > 0) {
    message(glue(
      "Warning: {nrow(imp_full$loggedEvents)} logged events during full sample imputation"
    ))
  }
}

# Post-imputation processing for full sample
daily_imputed_full <- complete(imp_full, action = "long", include = TRUE) |>
  pivot_longer(
    cols = -c(
      .imp,
      .id,
      pid,
      age,
      gender,
      edu_level,
      employment,
      marital_status,
      wemwbs,
      diaries_completed,
      self_reported_weekly_play
    ),
    names_to = c(".value", "wave"),
    names_pattern = "(.+)_w(.+)"
  ) |>
  mutate(wave = as.factor(wave)) |>
  mutate(
    global_ns = rowMeans(pick(bpnsfs_1, bpnsfs_3, bpnsfs_5), na.rm = TRUE),
    global_nf = rowMeans(pick(bpnsfs_2, bpnsfs_4, bpnsfs_6), na.rm = TRUE),
    game_ns = rowMeans(pick(bangs_1, bangs_3, bangs_5), na.rm = TRUE),
    game_nf = rowMeans(pick(bangs_2, bangs_4, bangs_6), na.rm = TRUE)
  ) |>
  left_join(telemetry_vars_full, by = c("pid", "wave")) |>
  group_by(.imp, pid) |>
  mutate(
    global_ns_pm = mean(global_ns, na.rm = TRUE),
    global_nf_pm = mean(global_nf, na.rm = TRUE),
    game_ns_pm = mean(game_ns, na.rm = TRUE),
    game_nf_pm = mean(game_nf, na.rm = TRUE)
  ) |>
  ungroup() |>
  group_by(.imp) |>
  mutate(
    global_ns_gm = mean(global_ns_pm, na.rm = TRUE),
    global_nf_gm = mean(global_nf_pm, na.rm = TRUE),
    game_ns_gm = mean(game_ns_pm, na.rm = TRUE),
    game_nf_gm = mean(game_nf_pm, na.rm = TRUE),
    global_ns_cw = global_ns - global_ns_pm,
    global_nf_cw = global_nf - global_nf_pm,
    game_ns_cw = game_ns - game_ns_pm,
    game_nf_cw = game_nf - game_nf_pm,
    global_ns_cb = global_ns_pm - global_ns_gm,
    global_nf_cb = global_nf_pm - global_nf_gm,
    game_ns_cb = game_ns_pm - game_ns_gm,
    game_nf_cb = game_nf_pm - game_nf_gm
  ) |>
  ungroup()

message(glue(
  "Full sample imputation complete: {length(unique(daily_imputed_full$pid))} participants"
))
```

```{r}
#| label: s4-full-h2-models
#| output: false
#| code-summary: "Show code (S4: Fit H2 models to full sample)"

sens5_cache_file <- "data/models/sens5_fits.rds"
sens5_pooled_file <- "data/models/sens5_pooled.rds"

if (file.exists(sens5_cache_file) && file.exists(sens5_pooled_file)) {
  message("Loading cached S5 model fits")
  sens5_fits <- readRDS(sens5_cache_file)
  sens5_pooled <- readRDS(sens5_pooled_file)
} else {
  message("Fitting S5 models to full sample...")

  # Prepare data for modeling
  dat_full <- daily_imputed_full |>
    filter(.imp > 0) |>
    mutate(
      pid = factor(pid),
      wave = factor(wave)
    )

  # Fit H2 model to each imputed dataset
  sens5_fits <- lapply(1:M_FULL_SAMPLE, function(i) {
    message(glue("Fitting S5 model to imputation {i} of {M_FULL_SAMPLE}"))
    dat_i <- dat_full |>
      filter(.imp == i) |>
      droplevels()
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  # Pool estimates
  sens5_pooled <- pool(sens5_fits)

  # Save to cache
  saveRDS(sens5_fits, sens5_cache_file)
  saveRDS(sens5_pooled, sens5_pooled_file)
  message("S4 (full sample) models saved to cache")
}
```

Here we also repeat the H2 imputation-based analysis across a range of plausible survey-completion thresholds, to assess whether conclusions depend on the specific ≥15-wave cutoff used in the primary analysis.

```{r}
#| label: s4-threshold-models
#| output: false
#| code-summary: "Show code (S4: Fit H2 models across completion thresholds)"

# Post-process each threshold's imputation: composites, centering, telemetry join
process_threshold <- function(imp_t, min_waves) {
  telemetry_t <- surveys |>
    filter(diaries_completed >= min_waves) |>
    select(
      pid,
      wave,
      telemetry_played_any_24h,
      play_minutes_24h,
      telemetry_played_any_12h,
      play_minutes_12h,
      telemetry_played_any_6h,
      play_minutes_6h,
      telemetry_played_any_24h_pre,
      play_minutes_24h_pre
    )

  complete(imp_t, action = "long", include = TRUE) |>
    pivot_longer(
      cols = -c(
        .imp,
        .id,
        pid,
        age,
        gender,
        edu_level,
        employment,
        marital_status,
        wemwbs,
        diaries_completed,
        self_reported_weekly_play
      ),
      names_to = c(".value", "wave"),
      names_pattern = "(.+)_w(.+)"
    ) |>
    mutate(wave = as.factor(wave)) |>
    mutate(
      global_ns = rowMeans(pick(bpnsfs_1, bpnsfs_3, bpnsfs_5), na.rm = TRUE),
      global_nf = rowMeans(pick(bpnsfs_2, bpnsfs_4, bpnsfs_6), na.rm = TRUE),
      game_ns = rowMeans(pick(bangs_1, bangs_3, bangs_5), na.rm = TRUE),
      game_nf = rowMeans(pick(bangs_2, bangs_4, bangs_6), na.rm = TRUE)
    ) |>
    left_join(telemetry_t, by = c("pid", "wave")) |>
    group_by(.imp, pid) |>
    mutate(
      global_ns_pm = mean(global_ns, na.rm = TRUE),
      global_nf_pm = mean(global_nf, na.rm = TRUE),
      game_ns_pm = mean(game_ns, na.rm = TRUE)
    ) |>
    ungroup() |>
    group_by(.imp) |>
    mutate(
      global_ns_gm = mean(global_ns_pm, na.rm = TRUE),
      global_nf_gm = mean(global_nf_pm, na.rm = TRUE),
      game_ns_gm = mean(game_ns_pm, na.rm = TRUE),
      global_ns_cw = global_ns - global_ns_pm,
      global_nf_cw = global_nf - global_nf_pm,
      game_ns_cw = game_ns - game_ns_pm,
      global_ns_cb = global_ns_pm - global_ns_gm,
      global_nf_cb = global_nf_pm - global_nf_gm,
      game_ns_cb = game_ns_pm - game_ns_gm
    ) |>
    ungroup() |>
    filter(.imp > 0)
}

# Fit the primary H2 model on each threshold's data and pool
fit_h2_threshold <- function(dat_t, min_waves) {
  cache_file <- glue("data/models/threshold_{min_waves}_h2_pooled.rds")

  if (file.exists(cache_file)) {
    message(glue("Loading threshold={min_waves} H2 pooled from cache"))
    return(readRDS(cache_file))
  }

  m <- max(as.integer(dat_t$.imp))
  fits <- lapply(1:m, function(i) {
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = filter(dat_t, .imp == i),
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  pooled <- pool(fits)
  saveRDS(pooled, cache_file)
  pooled
}

threshold_results <- map2(
  threshold_imps,
  threshold_values,
  function(imp_t, min_waves) {
    dat_t <- process_threshold(imp_t, min_waves)
    pooled_t <- fit_h2_threshold(dat_t, min_waves)

    summary(pooled_t) |>
      as_tibble() |>
      filter(term %in% c("game_ns_cw", "global_nf_cw")) |>
      mutate(
        min_waves = min_waves,
        lo = estimate - 1.96 * std.error,
        hi = estimate + 1.96 * std.error,
        coefficient = case_when(
          term == "game_ns_cw" ~ "H2a: Game need satisfaction",
          term == "global_nf_cw" ~ "H2b: Global need frustration"
        )
      )
  }
) |>
  list_rbind()
```

```{r}
#| label: s4-combined-results
#| code-summary: "Show code (S4: Combine sample-robustness results into one set of estimates)"

# Pull the two focal H2 coefficients from a pooled model, in a common format
extract_h2_terms <- function(pooled) {
  summary(pooled) |>
    as_tibble() |>
    filter(term %in% c("game_ns_cw", "global_nf_cw")) |>
    mutate(
      coefficient = case_when(
        term == "game_ns_cw" ~ "H2a: Game need satisfaction",
        term == "global_nf_cw" ~ "H2b: Global need frustration"
      ),
      lo = estimate - 1.96 * std.error,
      hi = estimate + 1.96 * std.error
    ) |>
    select(
      term,
      coefficient,
      estimate,
      std.error,
      statistic,
      df,
      p.value,
      lo,
      hi
    )
}

spec_levels <- c(
  "Complete cases",
  "10",
  "12",
  "15 (Primary)",
  "18",
  "20",
  "24",
  "Full sample (preregistered)"
)

sample_results <- bind_rows(
  extract_h2_terms(sens4_pooled) |> mutate(spec = "Complete cases"),
  threshold_results |>
    filter(min_waves != 15) |>
    mutate(spec = as.character(min_waves)) |>
    select(
      term,
      coefficient,
      estimate,
      std.error,
      statistic,
      df,
      p.value,
      lo,
      hi,
      spec
    ),
  # The primary (≥15 waves) specification reuses the main H2 result (M=27)
  # rather than the M=10 threshold-sweep refit, so it matches what is
  # reported as the primary result everywhere else in the paper.
  extract_h2_terms(h2_pooled) |> mutate(spec = "15 (Primary)"),
  extract_h2_terms(sens5_pooled) |> mutate(spec = "Full sample (preregistered)")
) |>
  mutate(
    spec = factor(spec, levels = spec_levels),
    is_primary = spec == "15 (Primary)"
  )
```

```{r}
#| label: tbl-s4-results
#| tbl-cap: "S4: H2 estimates across sample-construction and imputation specifications."
#| code-summary: "Show code (S4: Build combined sample-robustness table)"

sample_results |>
  arrange(coefficient, spec) |>
  transmute(
    coefficient,
    Specification = as.character(spec),
    Estimate = number(estimate, 0.001),
    SE = number(std.error, 0.001),
    Statistic = number(statistic, 0.001),
    df = number(df, 0.1),
    p = ifelse(p.value < 0.001, "<.001", number(p.value, 0.001))
  ) |>
  select(-coefficient) |>
  tt(
    notes = "Statistic and df follow Rubin's rules (Barnard-Rubin approximation).",
    width = .7
  ) |>
  group_tt(
    i = list(
      "H2a: Game need satisfaction" = 1,
      "H2b: Global need frustration" = 9
    )
  ) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = c(0, 1, 10), bold = TRUE)
```

```{r}
#| label: fig-s4-sample-robustness
#| fig-cap: "S4: H2 estimates across sample-construction and imputation specifications. Points show pooled log-odds estimates; bars show 95% confidence intervals. The primary specification (threshold = 15 waves) is highlighted."
#| code-summary: "Show code (S4: Plot sample-robustness estimates)"

sample_results |>
  ggplot(aes(
    x = spec,
    y = estimate,
    ymin = lo,
    ymax = hi,
    colour = is_primary,
    shape = is_primary
  )) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange() +
  scale_colour_manual(
    values = c("FALSE" = "grey40", "TRUE" = "#E05C2A"),
    guide = "none"
  ) +
  scale_shape_manual(values = c("FALSE" = 16, "TRUE" = 18), guide = "none") +
  facet_wrap(~coefficient, ncol = 1, scales = "free_y") +
  labs(
    x = NULL,
    y = "Estimate (log-odds)"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 30, hjust = 1)
  )
```

### S5: Interaction between game NS and global NF

Testing whether the association of global need frustration with play depends on recent game need satisfaction (i.e., do satisfied players respond differently to global need frustration?).

```{r}
#| label: s5-interaction-model
#| output: false
#| code-summary: "Show code (S5: Fit models with game NS × global NF interaction)"

# File-based caching to avoid re-running across multiple output formats
sens5b_cache_file <- "data/models/sens5b_fits.rds"
sens5b_pooled_file <- "data/models/sens5b_pooled.rds"

if (file.exists(sens5b_cache_file) && file.exists(sens5b_pooled_file)) {
  message("Loading cached S5 model fits")
  sens5b_fits <- readRDS(sens5b_cache_file)
  sens5b_pooled <- readRDS(sens5b_pooled_file)
} else {
  message("Fitting S5 models...")

  sens5b_fits <- lapply(1:m_imputations, function(i) {
    message(glue("Fitting S5 model to imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)
    glmmTMB(
      telemetry_played_any_24h ~
        game_ns_cw +
        game_ns_cb +
        global_nf_cw +
        global_nf_cb +
        game_ns_cw:global_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat_i,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  })

  sens5b_pooled <- pool(sens5b_fits)

  # Save to cache
  saveRDS(sens5b_fits, sens5b_cache_file)
  saveRDS(sens5b_pooled, sens5b_pooled_file)
  message("S5 models saved to cache")
}
```

```{r}
#| label: tbl-s5-results
#| tbl-cap: "S5: H2 with game NS \u00d7 global NF interaction"
#| code-summary: "Show code (Create S5 results table)"

summary(sens5b_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    term = ifelse(term %in% names(labels), labels[term], term),
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  rename(
    Parameter = term,
    Estimate = estimate,
    SE = std.error,
    z = statistic,
    p = p.value
  ) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### S6: Non-linearity test with splines

Testing whether the relationships between predictors and play behavior are non-linear by fitting natural splines to the H2 predictors. We use complete cases only (no imputation) for computational simplicity.

```{r}
#| label: s6-spline-model
#| output: false
#| code-summary: "Show code (S6: Fit H2 model with natural splines)"

# Use complete cases only (no imputation)
# Create this outside caching so it's available for plotting
dat_complete <- dat |>
  filter(.imp == 1) |>
  select(
    pid,
    wave,
    date,
    telemetry_played_any_24h,
    game_ns_cw,
    game_ns_cb,
    global_nf_cw,
    global_nf_cb
  ) |>
  filter(complete.cases(pick(everything())))

# File-based caching
sens8_linear_file <- "data/models/sens8_linear.rds"
sens8_spline_file <- "data/models/sens8_spline.rds"

if (file.exists(sens8_linear_file) && file.exists(sens8_spline_file)) {
  message("Loading cached S6 models")
  sens8_linear <- readRDS(sens8_linear_file)
  sens8_spline <- readRDS(sens8_spline_file)
} else {
  message("Fitting S6 models (linear vs spline)...")

  # Linear model (for comparison)
  sens8_linear <- glmmTMB(
    telemetry_played_any_24h ~
      game_ns_cw +
      game_ns_cb +
      global_nf_cw +
      global_nf_cb +
      (1 | pid) +
      ar1(factor(wave) + 0 | pid),
    data = dat_complete,
    family = binomial(link = "logit")
  )

  # Spline model with natural splines (3 df) on within-person predictors
  sens8_spline <- glmmTMB(
    telemetry_played_any_24h ~
      ns(game_ns_cw, df = 3) +
      game_ns_cb +
      ns(global_nf_cw, df = 3) +
      global_nf_cb +
      (1 | pid) +
      ar1(factor(wave) + 0 | pid),
    data = dat_complete,
    family = binomial(link = "logit")
  )

  # Cache results
  dir.create("data/models", showWarnings = FALSE, recursive = TRUE)
  saveRDS(sens8_linear, sens8_linear_file)
  saveRDS(sens8_spline, sens8_spline_file)
}
```

```{r}
#| label: tbl-s6-results
#| tbl-cap: "S6: Model comparison between linear and spline specifications"
#| code-summary: "Show code (Create S6 comparison table)"

# Compare model fit
comparison <- tibble(
  Model = c("Linear", "Spline (3 df)"),
  AIC = c(AIC(sens8_linear), AIC(sens8_spline)),
  BIC = c(BIC(sens8_linear), BIC(sens8_spline)),
  LogLik = c(logLik(sens8_linear), logLik(sens8_spline)),
  N = c(nobs(sens8_linear), nobs(sens8_spline))
) |>
  mutate(
    `ΔAic` = AIC - min(AIC),
    across(c(AIC, BIC, LogLik), ~ round(.x, 1))
  )

comparison |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

```{r}
#| label: fig-s6-spline-predictions
#| fig-cap: "S6: Comparison of linear vs spline predictions for H2 predictors. Points show observed data (aggregated), solid lines show linear model predictions, dashed lines show spline model predictions with 95% confidence ribbons."
#| code-summary: "Show code (Plot S6 spline vs linear predictions)"
#| fig-height: 6

# Generate predictions across the range of predictors
pred_data <- expand_grid(
  game_ns_cw = seq(
    min(dat_complete$game_ns_cw, na.rm = TRUE),
    max(dat_complete$game_ns_cw, na.rm = TRUE),
    length.out = 100
  ),
  global_nf_cw = seq(
    min(dat_complete$global_nf_cw, na.rm = TRUE),
    max(dat_complete$global_nf_cw, na.rm = TRUE),
    length.out = 100
  )
)

# Predictions for game NS (holding global NF at mean)
pred_game_linear <- marginaleffects::predictions(
  sens8_linear,
  newdata = datagrid(
    game_ns_cw = unique(pred_data$game_ns_cw),
    global_nf_cw = 0,
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Linear")

pred_game_spline <- marginaleffects::predictions(
  sens8_spline,
  newdata = datagrid(
    game_ns_cw = unique(pred_data$game_ns_cw),
    global_nf_cw = 0,
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Spline")

panel_a <- bind_rows(pred_game_linear, pred_game_spline) |>
  ggplot(aes(x = game_ns_cw, y = estimate, color = model, fill = model)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  geom_line(aes(linetype = model), linewidth = 1) +
  scale_color_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_fill_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_linetype_manual(values = c("Linear" = "solid", "Spline" = "dashed")) +
  labs(
    x = labels["game_ns (within-person)"],
    y = "P(Play in next 24h)",
    color = NULL,
    fill = NULL,
    linetype = NULL
  ) +
  theme(legend.position = "top")

# Predictions for global NF (holding game NS at mean)
pred_nf_linear <- marginaleffects::predictions(
  sens8_linear,
  newdata = datagrid(
    game_ns_cw = 0,
    global_nf_cw = unique(pred_data$global_nf_cw),
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Linear")

pred_nf_spline <- marginaleffects::predictions(
  sens8_spline,
  newdata = datagrid(
    game_ns_cw = 0,
    global_nf_cw = unique(pred_data$global_nf_cw),
    game_ns_cb = 0,
    global_nf_cb = 0
  ),
  re.form = NA,
  type = "response"
) |>
  as_tibble() |>
  mutate(model = "Spline")

panel_b <- bind_rows(pred_nf_linear, pred_nf_spline) |>
  ggplot(aes(x = global_nf_cw, y = estimate, color = model, fill = model)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  geom_line(aes(linetype = model), linewidth = 1) +
  scale_color_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_fill_manual(values = c("Linear" = "#4477AA", "Spline" = "#EE6677")) +
  scale_linetype_manual(values = c("Linear" = "solid", "Spline" = "dashed")) +
  labs(
    x = labels["global_nf (within-person)"],
    y = "P(Play in next 24h)",
    color = NULL,
    fill = NULL,
    linetype = NULL
  ) +
  theme(legend.position = "top")

panel_a +
  panel_b +
  plot_annotation(tag_levels = "A") +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "top",
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA)
  )
```

The spline model `r if(exists("comparison") && comparison$ΔAic[2] < -2) "shows substantially better fit (ΔAIC < -2)" else if(exists("comparison") && comparison$ΔAic[2] > 2) "does not outperform the linear model (ΔAIC > 2)" else "shows similar fit to the linear model"`, suggesting that the relationships between need satisfaction/frustration and play behavior `r if(exists("comparison") && comparison$ΔAic[2] < -2) "exhibit non-linear patterns" else "are adequately captured by linear terms"`.

### S7: Separate needs components

Testing whether associations with play differ across the three basic psychological needs (autonomy, competence, relatedness) rather than using composite need satisfaction scores. We test H2 separately for each need component.

```{r}
#| label: s7-components-prep
#| code-summary: "Show code (Prepare data with separate needs components)"
#| output: false

# File-based caching to avoid re-running across multiple output formats
sens9_cache_file <- "data/models/sens9_models.rds"

if (file.exists(sens9_cache_file)) {
  message("Loading cached S7 model fits")
  sens9_cached <- readRDS(sens9_cache_file)
  sens9_h2_aut <- sens9_cached$h2_aut
  sens9_h2_com <- sens9_cached$h2_com
  sens9_h2_rel <- sens9_cached$h2_rel
} else {
  message("Fitting S7 models...")

  # Prepare component-level data for each imputation
  sens9_data <- lapply(1:m_imputations, function(i) {
    message(glue("Preparing S7 data for imputation {i} of {m_imputations}"))
    dat_i <- dat |> filter(.imp == i)

    # Calculate person means for each component (game and global)
    dat_i <- dat_i |>
      group_by(pid) |>
      mutate(
        # Game needs
        game_aut_pm = mean(bangs_1, na.rm = TRUE),
        game_com_pm = mean(bangs_3, na.rm = TRUE),
        game_rel_pm = mean(bangs_5, na.rm = TRUE),
        # Global need frustration
        global_aut_nf_pm = mean(bpnsfs_2, na.rm = TRUE),
        global_com_nf_pm = mean(bpnsfs_4, na.rm = TRUE),
        global_rel_nf_pm = mean(bpnsfs_6, na.rm = TRUE)
      ) |>
      ungroup() |>
      # Calculate grand means
      mutate(
        # Game needs
        game_aut_gm = mean(game_aut_pm, na.rm = TRUE),
        game_com_gm = mean(game_com_pm, na.rm = TRUE),
        game_rel_gm = mean(game_rel_pm, na.rm = TRUE),
        # Global need frustration
        global_aut_nf_gm = mean(global_aut_nf_pm, na.rm = TRUE),
        global_com_nf_gm = mean(global_com_nf_pm, na.rm = TRUE),
        global_rel_nf_gm = mean(global_rel_nf_pm, na.rm = TRUE)
      ) |>
      # Within/between centering
      mutate(
        # Game needs
        game_aut_cw = bangs_1 - game_aut_pm,
        game_aut_cb = game_aut_pm - game_aut_gm,
        game_com_cw = bangs_3 - game_com_pm,
        game_com_cb = game_com_pm - game_com_gm,
        game_rel_cw = bangs_5 - game_rel_pm,
        game_rel_cb = game_rel_pm - game_rel_gm,
        # Global need frustration
        global_aut_nf_cw = bpnsfs_2 - global_aut_nf_pm,
        global_aut_nf_cb = global_aut_nf_pm - global_aut_nf_gm,
        global_com_nf_cw = bpnsfs_4 - global_com_nf_pm,
        global_com_nf_cb = global_com_nf_pm - global_com_nf_gm,
        global_rel_nf_cw = bpnsfs_6 - global_rel_nf_pm,
        global_rel_nf_cb = global_rel_nf_pm - global_rel_nf_gm
      )

    return(dat_i)
  })

  # H2 models: game component + matching global NF component → play
  message("Fitting S7 H2 autonomy models...")
  sens9_h2_aut <- pool(lapply(sens9_data, function(dat) {
    glmmTMB(
      telemetry_played_any_24h ~ game_aut_cw +
        global_aut_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  }))

  message("Fitting S7 H2 competence models...")
  sens9_h2_com <- pool(lapply(sens9_data, function(dat) {
    glmmTMB(
      telemetry_played_any_24h ~ game_com_cw +
        global_com_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  }))

  message("Fitting S7 H2 relatedness models...")
  sens9_h2_rel <- pool(lapply(sens9_data, function(dat) {
    glmmTMB(
      telemetry_played_any_24h ~ game_rel_cw +
        global_rel_nf_cw +
        (1 | pid) +
        ar1(wave + 0 | pid),
      data = dat,
      family = binomial(link = "logit"),
      ziformula = ~0
    )
  }))

  # Save to cache
  saveRDS(
    list(
      h2_aut = sens9_h2_aut,
      h2_com = sens9_h2_com,
      h2_rel = sens9_h2_rel
    ),
    sens9_cache_file
  )
  message("S7 models saved to cache")
}
```

```{r}
#| label: tbl-s7-h2-results
#| tbl-cap: "S7: Associations between need components and probability of subsequent play"
#| code-summary: "Show code (Create S7 results table)"

# H2a rows first (game NS components), then H2b rows (global NF components)
bind_rows(
  summary(sens9_h2_aut) |>
    as_tibble() |>
    filter(term == "game_aut_cw") |>
    mutate(predictor = "Autonomy satisfaction"),
  summary(sens9_h2_com) |>
    as_tibble() |>
    filter(term == "game_com_cw") |>
    mutate(predictor = "Competence satisfaction"),
  summary(sens9_h2_rel) |>
    as_tibble() |>
    filter(term == "game_rel_cw") |>
    mutate(predictor = "Relatedness satisfcation"),
  summary(sens9_h2_aut) |>
    as_tibble() |>
    filter(term == "global_aut_nf_cw") |>
    mutate(predictor = "Autonomy frustration"),
  summary(sens9_h2_com) |>
    as_tibble() |>
    filter(term == "global_com_nf_cw") |>
    mutate(predictor = "Competence frustration"),
  summary(sens9_h2_rel) |>
    as_tibble() |>
    filter(term == "global_rel_nf_cw") |>
    mutate(predictor = "Relatedness frustration")
) |>
  mutate(
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  select(
    Predictor = predictor,
    Estimate = estimate,
    SE = std.error,
    z = statistic,
    p = p.value
  ) |>
  tt(
    width = 0.5,
    notes = "All predictors are day-to-day fluctuations (within-person centered). Outcome: Probability of playing in subsequent 24 hours. Each need component is from a separate model."
  ) |>
  group_tt(
    i = list(
      "H2a: In-game need satisfaction → subsequent play" = 1,
      "H2b: Global need frustration → subsequent play" = 4
    )
  ) |>
  style_tt(i = c(1, 5), bold = TRUE) |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

### S8: Game need frustration and play behavior

Testing whether game need frustration (rather than satisfaction) is related to subsequent play behavior. This mirrors the H2a hypothesis but uses frustration instead of satisfaction.

```{r}
#| label: s8-game-nf-model
#| output: false
#| code-summary: "Show code (S8: Fit model with game NF predicting play)"

# File-based caching
sens10_cache_file <- "data/models/sens10_fits.rds"
sens10_pooled_file <- "data/models/sens10_pooled.rds"

if (file.exists(sens10_pooled_file)) {
  message("Loading cached S8 pooled results")
  sens10_pooled <- readRDS(sens10_pooled_file)
} else {
  message("Fitting S8 models...")

  # Prepare data with game_nf centered
  sens10_data <- lapply(1:m_imputations, function(i) {
    dat_i <- dat |> filter(.imp == i)

    dat_i |>
      group_by(pid) |>
      mutate(
        game_nf_pm = mean(game_nf, na.rm = TRUE)
      ) |>
      ungroup() |>
      mutate(
        game_nf_gm = mean(game_nf_pm, na.rm = TRUE),
        game_nf_cw = game_nf - game_nf_pm,
        game_nf_cb = game_nf_pm - game_nf_gm
      )
  })

  # Fit models
  sens10_fits <- lapply(sens10_data, function(dat_i) {
    glmmTMB::glmmTMB(
      telemetry_played_any_24h ~
        game_nf_cw +
        game_nf_cb +
        (1 | pid),
      family = binomial(link = "logit"),
      data = dat_i,
      control = glmmTMBControl(
        optimizer = optim,
        optArgs = list(method = "BFGS")
      )
    )
  })

  # Pool results
  sens10_pooled <- pool(sens10_fits)

  # Save to cache
  saveRDS(sens10_fits, sens10_cache_file)
  saveRDS(sens10_pooled, sens10_pooled_file)
  message("S8 models saved to cache")
}
```

```{r}
#| label: tbl-s8-results
#| tbl-cap: "S8: Game need frustration predicting subsequent play"
#| code-summary: "Show code (Create S8 results table)"

summary(sens10_pooled) |>
  as_tibble() |>
  filter(term != "(Intercept)", !str_detect(term, "_cb")) |>
  select(term, estimate, std.error, statistic, p.value) |>
  mutate(
    term = ifelse(term %in% names(labels), labels[term], term),
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  rename(
    Parameter = term,
    Estimate = estimate,
    SE = std.error,
    z = statistic,
    p = p.value
  ) |>
  tt() |>
  style_tt(fontsize = 0.7) |>
  style_tt(i = 0, bold = TRUE)
```

Results show that when people experience higher than usual in-game need frustration, they are less likely to play on the following day, but that this relationship is small. Nonetheless, in contrast to the robust null results for game need satisfaction across various specifications, this provides some initial evidence that need frustration may be more salient for day-to-day change in gaming behavior than need satisfaction.

### S9: H3 displacement by specific core life domain

The main H3 analysis aggregated all core life domains (work/school, social engagements, sleep/eating/fitness, caretaking) into a single binary indicator. Here we test whether specific displaced domains differ in their relationship with global need satisfaction.

```{r}
#| label: s9-h3-by-domain-prep
#| code-summary: "Show code (S9: Prepare domain-specific displacement indicators)"

# Create domain-specific displacement indicators
dat_domains <- dat |>
  left_join(
    activity_categories |> select(pid, wave, activity_label),
    by = c("pid", "wave")
  ) |>
  mutate(
    displaced_work_school = activity_label == "work_school",
    displaced_social = activity_label == "social_engagement",
    displaced_health_sleep = activity_label == "sleep_eat_fitness",
    displaced_caretaking = activity_label == "caretaking"
  )
```

```{r}
#| label: s9-h3-by-domain-models
#| output: false
#| code-summary: "Show code (S9: Fit H3 models for each core life domain)"

# File-based caching
s10_cache_file <- "data/models/s11_fits.rds"
s10_pooled_file <- "data/models/s11_pooled.rds"

if (file.exists(s10_cache_file) && file.exists(s10_pooled_file)) {
  message("Loading cached S9 model fits")
  s10_fits <- readRDS(s10_cache_file)
  s10_pooled <- readRDS(s10_pooled_file)
} else {
  message("Fitting S9 models...")

  # Fit separate model for each domain
  domains <- c(
    "displaced_work_school",
    "displaced_social",
    "displaced_health_sleep",
    "displaced_caretaking"
  )

  s10_fits <- list()
  s10_pooled <- list()

  for (domain in domains) {
    message(glue("Fitting model for {domain}"))

    # Filter to only observations where this specific domain could be displaced
    # (i.e., where the activity_label indicates this domain or other)
    domain_fits <- lapply(1:m_imputations, function(i) {
      dat_i <- dat_domains |>
        filter(.imp == i, !is.na(!!sym(domain)))

      glmmTMB(
        as.formula(glue(
          "global_ns ~ {domain} + (1 + {domain} | pid) + ar1(wave + 0 | pid)"
        )),
        data = dat_i
      )
    })

    s10_fits[[domain]] <- domain_fits
    s10_pooled[[domain]] <- pool(domain_fits)
  }

  # Save to cache
  dir.create("data/models", showWarnings = FALSE, recursive = TRUE)
  saveRDS(s10_fits, s10_cache_file)
  saveRDS(s10_pooled, s10_pooled_file)
  message("S9 models saved to cache")
}
```

```{r}
#| label: tbl-s9-domain-results
#| tbl-cap: "H3 sensitivity analysis: Effect of displacing specific core life domains on global need satisfaction"
#| code-summary: "Show code (Create S9 results table)"

# Extract results for each domain
s10_results <- bind_rows(
  lapply(names(s10_pooled), function(domain) {
    summary(s10_pooled[[domain]]) |>
      as_tibble() |>
      filter(str_detect(term, "TRUE")) |>
      select(term, estimate, std.error, statistic, p.value) |>
      mutate(
        Domain = case_when(
          domain == "displaced_work_school" ~ "Work/School",
          domain == "displaced_social" ~ "Social Engagement",
          domain == "displaced_health_sleep" ~ "Sleep/Eating/Fitness",
          domain == "displaced_caretaking" ~ "Caretaking",
          TRUE ~ domain
        )
      ) |>
      select(Domain, estimate, std.error, statistic, p.value)
  })
)

s10_results |>
  mutate(
    across(c(estimate, std.error, statistic), ~ round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<.001",
      p.value < 0.01 ~ sprintf("%.3f", p.value),
      TRUE ~ sprintf("%.2f", p.value)
    )
  ) |>
  tt(
    width = 0.5,
    escape = TRUE,
    notes = "All models include random intercepts, random slopes, and AR(1) autocorrelation. Estimates represent the difference in global need satisfaction when the specific domain was displaced vs. not displaced."
  ) |>
  style_tt(fontsize = 0.8) |>
  style_tt(i = 0, bold = TRUE)
```

Results showed that global need satisfaction was lower when gaming displaced sleep/eating/fitness, but---contrary to expectations---tended to be higher when gaming displaced social engagements or caretaking.

## References

::: {#refs}
:::
